### 2007-02-14 papers/hpdc-gmw-2007/paper.tex
adding files
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6515 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{User-level Grid Monitoring with Inca 2}

\author{Shava Smallen, Kate Ericson, and Jim Hayes \\
San Diego Supercomputer Center\\ University of California, San Diego\\ 
9500 Gilman Drive, La Jolla, CA 92093-0505, USA\\ 
\{ssmallen,kericson,jhayes\}@sdsc.edu\\
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
User-level Grid monitoring is valuable, how it relates to other Grid
monitoring,  and what are its implementation challenges.
Inca 1 good but had limitations.  In this paper, we introduce Inca 2 and
describe its features and architecture.  We then show a few use cases for Inca
is being deployed on TeraGrid and XXX?  System impact results and performance
results.  Finally, we discuss our future work.  
\end{abstract}

% Goals:
% 1. Motivated and differentiate the Grid monitoring Inca does and 
% 3. Describe Inca 2 design and its benefits
% 4. Illustrate that Inca 2 design is mature and being used in production by
%     several Grids
% 2. Not to restate stuff from Inca 1 paper

%------------------------------------------------------------------------- 
\Section{Introduction}

Grid monitoring is x, y, and z.  Describe the stakeholders.

User-level Grid monitoring is x and is valuable.

However, implementing user-level Grid monitoring has challenges.  List.

Inca 1~\cite{inca1} first addressed this but had limitations.  We learned
lessons from our TeraGrid deployment.  This motivated our development of a new
version of Inca.

%------------------------------------------------------------------------- 
\Section{Design and Implementation}

Features list.

Overview of all architecture components -- arch picture

%-------------------------------------------------------------------------

\SubSection{Inca Components}

%\begin{figure}[h]
%   \caption{Example of caption.}
%\end{figure}
%
%\noindent Long captions should be set as in 
%\begin{figure}[h] 
%   \caption{Example of long caption requiring more than one line. It is 
%     not typed centered but aligned on both sides and indented with an 
%     additional margin on both sides of 1~pica.}
%\end{figure}

%------------------------------------------------------------------------- 
\Section{Use Cases}

\SubSection{TeraGrid}

\SubSection{DEISA??}

%------------------------------------------------------------------------- 
\Section{System Impact and Performance Results}

Maybe.

%------------------------------------------------------------------------- 
\Section{Summary}

%------------------------------------------------------------------------- 
\bibliographystyle{latex8}
\bibliography{paper}

\end{document}

### 2007-02-16 pubs/papers/hpdc-gmw-2007/paper.tex
start of outline
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6517 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{User-level Grid Monitoring with Inca 2}

\author{Shava Smallen, Kate Ericson, and Jim Hayes \\
San Diego Supercomputer Center\\ University of California, San Diego\\ 
9500 Gilman Drive, La Jolla, CA 92093-0505, USA\\ 
\{ssmallen,kericson,jhayes\}@sdsc.edu\\
}

\maketitle
\thispagestyle{empty}

%1.  Motivate and differentiate the Grid monitoring Inca does
%2. Describe Inca 2 design and its benefits
%3. Illustrate that Inca 2 design is mature and being used in production by
%several Grids
%4. Be different from Inca 1 paper

\begin{abstract}
User-level Grid monitoring is valuable, how it relates to other Grid
monitoring,  and what are its implementation challenges.
Inca 1 good but had limitations.  In this paper, we introduce Inca 2 and
describe its features and architecture.  We then show a few use cases for Inca
is being deployed on TeraGrid and XXX?  System impact results and performance
results.  Finally, we discuss our future work.  
\end{abstract}

%------------------------------------------------------------------------- 
\Section{Introduction}

Grid monitoring is x, y, and z.  Describe the stakeholders.

User-level Grid monitoring is x and is valuable.

However, implementing user-level Grid monitoring has challenges.  List.

Inca 1~\cite{inca1} first addressed this but had limitations.  We learned
lessons from our TeraGrid deployment.  This motivated our development of a new
version of Inca.

~\newpage
~\newpage
~\newpage
~\newpage

%------------------------------------------------------------------------- 
\Section{Design and Implementation}

Features list.

Differences with Inca 1 table?

Overview of all architecture components -- arch picture

The core of the Inca architecture (shown in Figure 1) is formed by two
components: the agent and the depot.  The agent controls the execution of the
Inca installation, while the depot provides data storage. All Inca components
use SSL to communicate.

\begin{figure}[Htb]
  \centering
  \mbox{\epsfig{file=arch.eps, width=\columnwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure}

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  After determining which Inca tests should be executed on
each resource, the agent stores this configuration information in the depot.
It then stages and launches a dependent component, called a reporter manager,
on each resource using either SSH or Globus [13].  Once a reporter manager
contacts its agent, the agent transmits Inca tests to execute, along with
their dependencies, configuration and schedule of execution.

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca tests, called reporters, on a single
resource. The reporter manager receives reporter updates and dependencies
(e.g., Inca Perl APIs or source code) from the agent along with requests for
reporter scheduling changes.  Running under a regular user account, the
reporter manager executes reporters on-demand or using an internal cron
scheduler, and sends reports to the depot for archiving. The reporter
manager monitors reporter system usage and enforces limits (e.g., wall clock
time, CPU time, memory).  System usage information is sent to the depot with
each report.

Each Inca reporter is an executable program that tests or measures some
aspect of a system or installed software.   Reporter executables are
designed to be easy to produce and can be run outside of the Inca system
(e.g., by a system administrator).  A reporter could be a simple Globus
gatekeeper ping test (see Figure 2) or a more complex Grid application
benchmark.  Reporters must support certain command line options and produce
XML according to the Inca reporter schema.  The reporter schema requires a
header describing the context of the reporter execution (e.g., reporter
name, arguments, working directory, timestamp) and a body containing the
results expressed as any XML sequence. This flexible body schema enables
reporters to express a wide variety of information.  Today, we have three
standard body schemas to express software version information, software
functionality or service tests results, and usage information.  We provide
Perl APIs to handle much of the effort of writing reporters.  Most current
reporters use these APIs and consist of fewer than 30 lines of code.

The Inca agent retrieves reporters from collections called reporter
repositories, that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.

The Inca depot server is responsible for storing configuration information
and the data produced by reporters. The depot maintains a relational
database via Hibernate [14] so that it can use a variety of databases.  The
depot provides full archiving of reporter output and structures its schema
to reduce redundant data.  Data can be queried using SQL queries. Predefined
queries exist to return the latest report instances of a suite, a single
report instance, or a report history.  A Web services interface is also
available to provide unauthenticated query access to data.

To configure reporter execution, an Inca administrator launches a GUI tool,
called incat.  Incat allows the administrator to choose which resources to
monitor and which reporters to deploy to those resources.  For each
reporter, the administrator can specify the resources to run on,
command-line arguments, the runtime environment, the frequency of execution,
and resource limits. The Inca administrator may also group related reporters
into suites that can be shared across different Inca deployments.  This can
be useful to determine interoperability among Grids or to determine whether
an application's requirements are being fulfilled on a Grid.

The Inca data consumer is a Web application that queries the Inca depot for
data and displays it in a user-friendly format.  The data consumer is
packaged with Jetty [15] so that pages can be served immediately without
deploying Tomcat [16].  A set of JSP tags and pages query the Inca depot for
data (returned as XML) and a set of XSL stylesheets format the data as HTML.

~\newpage
~\newpage
~\newpage
~\newpage
%-------------------------------------------------------------------------

\Section{Use Cases}

\SubSection{TeraGrid}
~\newpage
~\newpage

\SubSection{GrASP}
~\newpage

\SubSection{Other uses}
~\newpage
%------------------------------------------------------------------------- 
\Section{Future Work}
~\newpage

%------------------------------------------------------------------------- 
\Section{Summary}

~\newpage

%------------------------------------------------------------------------- 
\bibliographystyle{latex8}
\bibliography{paper}

\end{document}

### 2007-02-20 pubs/papers/hpdc-gmw-2007/paper.tex
better outline -- and some text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6528 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \usepackage{times}
+\usepackage{url}
 
@@
 
-\author{Shava Smallen, Kate Ericson, and Jim Hayes \\
+\author{Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
 San Diego Supercomputer Center\\ University of California, San Diego\\ 
 9500 Gilman Drive, La Jolla, CA 92093-0505, USA\\ 
-\{ssmallen,kericson,jhayes\}@sdsc.edu\\
+\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu\\
 }
@@
 
-Grid monitoring is x, y, and z.  Describe the stakeholders.
+% Standard "Grids are good" intro paragraph.  But are complex.  
+Grid systems provide unified and coherent access to distributed computing,
+data storage and analysis, instruments, and other resources.  These systems
+require the careful coordination of software packages, services, and
+configurations across multiple, heterogenous resources.  The TeraGrid
+project~\cite{teragrid}, for example, manages the coordination of software and
+services by deploying and monitoring a common user environment across
+distributed, heterogeneous resources. The organization of TeraGrid software
+and services is referred to as the Common TeraGrid Software and Services
+(CTSS).  TeraGrid's software and services uniformity simplifies access to its
+resources, which consist of more than 102 teraflops of compute capability and
+more than 15 petabytes of online storage, all interconnected by a network that
+can transfer a terabyte of data in under 10 minutes.
 
+% Complex means they are difficult to provide and maintain. Describe the
+% stakeholders.   Monitoring is needed.
+Providing and maintaining a stable infrastructure for these complex 
+Grid systems poses challenges for both administrators who build and
+maintain Grid resources and scientists who use them.  
+% Why?  
+% 1. Administration is distributed across multiple admins
+Administration of the Grid infrastructure is typically coordinated by a group 
+of Grid operators who decide when software should be deployed to resources and
+how it should be configured.  Each site's system administrators are then
+responsible for providing the required software components and services for
+their resource.  Grid operators need to take into account local site policies
+and heterogenous architectures when requiring software.  System administrators
+need to learn enough Grid knowledge to deploy software and debug problems.  In
+this distributed model, good communication of the requirements is required in
+order for Grid resources to interoperate with one another.  Otherwise
+inconsistencies between the resources arise that can either inconvenience the
+user or prevent them from using particular resources together.
+% 2. Grid software failures
+distributed system, components will fail over time.  As with any distributed
+systems, the probability of failure increases as the number of elements 
+increase.  Failures can occur due to system downtimes, misconfiguration in the 
+software, bugs in the software, high load.  
+which means miscommunications can occur.  
+% 3. Changes 
+Third it is challenging due to the
+activeness in Grids, packages and updates can occur frequently.
+
+% What types of Grid monitoring are around?  What user-level monitoring
+% provides and why we think it is good
+One approach to monitoring Grids, used by tools such as
+MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
+display data from existing cluster or system administrator monitoring tools
+such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, and
+Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
+resources where low-level host statistics and queue information can be
+examined.  This type of monitoring information is useful for showing the
+utilization of Grid resources, however, it does not provide the type of
+high-level monitoring needed to detect user problems within the Grid
+infrastructure, such as incompatible software versions.  User-level
+Grid monitoring approaches testing is important because it run commands that users use and tests
+to see if they operate as expected. Execute commands published in user
+documentation, detect problems otherwise reported by users.
+
+so called user-level Grid monitoring is bIn our view, what was
+needed was a separate
+monitoring system to perform automated, periodic user-level Grid testing with
+the following features:
 User-level Grid monitoring is x and is valuable.  
+At that
+time, the only available user-level Grid monitoring tools were the NCSA
+TestGrid script [9] and GITS [10], scripts that run a fixed number of Grid
+tests and output results in HTML.  Although these tools were easy to install
+and produced useful information, they showed only the view of the Grid from a
+single resource, lacked automation, and were not easily extensible.
 
-However, implementing user-level Grid monitoring has challenges.  List.
+% Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
+% limitations.  We learned lessons from our TeraGrid deployment.  
+In 2003, SDSC, in partnership with TeraGrid, began developing the Inca
+monitoring tool to implement a user-level monitoring system with the above
+features and started using it to validate and verify that CTSS was deployed
+consistently across all TeraGrid resources and to monitor its status.  
+The initial version of Inca was implemented as a client-server architecture.
+It provided data collection, data storage (with limited archiving
+capabilities) that was accessible from a Web services interface, and data
+display though Web status pages.  Inca was first deployed to TeraGrid in mid
+2003 and released in late 2003. After running Inca 1 for a year and a half on
+TeraGrid, we learned some valuable lessons and designed Inca version 2, our
+current release.  Inca 2 contains a number of substantial improvements over
+Inca 1 with respect to security, installation and maintenance, and storage
+capabilities.  A pre-release of Inca 2 was provided in February 2006 and a
+beta release in November 2006.  A production version of Inca 2 was released in
+January 2007.  Currently, seven other Grids in the U.S., Europe, and Australia
+use Inca.
 
-Inca 1~\cite{inca1} first addressed this but had limitations.  We learned
-lessons from our TeraGrid deployment.  This motivated our development of a new
-version of Inca.
+% This motivated our development of a new version of Inca.
+In the next section, we describe our experiences with deploying Inca 1 to
+TeraGrid and the lessons learned.  We then describe the Inca 2 architecture
+and the benefits it provides.  Use cases illustrate that Inca 2 is being used
+today and has great results.
 
-~\newpage
-~\newpage
-~\newpage
+\Section{Features}
+
+% Philosophy of user-level testing
+% Practical byproducts
+
+1.  Periodic tests executed by the monitoring system should be automated and
+run from a standard user account.  A user GSI credential should be issued and
+used by the monitoring system to test services that require authentication.  
+%myproxy stuff
+2.  Tests should be executed locally on all Grid resources when appropriate so
+that all Grid access points available to users are tested.  
+3.  The configuration of tests should be managed centrally in order to ensure
+consistent testing of the resources, rather than by system administrators who
+may not use the same information that is available to users.
+4.  The testing system should easily adapt to new resources and testing
+requirements.  In our experience, testing has an iterative refinement process
+because Grids are dynamic and the software environment changes over time as
+packages are upgraded.  Furthermore, it is often difficult to write and deploy
+a test perfectly the first time because of portability issues and incomplete
+user documentation.   
+5.  System administrators should not need to know the details of the
+monitoring system in order to troubleshoot problems.  When a problem is
+detected the monitoring system should provide system administrators with
+sufficient information to locate the problem easily and test repairs.
+6.  A history of test results (especially any error messages) should be
+retained in order to understand the behavior of their Grid over time. This
+history should be available through a flexible querying interface.
+7.  A running monitoring system should have a limited impact on the resources
+it measures and should be secure.
+
 ~\newpage
@@
 %------------------------------------------------------------------------- 
-\Section{Design and Implementation}
+%------------------------------------------------------------------------- 
+\Section{Architecture}
 
-Features list.
+\SubSection{Overview}
+% may not need to leave in here -- intro is assumed to be overview
+% Overview of all architecture components -- arch picture
+% move text to here I think
+1) The user creates a suite using incat and submits it to the agent
 
-Differences with Inca 1 table?
+2) The agent 
+    a) fetches reporters from the reporter repository
+    b) creates a reporter manager on each resource
+    c) sends the suite and reporters to each reporter manager.
 
-Overview of all architecture components -- arch picture
+3) Each reporter manager executes reporters according to its schedule and
+sends results (reports) to the depot
 
-The core of the Inca architecture (shown in Figure 1) is formed by two
-components: the agent and the depot.  The agent controls the execution of the
-Inca installation, while the depot provides data storage. All Inca components
-use SSL to communicate.
+4) Data consumers display collected data (reports) by querying the depot
 
-\begin{figure}[Htb]
+\begin{figure*}[Htb]
   \centering
-  \mbox{\epsfig{file=arch.eps, width=\columnwidth}}
+  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
   \caption{\label{arch_fig} Inca architecture.}
-\end{figure}
+\end{figure*}
 
-The Inca agent is a server that implements the configuration specified by the
-Inca administrator.  After determining which Inca tests should be executed on
-each resource, the agent stores this configuration information in the depot.
-It then stages and launches a dependent component, called a reporter manager,
-on each resource using either SSH or Globus [13].  Once a reporter manager
-contacts its agent, the agent transmits Inca tests to execute, along with
-their dependencies, configuration and schedule of execution.
+\SubSection{Inca administration GUI tool (incat)}
 
-The Inca reporter manager is a lightweight process responsible for managing
-the schedule and execution of Inca tests, called reporters, on a single
-resource. The reporter manager receives reporter updates and dependencies
-(e.g., Inca Perl APIs or source code) from the agent along with requests for
-reporter scheduling changes.  Running under a regular user account, the
-reporter manager executes reporters on-demand or using an internal cron
-scheduler, and sends reports to the depot for archiving. The reporter
-manager monitors reporter system usage and enforces limits (e.g., wall clock
-time, CPU time, memory).  System usage information is sent to the depot with
-each report.
+To configure reporter execution, an Inca administrator launches a GUI tool,
+called incat.  Incat allows the administrator to choose which resources to
+monitor and which reporters to deploy to those resources.  For each
+reporter, the administrator can specify the resources to run on,
+command-line arguments, the runtime environment, the frequency of execution,
+and resource limits. The Inca administrator may also group related reporters
+into suites that can be shared across different Inca deployments.  This can
+be useful to determine interoperability among Grids or to determine whether
+an application's requirements are being fulfilled on a Grid.
+
+\subsubsection{Reporters}
 
@@
 reporters use these APIs and consist of fewer than 30 lines of code.  
+% capture context of execution
+
+\subsubsection{Reporter Repositories}
 
@@
 reporter repository that contains reporters developed for TeraGrid.
+
+\subsubsection{Suites}
+%\subsubsection{Series}
+
+\subsubsection{Resource Macros}
+
+\SubSection{Agent}
+
+The Inca agent is a server that implements the configuration specified by the
+Inca administrator.  After determining which Inca tests should be executed on
+each resource, the agent stores this configuration information in the depot.
+It then stages and launches a dependent component, called a reporter manager,
+on each resource using either SSH or Globus [13].  Once a reporter manager
+contacts its agent, the agent transmits Inca tests to execute, along with
+their dependencies, configuration and schedule of execution.
+
+\SubSection{Reporter Manager}
+
+The Inca reporter manager is a lightweight process responsible for managing
+the schedule and execution of Inca tests, called reporters, on a single
+resource. The reporter manager receives reporter updates and dependencies
+(e.g., Inca Perl APIs or source code) from the agent along with requests for
+reporter scheduling changes.  Running under a regular user account, the
+reporter manager executes reporters on-demand or using an internal cron
+scheduler, and sends reports to the depot for archiving. The reporter
+manager monitors reporter system usage and enforces limits (e.g., wall clock
+time, CPU time, memory).  System usage information is sent to the depot with
+each report.
+
+\SubSection{Depot}
 
@@
 
-To configure reporter execution, an Inca administrator launches a GUI tool,
-called incat.  Incat allows the administrator to choose which resources to
-monitor and which reporters to deploy to those resources.  For each
-reporter, the administrator can specify the resources to run on,
-command-line arguments, the runtime environment, the frequency of execution,
-and resource limits. The Inca administrator may also group related reporters
-into suites that can be shared across different Inca deployments.  This can
-be useful to determine interoperability among Grids or to determine whether
-an application's requirements are being fulfilled on a Grid.
+\SubSection{Data Consumer}
 
@@
 \SubSection{TeraGrid}
-~\newpage
+
+\subsubsection{Description and Requirements}
+
+% Describe CTSS
+
+\subsubsection{Usage of Inca}
+
+% Describe reporters, configuration, and deployment.  Figure.
+
+\subsubsection{Results}
+
+% Consumer view of CTSS, security, etc.
+
 ~\newpage
@@
 \SubSection{GrASP}
+
+\subsubsection{Description and Requirements}
+
+% Describe GrASP probes
+
+\subsubsection{Usage of Inca}
+
+% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
+% right in future as though we already included GrASP as a dependency cause
+% it should be done by June.
+
+\subsubsection{Results}
+
+% A paper.  Interesting that error messages were important.  Predictions?
+
 ~\newpage
@@
 \Section{Future Work}
+
+\SubSection{Graphing and Summary Statistics}
+
+\SubSection{Knowledge Base}
+
+\SubSection{Fault Tolerance}
 ~\newpage

### 2007-02-21 papers/hpdc-gmw-2007/paper.tex
Smoothing out intro some
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6529 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \documentclass[times, 10pt,twocolumn]{article} 
+\usepackage{epsfig}
 \usepackage{latex8}
 \usepackage{times}
+\usepackage{url}
 
@@
 \thispagestyle{empty}
+
+%1.  Motivate and differentiate the Grid monitoring Inca does
+%2. Describe Inca 2 design and its benefits
+%3. Illustrate that Inca 2 design is mature and being used in production by
+%several Grids
+%4. Be different from Inca 1 paper
 
@@
 
-% Goals:
-% 1. Motivated and differentiate the Grid monitoring Inca does and 
-% 3. Describe Inca 2 design and its benefits
-% 4. Illustrate that Inca 2 design is mature and being used in production by
-%     several Grids
-% 2. Not to restate stuff from Inca 1 paper
-
 %------------------------------------------------------------------------- 
@@
 
-Grid monitoring is x, y, and z.  Describe the stakeholders.
+% Standard "Grids are good" intro paragraph.  But are complex.  
+Grid systems provide unified and coherent access to distributed computing,
+data storage and analysis, instruments, and other resources.  These systems
+require the careful coordination of software packages, services, and
+configurations across multiple, heterogenous resources.  The TeraGrid
+project~\cite{teragrid}, for example, manages the coordination of software and
+services by deploying and monitoring a common user environment across
+distributed, heterogeneous resources. The organization of TeraGrid software
+and services is referred to as the Common TeraGrid Software and Services
+(CTSS).  TeraGrid's software and services uniformity simplifies access to its
+resources, which consist of more than 102 teraflops of compute capability and
+more than 15 petabytes of online storage, all interconnected by a network that
+can transfer a terabyte of data in under 10 minutes.
 
+% Complex means they are difficult to provide and maintain. Describe the
+% stakeholders.   Monitoring is needed.
+Providing and maintaining a stable infrastructure for these complex 
+Grid systems poses challenges for both administrators who build and
+maintain Grid resources and scientists who use them.  First, system
+administration is distributed across multiple administrative domains which
+requires a significant amount of coordination.  This is typically performed by
+a group of Grid operators who take into account local site policies 
+and decide when software (including updates and patches) should be deployed to
+resources and how it should be configured for the set of heterogenous
+resources.  Each site's system administrators, who are oftentimes not Grid
+experts, are then responsible for providing the required Grid software
+components and services for their resource and debugging any problems that
+arise.  Well-defined requirements and good communication are required in this
+model.  Otherwise inconsistencies between the resources arise that can either
+inconvenience the user or prevent them from using particular resources
+together.  Second, as a large distributed system, failures will occur over
+time in the Grid services due to network or system failures, software
+misconfiguration, or software bugs.  In order to detect such problems, 
+monitoring of the resources is required.
+
+% What types of Grid monitoring are around and what the limitations are
+One approach to monitoring Grids, used by tools such as
+MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
+display data from existing cluster or system administrator monitoring tools
+such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, and
+Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
+resources where low-level host statistics and queue information can be
+examined.  This type of monitoring information is useful for showing the
+utilization of Grid resources, however, it does not provide the type of
+high-level monitoring needed to detect user problems within the Grid
+infrastructure, such as incompatible software versions.
+
+% What user-level monitoring provides and why we think it is good
+User-level Grid monitoring approaches testing and performance measurement of
+the Grid infrastructure from the user perspective.  The goal is to act as an
+impartial test user of the Grid and detect problems with the Grid
+infrastructure so they can be fixed before users notice them -- user
+complaints should not be the first indication of Grid failures.  User-level
+Grid monitoring has the following characteristics:
+
+\begin{itemize}
+
+\item Tests or performance measurements of the Grid infrastructure should be
+done from a standard user account.  Tests executed by system administrators may
+not reflect regular user experiences because they run under privileged
+accounts that often have custom shell initialization files.
+System administrators may also configure tests using undocumented information
+(e.g., they know GridFTP server hostnames not in the user guide).
+
+\item Because the Grid infrastructure is dynamic, Tests or performance
+measurements should be executed periodically and automated.
+
+\item A user GSI credential should be issued and
+used by the monitoring system to test services that require authentication.
+
+\item Tests should be executed locally on all Grid resources when appropriate
+so that all Grid access points available to users are tested.
+
+\item Also important to test some services from site to site.
+\end{itemize}
+Amount of testing can vary and is oftentimes limited by the amount of
+reosurces that can be addressed to it.  A good approach is to test all the
+commands that exist in the user documentation or have at least one basic test
+for each software component of the Grid infrastructure.  
+commands that users use and tests to see if they operate as expected. Execute
+commands published in user
+documentation, detect problems otherwise reported by users.
+
+so called user-level Grid monitoring is bIn our view, what was
+needed was a separate
+monitoring system to perform automated, periodic user-level Grid testing with
+the following features:
 User-level Grid monitoring is x and is valuable.  
+At that
+time, the only available user-level Grid monitoring tools were the NCSA
+TestGrid script [9] and GITS [10], scripts that run a fixed number of Grid
+tests and output results in HTML.  Although these tools were easy to install
+and produced useful information, they showed only the view of the Grid from a
+single resource, lacked automation, and were not easily extensible.
 
-However, implementing user-level Grid monitoring has challenges.  List.
+% Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
+% limitations.  We learned lessons from our TeraGrid deployment.  
+In 2003, SDSC, in partnership with TeraGrid, began developing the Inca
+monitoring tool to implement a user-level monitoring system with the above
+features and started using it to validate and verify that CTSS was deployed
+consistently across all TeraGrid resources and to monitor its status.  
+The initial version of Inca was implemented as a client-server architecture.
+It provided data collection, data storage (with limited archiving
+capabilities) that was accessible from a Web services interface, and data
+display though Web status pages.  Inca was first deployed to TeraGrid in mid
+2003 and released in late 2003. After running Inca 1 for a year and a half on
+TeraGrid, we learned some valuable lessons and designed Inca version 2, our
+current release.  Inca 2 contains a number of substantial improvements over
+Inca 1 with respect to security, installation and maintenance, and storage
+capabilities.  A pre-release of Inca 2 was provided in February 2006 and a
+beta release in November 2006.  A production version of Inca 2 was released in
+January 2007.  Currently, seven other Grids in the U.S., Europe, and Australia
+use Inca.
 
-Inca 1~\cite{inca1} first addressed this but had limitations.  We learned
-lessons from our TeraGrid deployment.  This motivated our development of a new
-version of Inca.
+% This motivated our development of a new version of Inca.
+In the next section, we describe our experiences with deploying Inca 1 to
+TeraGrid and the lessons learned.  We then describe the Inca 2 architecture
+and the benefits it provides.  Use cases illustrate that Inca 2 is being used
+today and has great results.
+
+\Section{Features}
+
+% Philosophy of user-level testing
+% Practical byproducts
+
+1.  Periodic tests executed by the monitoring system should be automated and
+run from a standard user account.  A user GSI credential should be issued and
+used by the monitoring system to test services that require authentication.  
+%myproxy stuff
+2.  Tests should be executed locally on all Grid resources when appropriate so
+that all Grid access points available to users are tested.  
+3.  The configuration of tests should be managed centrally in order to ensure
+consistent testing of the resources, rather than by system administrators who
+may not use the same information that is available to users.
+4.  The testing system should easily adapt to new resources and testing
+requirements.  In our experience, testing has an iterative refinement process
+because Grids are dynamic and the software environment changes over time as
+packages are upgraded.  Furthermore, it is often difficult to write and deploy
+a test perfectly the first time because of portability issues and incomplete
+user documentation.   
+5.  System administrators should not need to know the details of the
+monitoring system in order to troubleshoot problems.  When a problem is
+detected the monitoring system should provide system administrators with
+sufficient information to locate the problem easily and test repairs.
+6.  A history of test results (especially any error messages) should be
+retained in order to understand the behavior of their Grid over time. This
+history should be available through a flexible querying interface.
+7.  A running monitoring system should have a limited impact on the resources
+it measures and should be secure.
+
+~\newpage
 
 %------------------------------------------------------------------------- 
-\Section{Design and Implementation}
+%------------------------------------------------------------------------- 
+\Section{Architecture}
 
-Features list.
+\SubSection{Overview}
+% may not need to leave in here -- intro is assumed to be overview
+% Overview of all architecture components -- arch picture
+% move text to here I think
+1) The user creates a suite using incat and submits it to the agent
 
-Overview of all architecture components -- arch picture
+2) The agent 
+    a) fetches reporters from the reporter repository
+    b) creates a reporter manager on each resource
+    c) sends the suite and reporters to each reporter manager.
 
+3) Each reporter manager executes reporters according to its schedule and
+sends results (reports) to the depot
+
+4) Data consumers display collected data (reports) by querying the depot
+
+\begin{figure*}[Htb]
+  \centering
+  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
+  \caption{\label{arch_fig} Inca architecture.}
+\end{figure*}
+
+\SubSection{Inca administration GUI tool (incat)}
+
+To configure reporter execution, an Inca administrator launches a GUI tool,
+called incat.  Incat allows the administrator to choose which resources to
+monitor and which reporters to deploy to those resources.  For each
+reporter, the administrator can specify the resources to run on,
+command-line arguments, the runtime environment, the frequency of execution,
+and resource limits. The Inca administrator may also group related reporters
+into suites that can be shared across different Inca deployments.  This can
+be useful to determine interoperability among Grids or to determine whether
+an application's requirements are being fulfilled on a Grid.
+
+\subsubsection{Reporters}
+
+Each Inca reporter is an executable program that tests or measures some
+aspect of a system or installed software.   Reporter executables are
+designed to be easy to produce and can be run outside of the Inca system
+(e.g., by a system administrator).  A reporter could be a simple Globus
+gatekeeper ping test (see Figure 2) or a more complex Grid application
+benchmark.  Reporters must support certain command line options and produce
+XML according to the Inca reporter schema.  The reporter schema requires a
+header describing the context of the reporter execution (e.g., reporter
+name, arguments, working directory, timestamp) and a body containing the
+results expressed as any XML sequence. This flexible body schema enables
+reporters to express a wide variety of information.  Today, we have three
+standard body schemas to express software version information, software
+functionality or service tests results, and usage information.  We provide
+Perl APIs to handle much of the effort of writing reporters.  Most current
+reporters use these APIs and consist of fewer than 30 lines of code.  
+% capture context of execution
+
+\subsubsection{Reporter Repositories}
+
+The Inca agent retrieves reporters from collections called reporter
+repositories, that consist of reporters, required packages and libraries,
+and a catalog file. Repository contents are accessible using a URL and can
+be shared across multiple Inca deployments. The Inca team publishes a
+reporter repository that contains reporters developed for TeraGrid.
+
+\subsubsection{Suites}
+%\subsubsection{Series}
+
+\subsubsection{Resource Macros}
+
+\SubSection{Agent}
+
+The Inca agent is a server that implements the configuration specified by the
+Inca administrator.  After determining which Inca tests should be executed on
+each resource, the agent stores this configuration information in the depot.
+It then stages and launches a dependent component, called a reporter manager,
+on each resource using either SSH or Globus [13].  Once a reporter manager
+contacts its agent, the agent transmits Inca tests to execute, along with
+their dependencies, configuration and schedule of execution.
+
+\SubSection{Reporter Manager}
+
+The Inca reporter manager is a lightweight process responsible for managing
+the schedule and execution of Inca tests, called reporters, on a single
+resource. The reporter manager receives reporter updates and dependencies
+(e.g., Inca Perl APIs or source code) from the agent along with requests for
+reporter scheduling changes.  Running under a regular user account, the
+reporter manager executes reporters on-demand or using an internal cron
+scheduler, and sends reports to the depot for archiving. The reporter
+manager monitors reporter system usage and enforces limits (e.g., wall clock
+time, CPU time, memory).  System usage information is sent to the depot with
+each report.
+
+\SubSection{Depot}
+
+The Inca depot server is responsible for storing configuration information
+and the data produced by reporters. The depot maintains a relational
+database via Hibernate [14] so that it can use a variety of databases.  The
+depot provides full archiving of reporter output and structures its schema
+to reduce redundant data.  Data can be queried using SQL queries. Predefined
+queries exist to return the latest report instances of a suite, a single
+report instance, or a report history.  A Web services interface is also
+available to provide unauthenticated query access to data.
+
+\SubSection{Data Consumer}
+
+The Inca data consumer is a Web application that queries the Inca depot for
+data and displays it in a user-friendly format.  The data consumer is
+packaged with Jetty [15] so that pages can be served immediately without
+deploying Tomcat [16].  A set of JSP tags and pages query the Inca depot for
+data (returned as XML) and a set of XSL stylesheets format the data as HTML.
+
+~\newpage
+~\newpage
+~\newpage
+~\newpage
 %-------------------------------------------------------------------------
 
-\SubSection{Inca Components}
-
-%\begin{figure}[h]
-%   \caption{Example of caption.}
-%\end{figure}
-%
-%\noindent Long captions should be set as in 
-%\begin{figure}[h] 
-%   \caption{Example of long caption requiring more than one line. It is 
-%     not typed centered but aligned on both sides and indented with an 
-%     additional margin on both sides of 1~pica.}
-%\end{figure}
-
-%------------------------------------------------------------------------- 
 \Section{Use Cases}
@@
 
-\SubSection{DEISA??}
+\subsubsection{Description and Requirements}
 
+% Describe CTSS
+
+\subsubsection{Usage of Inca}
+
+% Describe reporters, configuration, and deployment.  Figure.
+
+\subsubsection{Results}
+
+% Consumer view of CTSS, security, etc.
+
+~\newpage
+
+\SubSection{GrASP}
+
+\subsubsection{Description and Requirements}
+
+% Describe GrASP probes
+
+\subsubsection{Usage of Inca}
+
+% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
+% right in future as though we already included GrASP as a dependency cause
+% it should be done by June.
+
+\subsubsection{Results}
+
+% A paper.  Interesting that error messages were important.  Predictions?
+
+~\newpage
+
+\SubSection{Other uses}
+~\newpage
 %------------------------------------------------------------------------- 
-\Section{System Impact and Performance Results}
+\Section{Future Work}
 
-Maybe.
+\SubSection{Graphing and Summary Statistics}
+
+\SubSection{Knowledge Base}
+
+\SubSection{Fault Tolerance}
+~\newpage
 
@@
 \Section{Summary}
+
+~\newpage
 

### 2007-02-21 pubs/papers/hpdc-gmw-2007/paper.tex
smoothing of intro and biblio adding and cleaning
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6531 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 Grid systems poses challenges for both administrators who build and
-maintain Grid resources and scientists who use them.  
-% Why?  
-% 1. Administration is distributed across multiple admins
-Administration of the Grid infrastructure is typically coordinated by a group 
-of Grid operators who decide when software should be deployed to resources and
-how it should be configured.  Each site's system administrators are then
-responsible for providing the required software components and services for
-their resource.  Grid operators need to take into account local site policies
-and heterogenous architectures when requiring software.  System administrators
-need to learn enough Grid knowledge to deploy software and debug problems.  In
-this distributed model, good communication of the requirements is required in
-order for Grid resources to interoperate with one another.  Otherwise
-inconsistencies between the resources arise that can either inconvenience the
-user or prevent them from using particular resources together.
-% 2. Grid software failures
-distributed system, components will fail over time.  As with any distributed
-systems, the probability of failure increases as the number of elements 
-increase.  Failures can occur due to system downtimes, misconfiguration in the 
-software, bugs in the software, high load.  
-which means miscommunications can occur.  
-% 3. Changes 
-Third it is challenging due to the
-activeness in Grids, packages and updates can occur frequently.
+maintain Grid resources and scientists who use them.  First, system
+administration is distributed across multiple administrative domains which
+requires a significant amount of coordination.  This is typically performed by
+a group of Grid operators who take into account local site policies 
+and decide when software (including updates and patches) should be deployed to
+resources and how it should be configured for the set of heterogenous
+resources.  Each site's system administrators, who are oftentimes not Grid
+experts, are then responsible for providing the required Grid software
+components and services for their resource and debugging any problems that
+arise.  Well-defined requirements and good communication are required in this
+model.  Otherwise inconsistencies between the resources arise that can either
+inconvenience the user or prevent them from using particular resources
+together.  Second, as a large distributed system, failures will occur over
+time in the Grid services due to network or system failures, software
+misconfiguration, or software bugs.  In order to detect such problems, 
+monitoring of the resources is required.
 
-% What types of Grid monitoring are around?  What user-level monitoring
-% provides and why we think it is good
+% What types of Grid monitoring are around and what the limitations are
 One approach to monitoring Grids, used by tools such as
@@
 high-level monitoring needed to detect user problems within the Grid
-infrastructure, such as incompatible software versions.  User-level
-Grid monitoring approaches testing is important because it run commands that users use and tests
-to see if they operate as expected. Execute commands published in user
-documentation, detect problems otherwise reported by users.
+infrastructure, such as incompatible software versions.
 
-so called user-level Grid monitoring is bIn our view, what was
-needed was a separate
-monitoring system to perform automated, periodic user-level Grid testing with
-the following features:
-User-level Grid monitoring is x and is valuable.  
-At that
-time, the only available user-level Grid monitoring tools were the NCSA
-TestGrid script [9] and GITS [10], scripts that run a fixed number of Grid
-tests and output results in HTML.  Although these tools were easy to install
-and produced useful information, they showed only the view of the Grid from a
-single resource, lacked automation, and were not easily extensible.
+% What user-level monitoring provides and why we think it is good
+User-level Grid monitoring approaches testing and performance measurement of
+the Grid infrastructure from the user perspective.  The goal is to act as an
+impartial test user of the Grid and detect problems with the infrastructure so
+they can be fixed before users notice them -- user complaints should not be
+the first indication of Grid failures.  We refer to an executable program that
+tests or measures some aspect of a system or installed software from the
+user-perspective as a reporter.  User-level Grid monitoring has the following
+characteristics:
+
+\begin{itemize}
+
+\item In order to reflect regular user experiences, tests or performance
+measurements of the Grid infrastructure should be done from a standard user
+account.  In fact, it is important to not execute under a system
+administrator's account because they may be privileged and often have custom
+shell initialization files.
+
+\item Also in order to reflect regular user experiences, tests should be
+written and configured using information directly from user documentation
+(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
+when documentation and testing are done in parallel in a pre-production
+environment but they should be closely coordinated activities.
+
+\item Since Grids are dynamic, user-level tests or performance measurements
+should be automated and executed periodically.
+
+\item Tests or performance measurements that interact with Grid services
+require authentication and should be executed using a standard user GSI
+credential that is mapped to the standard user account.
+
+\item Tests or performance measurements should be executed locally on all Grid
+resources when appropriate so that all Grid access points available to users
+are verified.  Similarly, it is important to executed some tests all-to-all
+in order to detect site-to-site configuration errors such as authentication
+problems.
+
+\end{itemize}
+
+\noindent In our experience, writing and maintaining user-level tests and
+performance measurements is an iterative refinement process since Grids are
+dynamic and the software environment changes over time as packages are
+upgraded.  It is also difficult to write and deploy a test perfectly the first
+time because of portability issues and sometimes incomplete user
+documentation.  For example, it may take a few iterations to determine whether
+detected failures are the result of a faulty test, fault user documentation,
+or a faulty system.  Realistically, this is a labor-intensive activity and
+thus the amount of user-level Grid monitoring is often limited by the amount
+of people resources that can be assiged to it.  However, A good goal is to
+test all the commands that exist in the user documentation and/or have at
+least one basic test for each software component of the Grid infrastructure.
 
@@
 % limitations.  We learned lessons from our TeraGrid deployment.  
-In 2003, SDSC, in partnership with TeraGrid, began developing the Inca
-monitoring tool to implement a user-level monitoring system with the above
-features and started using it to validate and verify that CTSS was deployed
-consistently across all TeraGrid resources and to monitor its status.  
-The initial version of Inca was implemented as a client-server architecture.
-It provided data collection, data storage (with limited archiving
-capabilities) that was accessible from a Web services interface, and data
-display though Web status pages.  Inca was first deployed to TeraGrid in mid
-2003 and released in late 2003. After running Inca 1 for a year and a half on
-TeraGrid, we learned some valuable lessons and designed Inca version 2, our
-current release.  Inca 2 contains a number of substantial improvements over
-Inca 1 with respect to security, installation and maintenance, and storage
-capabilities.  A pre-release of Inca 2 was provided in February 2006 and a
-beta release in November 2006.  A production version of Inca 2 was released in
-January 2007.  Currently, seven other Grids in the U.S., Europe, and Australia
-use Inca.
+In 2003, SDSC, in partnership with TeraGrid, began developing Inca
+1~\cite{inca1} to implement a user-level monitoring system with the above
+features and started using it to validate and
+verify that CTSS was deployed consistently across all TeraGrid resources and
+to monitor its status.  At that time, the only available user-level Grid
+monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
+GITS~\cite{gits}, scripts that run a fixed number of Grid tests and output
+results in HTML.  Although these tools were easy to install and produced
+useful information, they showed only the view of the Grid from a single
+resource, lacked automation, and were not easily extensible.  The initial
+version of Inca was implemented as a client-server architecture.  It provided
+data collection, data storage (with limited archiving capabilities) that was
+accessible from a Web services interface, and data display though Web status
+pages.  Inca was first deployed to TeraGrid in mid 2003 and released in late
+2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
+valuable lessons and designed Inca 2, our current release.  Inca 2
+contains a number of substantial improvements over Inca 1 with respect to
+security, installation and maintenance, and storage capabilities.  A
+production release of Inca 2 was provided in February 2007 and has been
+running on TeraGrid since November 2006.  Currently, seven other Grids in the
+U.S., Europe, and Australia use Inca.
 
 % This motivated our development of a new version of Inca.
-In the next section, we describe our experiences with deploying Inca 1 to
-TeraGrid and the lessons learned.  We then describe the Inca 2 architecture
-and the benefits it provides.  Use cases illustrate that Inca 2 is being used
-today and has great results.
+In the next section, we describe the features of Inca 2 and note which
+are new features based on our experiences with deploying Inca 1 on TeraGrid.
+We then describe the Inca 2 architecture and how it can be used to provide
+user-level Grid monitoring.  In Section~\ref{usecases}, we describe two 
+uses of Inca 2 for Grid software environment verification and benchmarking.  
+Finally, we describe some future work and summarize the paper.
 
-\Section{Features}
+%------------------------------------------------------------------------- 
+\Section{Inca 2 Features}
 
@@
 
-%------------------------------------------------------------------------- 
 %------------------------------------------------------------------------- 
@@
 \Section{Use Cases}
+\label{usecases}
 

### 2007-02-21 papers/hpdc-gmw-2007/paper.tex
small mods to arch figure and added arch intro
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6533 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\documentclass[times, 10pt,twocolumn]{article} 
+\documentclass[times,10pt,twocolumn]{article} 
 \usepackage{epsfig}
@@
 require the careful coordination of software packages, services, and
-configurations across multiple, heterogenous resources.  The TeraGrid
+configurations across multiple, heterogeneous resources.  The TeraGrid
 project~\cite{teragrid}, for example, manages the coordination of software and
@@
 and decide when software (including updates and patches) should be deployed to
-resources and how it should be configured for the set of heterogenous
+resources and how it should be configured for the set of heterogeneous
 resources.  Each site's system administrators, who are oftentimes not Grid
@@
 the Grid infrastructure from the user perspective.  The goal is to act as an
-impartial test user of the Grid and detect problems with the Grid
-infrastructure so they can be fixed before users notice them -- user
-complaints should not be the first indication of Grid failures.  User-level
-Grid monitoring has the following characteristics:
+impartial test user of the Grid and detect problems with the infrastructure so
+they can be fixed before users notice them -- user complaints should not be
+the first indication of Grid failures.  We refer to an executable program that
+tests or measures some aspect of a system or installed software from the
+user-perspective as a reporter.  User-level Grid monitoring has the following
+characteristics:
 
@@
 
-\item Tests or performance measurements of the Grid infrastructure should be
-done from a standard user account.  Tests executed by system administrators may
-not reflect regular user experiences because they run under privileged
-accounts that often have custom shell initialization files.
-System administrators may also configure tests using undocumented information
-(e.g., they know GridFTP server hostnames not in the user guide).
+\item In order to reflect regular user experiences, tests or performance
+measurements of the Grid infrastructure should be done from a standard user
+account.  In fact, it is important to not execute under a system
+administrator's account because they may be privileged and often have custom
+shell initialization files.
 
-\item Because the Grid infrastructure is dynamic, Tests or performance
-measurements should be executed periodically and automated.
+\item Also in order to reflect regular user experiences, tests should be
+written and configured using information directly from user documentation
+(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
+when documentation and testing are done in parallel in a pre-production
+environment but they should be closely coordinated activities.
 
-\item A user GSI credential should be issued and
-used by the monitoring system to test services that require authentication.
+\item Since Grids are dynamic, user-level tests or performance measurements
+should be automated and executed periodically.
 
-\item Tests should be executed locally on all Grid resources when appropriate
-so that all Grid access points available to users are tested.
+\item Tests or performance measurements that interact with Grid services
+require authentication and should be executed using a standard user GSI
+credential that is mapped to the standard user account.
 
-\item Also important to test some services from site to site.
+\item Tests or performance measurements should be executed locally on all Grid
+resources when appropriate so that all Grid access points available to users
+are verified.  Similarly, it is important to execute some tests all-to-all
+in order to detect site-to-site configuration errors such as authentication
+problems.
+
 \end{itemize}
-Amount of testing can vary and is oftentimes limited by the amount of
-reosurces that can be addressed to it.  A good approach is to test all the
-commands that exist in the user documentation or have at least one basic test
-for each software component of the Grid infrastructure.  
-commands that users use and tests to see if they operate as expected. Execute
-commands published in user
-documentation, detect problems otherwise reported by users.
 
-so called user-level Grid monitoring is bIn our view, what was
-needed was a separate
-monitoring system to perform automated, periodic user-level Grid testing with
-the following features:
-User-level Grid monitoring is x and is valuable.  
-At that
-time, the only available user-level Grid monitoring tools were the NCSA
-TestGrid script [9] and GITS [10], scripts that run a fixed number of Grid
-tests and output results in HTML.  Although these tools were easy to install
-and produced useful information, they showed only the view of the Grid from a
-single resource, lacked automation, and were not easily extensible.
+\noindent In our experience, writing and maintaining user-level tests and
+performance measurements is an iterative refinement process since Grids are
+dynamic and the software environment changes over time as packages are
+upgraded.  It is also difficult to write and deploy a test perfectly the first
+time because of portability issues and sometimes incomplete user
+documentation.  For example, it may take a few iterations to determine whether
+detected failures are the result of a faulty test, fault user documentation,
+or a faulty system.  Realistically, this is a labor-intensive activity and
+thus the amount of user-level Grid monitoring is often limited by the amount
+of people resources that can be assigned to it.  However, A good goal is to
+test all the commands that exist in the user documentation and/or have at
+least one basic test for each software component of the Grid infrastructure.
 
 % Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
-% limitations.  We learned lessons from our TeraGrid deployment.  
-In 2003, SDSC, in partnership with TeraGrid, began developing the Inca
-monitoring tool to implement a user-level monitoring system with the above
-features and started using it to validate and verify that CTSS was deployed
-consistently across all TeraGrid resources and to monitor its status.  
-The initial version of Inca was implemented as a client-server architecture.
-It provided data collection, data storage (with limited archiving
-capabilities) that was accessible from a Web services interface, and data
-display though Web status pages.  Inca was first deployed to TeraGrid in mid
-2003 and released in late 2003. After running Inca 1 for a year and a half on
-TeraGrid, we learned some valuable lessons and designed Inca version 2, our
-current release.  Inca 2 contains a number of substantial improvements over
-Inca 1 with respect to security, installation and maintenance, and storage
-capabilities.  A pre-release of Inca 2 was provided in February 2006 and a
-beta release in November 2006.  A production version of Inca 2 was released in
-January 2007.  Currently, seven other Grids in the U.S., Europe, and Australia
-use Inca.
+% limitations.  We learned lessons from our TeraGrid deployment and
+% developed Inca 2.
+In 2003, SDSC, in partnership with TeraGrid, began developing Inca
+1~\cite{inca1} to implement a user-level monitoring system with the above
+features and started using it to validate and
+verify that CTSS was deployed consistently across all TeraGrid resources and
+to monitor its status.  At that time, the only available user-level Grid
+monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
+GITS~\cite{gits}, scripts that run a fixed number of Grid tests and output
+results in HTML.  Although these tools were easy to install and produced
+useful information, they showed only the view of the Grid from a single
+resource, lacked automation, and were not easily extensible.  The initial
+version of Inca was implemented as a client-server architecture.  It provided
+data collection, data storage (with limited archiving capabilities) that was
+accessible from a Web services interface, and data display though Web status
+pages.  Inca was first deployed to TeraGrid in mid 2003 and released in late
+2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
+valuable lessons and designed Inca 2, our current release.  Inca 2
+contains a number of substantial improvements over Inca 1 with respect to
+security, installation and maintenance, and storage capabilities.  A
+production release of Inca 2 was provided in February 2007 and has been
+running on TeraGrid since November 2006.  Currently, seven other Grids in the
+U.S., Europe, and Australia use Inca.
 
 % This motivated our development of a new version of Inca.
-In the next section, we describe our experiences with deploying Inca 1 to
-TeraGrid and the lessons learned.  We then describe the Inca 2 architecture
-and the benefits it provides.  Use cases illustrate that Inca 2 is being used
-today and has great results.
+In the next section, we describe the features of Inca 2 and note which
+are new features based on our experiences with deploying Inca 1 on TeraGrid.
+We then describe the Inca 2 architecture and how it can be used to provide
+user-level Grid monitoring.  In Section~\ref{usecases}, we describe two 
+uses of Inca 2 for Grid software environment verification and benchmarking.  
+Finally, we describe some future work and summarize the paper.
 
-\Section{Features}
+%------------------------------------------------------------------------- 
+\Section{Inca 2 Features}
 
@@
 % Practical byproducts
+The goal of the Inca 2 design was to
 
@@
 
-~\newpage
-
-%------------------------------------------------------------------------- 
 %------------------------------------------------------------------------- 
@@
 
-\SubSection{Overview}
-% may not need to leave in here -- intro is assumed to be overview
-% Overview of all architecture components -- arch picture
-% move text to here I think
-1) The user creates a suite using incat and submits it to the agent
-
-2) The agent 
-    a) fetches reporters from the reporter repository
-    b) creates a reporter manager on each resource
-    c) sends the suite and reporters to each reporter manager.
-
-3) Each reporter manager executes reporters according to its schedule and
-sends results (reports) to the depot
-
-4) Data consumers display collected data (reports) by querying the depot
-
-\begin{figure*}[Htb]
+\begin{figure*}[htb]
   \centering
@@
 \end{figure*}
+
+% overview description of components
+Figure~\ref{arch_fig} shows the architecture of Inca 2 designed to implement
+the features described in the previous section.  Inca 2 is composed of 3 core
+components (in highlighted box):  the agent, depot, and reporter manager.
+The \textit{agent} and \textit{reporter managers} coordinate the execution of
+tests and performance measurements on the Grid resources and the
+\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
+or more \textit{reporter repositories} that contain user-level tests and
+benchmarks called \textit{reporters} and a configuration file describing how
+to execute them on the Grid resources created using an administration GUI tool
+called \textit{incat} (Inca Administration Tool).  The output or results
+collected from the resources are queried by the \textit{data consumer} and
+displayed to users.  The following steps describe how an Inca administrator
+would deploy user-level test and/or performance measurements to their
+resources.
+
+\begin{enumerate}
+\item The Inca administrator creates a deployment configuration file using
+incat and submits it to the agent.
+
+\item The agent
+  \begin{enumerate}
+    \item fetches reporters from the reporter repository
+    \item creates a reporter manager on each resource
+    \item sends the reporters and instruction for executed them to each reporter manager.
+  \end{enumerate}
+
+\item Each reporter manager executes reporters according to its schedule and
+sends results (reports) to the depot
+
+\item Data consumers display collected data (reports) by querying the depot
+\end{enumerate}
+
+\noindent The following subsections describe the Inca components in more
+detail in the order of the steps above.
 

### 2007-02-22 pubs/papers/hpdc-gmw-2007/paper.tex
mods to arch intro and added reporter subsection
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6538 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\documentclass[times, 10pt,twocolumn]{article} 
+\documentclass[times,10pt,twocolumn]{article} 
 \usepackage{epsfig}
 \usepackage{latex8}
+\usepackage{listings}
+\usepackage{subfigure}
 \usepackage{times}
@@
 tests or measures some aspect of a system or installed software from the
-user-perspective as a reporter.  User-level Grid monitoring has the following
-characteristics:
+user-perspective as a reporter.  In our view, the following guidelines 
+define user-level Grid monitoring:
 
@@
 resources when appropriate so that all Grid access points available to users
-are verified.  Similarly, it is important to executed some tests all-to-all
+are verified.  Similarly, it is important to execute some tests all-to-all
 in order to detect site-to-site configuration errors such as authentication
@@
 thus the amount of user-level Grid monitoring is often limited by the amount
-of people resources that can be assiged to it.  However, A good goal is to
+of people resources that can be assigned to it.  However, A good goal is to
 test all the commands that exist in the user documentation and/or have at
@@
 % Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
-% limitations.  We learned lessons from our TeraGrid deployment.  
+% limitations.  We learned lessons from our TeraGrid deployment and
+% developed Inca 2.
 In 2003, SDSC, in partnership with TeraGrid, began developing Inca
@@
 % Practical byproducts
+The goal of the Inca 2 design was to
 
-1.  Periodic tests executed by the monitoring system should be automated and
+\begin{enumerate}
+\item A reporter 
+\item logging in reporters
+\item Given the challenges of writing portable tests and benchmarks, Inca 2 
+includes a set of Perl APIs that provide convenience functions to simplify
+this process.
+
+\item Periodic tests executed by the monitoring system should be automated and
 run from a standard user account.  A user GSI credential should be issued and
@@
 %myproxy stuff
-2.  Tests should be executed locally on all Grid resources when appropriate so
+\item Tests should be executed locally on all Grid resources when appropriate so
 that all Grid access points available to users are tested.  
-3.  The configuration of tests should be managed centrally in order to ensure
+\item The configuration of tests should be managed centrally in order to ensure
 consistent testing of the resources, rather than by system administrators who
 may not use the same information that is available to users.
-4.  The testing system should easily adapt to new resources and testing
+\item The testing system should easily adapt to new resources and testing
 requirements.  In our experience, testing has an iterative refinement process
@@
 user documentation.   
-5.  System administrators should not need to know the details of the
+\item System administrators should not need to know the details of the
 monitoring system in order to troubleshoot problems.  When a problem is
@@
 sufficient information to locate the problem easily and test repairs.
-6.  A history of test results (especially any error messages) should be
+\item A history of test results (especially any error messages) should be
 retained in order to understand the behavior of their Grid over time. This
 history should be available through a flexible querying interface.
-7.  A running monitoring system should have a limited impact on the resources
+\item A running monitoring system should have a limited impact on the resources
 it measures and should be secure.
-
-~\newpage
+\end{enumerate}
 
 %------------------------------------------------------------------------- 
-\Section{Architecture}
+\Section{Inca 2 Architecture}
 
-\SubSection{Overview}
-% may not need to leave in here -- intro is assumed to be overview
-% Overview of all architecture components -- arch picture
-% move text to here I think
-1) The user creates a suite using incat and submits it to the agent
-
-2) The agent 
-    a) fetches reporters from the reporter repository
-    b) creates a reporter manager on each resource
-    c) sends the suite and reporters to each reporter manager.
-
-3) Each reporter manager executes reporters according to its schedule and
-sends results (reports) to the depot
-
-4) Data consumers display collected data (reports) by querying the depot
-
-\begin{figure*}[Htb]
+\begin{figure*}[htb]
   \centering
@@
 
+% overview description of components
+Figure~\ref{arch_fig} shows the architecture of Inca 2 designed to implement
+the features described in the previous section.  Inca 2 is composed of 3 core
+components (in highlighted box):  the agent, depot, and reporter manager.
+The \textit{agent} and \textit{reporter managers} coordinate the execution of
+tests and performance measurements on the Grid resources and the
+\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
+or more \textit{reporter repositories} that contain user-level tests and
+benchmarks called \textit{reporters} and a configuration file describing how
+to execute them on the Grid resources created using an administration GUI tool
+called \textit{incat} (Inca Administration Tool).  The output or results
+collected from the resources are queried by the \textit{data consumer} and
+displayed to users.  The following steps describe how an Inca administrator
+would deploy user-level test and/or performance measurements to their
+resources.
+
+\begin{enumerate}
+
+\item Using the guidelines described in the introduction, the Inca
+administrator either writes reporters to monitor their Grid or uses existing
+reporters in a published repository.
+
+\item The Inca administrator creates a deployment configuration file that
+describes the user-level monitoring for their Grid using incat and submits it
+to the agent.
+
+\item The agent
+  \begin{enumerate}
+    \item fetches reporters from the reporter repository
+    \item creates a reporter manager on each resource
+    \item sends the reporters and instruction for executed them to each reporter manager.
+  \end{enumerate}
+
+\item Each reporter manager executes reporters according to its schedule and
+sends results (reports) to the depot
+
+\item Data consumers display collected data (reports) by querying the depot
+\end{enumerate}
+
+\noindent The following subsections describe the Inca components in more
+detail using the order of the steps above.
+
+\SubSection{Reporters}
+
+\lstset{
+  basicstyle=\scriptsize\ttfamily, 
+  frame=single,
+  keywordstyle=\textbf, 
+  identifierstyle=, 
+  commentstyle=\scriptsize\ttfamily, 
+  stringstyle=\ttfamily, 
+  numbers=left, 
+  numberstyle=\scriptsize,
+  stepnumber=2,
+  firstnumber=1,
+  showstringspaces=false} 
+\begin{figure}
+\lstset{language=Perl} 
+\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
+\lstset{language=XML,keywordstyle={}} 
+\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
+\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
+availability of a Globus GRAM server and (b) its sample output.}
+\end{figure}
+
+An Inca reporter is an executable program that tests or measures some aspect
+of a system or installed software.   Reporter executables are designed to be
+easy to produce and can be run outside of the Inca system (e.g., by a system
+administrator).  A reporter should be written following the user-level
+monitoring guidelines described in the introduction and could be a simple
+Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
+or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
+support certain command line options and produce an XML report according to
+the Inca reporter schema.  The goal of the reporter schema is to accomodate
+multiple types of data and to capture information about the the reporter
+execution to diagnose any detected failures.  The reporter schema consists of
+the following elements:
+
+\begin{itemize}
+\item a set of header tags describing the context of the reporter
+execution:  GMT timestamp, hostname, reporter name, reporter version, working
+directory, reporter path, and arguments;
+\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
+\item a body containing the results expressed as any XML sequence; and
+\item an exit status tag
+indicating whether the reporter was able to complete its test or measurement
+and an optional error message.  
+\end{itemize} 
+\noindent Because the body of the report can be any XML sequence, it enables
+reporters to express a wide variety of information.  Today, we have four
+standard body schemas to express software version information, software
+functionality or service tests results, usage information, and performance
+results.
+
+We provide an extensible set of Perl APIs to handle much of the effort of
+writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
+pings a pre-WS Globus GRAM server and (b) its corresponding output when
+executed on a local machine.  The reporter uses two of the Perl APIs:
+Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
+Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
+functions for handling the required input arguments
+(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
+10-31) and printing the Inca-compliant header and exit status XML tags
+(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
+1-9,43-46).  It also includes some informational and debug logging functions
+again similar to log4j; the log output has been very useful to system
+administrators who can view a summary of the test or benchmark that the
+reporter performed without reading the reporter source code.  Line
+\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
+executes a system command (using a 30 second timeout) and logs to the 'system'
+level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
+Inca::Reporter::SimpleUnit is the API responsible for printing the simplist
+standard reporter body schema -- reporting software functionality or service
+tests results; it handles the printing of the small body XML
+(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
+(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
+18, 20) depending on the output of system command.  And finally, the
+Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
+dependency to the reporter which tells the Inca system to download a
+short-term proxy before running this reporter (this is discussed further in
+Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
+fewer than 30 lines of code.
+
+\SubSection{Reporter Repositories}
+
+The Inca agent retrieves reporters from collections called reporter
+repositories, that consist of reporters, required packages and libraries,
+and a catalog file. Repository contents are accessible using a URL and can
+be shared across multiple Inca deployments. The Inca team publishes a
+reporter repository that contains reporters developed for TeraGrid.
+
 \SubSection{Inca administration GUI tool (incat)}
 
+The Inca administrative GUI tool (incat) is the main interface by which an
+Inca administrator interacts with the Inca system.  Incat allows the Inca
+administrator to view the choose which resources to monitor and which tests or 
+benchmarks to deploy to those resources.  The following subsections
+describe the Inca components that are configurable via incat.  
 To configure reporter execution, an Inca administrator launches a GUI tool,
@@
 an application's requirements are being fulfilled on a Grid.
-
-\subsubsection{Reporters}
-
-Each Inca reporter is an executable program that tests or measures some
-aspect of a system or installed software.   Reporter executables are
-designed to be easy to produce and can be run outside of the Inca system
-(e.g., by a system administrator).  A reporter could be a simple Globus
-gatekeeper ping test (see Figure 2) or a more complex Grid application
-benchmark.  Reporters must support certain command line options and produce
-XML according to the Inca reporter schema.  The reporter schema requires a
-header describing the context of the reporter execution (e.g., reporter
-name, arguments, working directory, timestamp) and a body containing the
-results expressed as any XML sequence. This flexible body schema enables
-reporters to express a wide variety of information.  Today, we have three
-standard body schemas to express software version information, software
-functionality or service tests results, and usage information.  We provide
-Perl APIs to handle much of the effort of writing reporters.  Most current
-reporters use these APIs and consist of fewer than 30 lines of code.  
-% capture context of execution
-
-\subsubsection{Reporter Repositories}
-
-The Inca agent retrieves reporters from collections called reporter
-repositories, that consist of reporters, required packages and libraries,
-and a catalog file. Repository contents are accessible using a URL and can
-be shared across multiple Inca deployments. The Inca team publishes a
-reporter repository that contains reporters developed for TeraGrid.
 

### 2007-02-22 papers/hpdc-gmw-2007/paper.tex
word grammar pass
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6539 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \usepackage{latex8}
+\usepackage{listings}
+\usepackage{subfigure}
 \usepackage{times}
@@
 maintain Grid resources and scientists who use them.  First, system
-administration is distributed across multiple administrative domains which
-requires a significant amount of coordination.  This is typically performed by
+administration is distributed across multiple administrative domains 
+requiring a significant amount of coordination.  This is typically performed by
 a group of Grid operators who take into account local site policies 
@@
 
-1.  Periodic tests executed by the monitoring system should be automated and
+\begin{enumerate}
+\item A reporter 
+\item logging in reporters
+\item Given the challenges of writing portable tests and benchmarks, Inca 2 
+includes a set of Perl APIs that provide convenience functions to simplify
+this process.
+
+\item Periodic tests executed by the monitoring system should be automated and
 run from a standard user account.  A user GSI credential should be issued and
@@
 sufficient information to locate the problem easily and test repairs.
-6.  A history of test results (especially any error messages) should be
+\item A history of test results (especially any error messages) should be
 retained in order to understand the behavior of their Grid over time. This
 history should be available through a flexible querying interface.
-7.  A running monitoring system should have a limited impact on the resources
+\item A running monitoring system should have a limited impact on the resources
 it measures and should be secure.
+\end{enumerate}
 
 %------------------------------------------------------------------------- 
-\Section{Architecture}
+\Section{Inca 2 Architecture}
 
@@
 \begin{enumerate}
-\item The Inca administrator creates a deployment configuration file using
-incat and submits it to the agent.
+
+\item Using the guidelines described in the introduction, the Inca
+administrator either writes reporters to monitor their Grid or uses existing
+reporters in a published repository.
+
+\item The Inca administrator creates a deployment configuration file that
+describes the user-level monitoring for their Grid using incat and submits it
+to the agent.
 
@@
 \noindent The following subsections describe the Inca components in more
-detail in the order of the steps above.
+detail using the order of the steps above.
+
+\SubSection{Reporters}
+
+\lstset{
+  basicstyle=\scriptsize\ttfamily, 
+  frame=single,
+  keywordstyle=\textbf, 
+  identifierstyle=, 
+  commentstyle=\scriptsize\ttfamily, 
+  stringstyle=\ttfamily, 
+  numbers=left, 
+  numberstyle=\scriptsize,
+  stepnumber=2,
+  firstnumber=1,
+  showstringspaces=false} 
+\begin{figure}
+\lstset{language=Perl} 
+\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
+\lstset{language=XML,keywordstyle={}} 
+\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
+\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
+availability of a Globus GRAM server and (b) its sample output.}
+\end{figure}
+
+An Inca reporter is an executable program that tests or measures some aspect
+of a system or installed software.   Reporter executables are designed to be
+easy to produce and can be run outside of the Inca system (e.g., by a system
+administrator).  A reporter should be written following the user-level
+monitoring guidelines described in the introduction and could be a simple
+Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
+or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
+support certain command line options and produce an XML report according to
+the Inca reporter schema.  The goal of the reporter schema is to accommodate
+multiple types of data and to capture information about the reporter
+execution to diagnose any detected failures.  The reporter schema consists of
+the following elements:
+
+\begin{itemize}
+\item a set of header tags describing the context of the reporter
+execution:  GMT timestamp, hostname, reporter name, reporter version, working
+directory, reporter path, and arguments;
+\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
+\item a body containing the results expressed as any XML sequence; and
+\item an exit status tag
+indicating whether the reporter was able to complete its test or measurement
+and an optional error message.  
+\end{itemize} 
+\noindent Because the body of the report can be any XML sequence, it enables
+reporters to express a wide variety of information.  Today, we have four
+standard body schemas to express software version information, software
+functionality or service tests results, usage information, and performance
+results.
+
+We provide an extensible set of Perl APIs to handle much of the effort of
+writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
+pings a pre-WS Globus GRAM server and (b) its corresponding output when
+executed on a local machine.  The reporter uses two of the Perl APIs:
+Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
+Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
+functions for handling the required input arguments
+(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
+10-31) and printing the Inca-compliant header and exit status XML tags
+(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
+1-9,43-46).  It also includes some informational and debug logging functions
+again similar to log4j; the log output has been very useful to system
+administrators who can view a summary of the test or benchmark that the
+reporter performed without reading the reporter source code.  Line
+\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
+executes a system command (using a 30 second timeout) and logs to the 'system'
+level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
+Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
+standard reporter body schema -- reporting software functionality or service
+tests results; it handles the printing of the small body XML
+(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
+(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
+18, 20) depending on the output of system command.  And finally, the
+Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
+dependency to the reporter telling the Inca system to download a
+short-term proxy before running this reporter (this is discussed further in
+Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
+fewer than 30 lines of code.
+
+\SubSection{Reporter Repositories}
+
+The Inca agent retrieves reporters from collections called reporter
+repositories that consist of reporters, required packages and libraries,
+and a catalog file. Repository contents are accessible using a URL and can
+be shared across multiple Inca deployments. The Inca team publishes a
+reporter repository that contains reporters developed for TeraGrid.
 
@@
 
+The Inca administrative GUI tool (incat) is the main interface by which an
+Inca administrator interacts with the Inca system.  Incat allows the Inca
+administrator to view the choose which resources to monitor and which tests or 
+benchmarks to deploy to those resources.  The following subsections
+describe the Inca components that are configurable via incat.  
 To configure reporter execution, an Inca administrator launches a GUI tool,

### 2007-02-22 pubs/papers/hpdc-gmw-2007/paper.tex
small commit to test email to cathie
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6541 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 support certain command line options and produce an XML report according to
-the Inca reporter schema.  The goal of the reporter schema is to accomodate
-multiple types of data and to capture information about the the reporter
+the Inca reporter schema.  The goal of the reporter schema is to accommodate
+multiple types of data and to capture information about the reporter
 execution to diagnose any detected failures.  The reporter schema consists of
@@
 level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
-Inca::Reporter::SimpleUnit is the API responsible for printing the simplist
+Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
 standard reporter body schema -- reporting software functionality or service
@@
 (line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
-18, 20) depending on the output of system command.  And finally, the
+18, 20) depending on the output of system command.  Finally, the
 Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
-dependency to the reporter which tells the Inca system to download a
+dependency to the reporter telling the Inca system to download a
 short-term proxy before running this reporter (this is discussed further in
@@
 The Inca agent retrieves reporters from collections called reporter
-repositories, that consist of reporters, required packages and libraries,
+repositories that consist of reporters, required packages and libraries,
 and a catalog file. Repository contents are accessible using a URL and can

### 2007-02-22 pubs/papers/hpdc-gmw-2007/paper.tex
smooth over key reporter features
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6542 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 arise.  Well-defined requirements and good communication are required in this
-model.  Otherwise inconsistencies between the resources arise that can either
+model.  Otherwise inconsistencies between the resources arise that either
 inconvenience the user or prevent them from using particular resources
@@
 % Practical byproducts
-The goal of the Inca 2 design was to
+The main goal of the Inca 2 design was to XXX (general, flexible, easy to
+install, deploy, and
+maintain, scalable, secure).
+The following lists the key features of Inca 2 noting which are new features
+to Inca 1 versus improved.
 
 \begin{enumerate}
-\item A reporter 
-\item logging in reporters
-\item Given the challenges of writing portable tests and benchmarks, Inca 2 
-includes a set of Perl APIs that provide convenience functions to simplify
-this process.
+
+\item Collects a wide variety of user-level monitoring results (e.g., simple
+test data to more complex performance benchmark output).  (improved)
+
+\item Captures the context of a test or benchmark as it executes (e.g.,
+executable name, inputs, source host, etc.) so that system administrators have
+enough information to understand the result and can troubleshoot system
+problems without having to know the internals of Inca 2. (improved)
+
+\item Provides facilities to ease the process of writing test or benchmarks,
+deploying them into Inca 2 installations, and sharing them with other Inca 2
+users.
 
@@
 or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
-support certain command line options and produce an XML report according to
-the Inca reporter schema.  The goal of the reporter schema is to accommodate
-multiple types of data and to capture information about the reporter
-execution to diagnose any detected failures.  The reporter schema consists of
-the following elements:
+support certain command line options and produce an XML document or report
+according to the Inca reporter schema.  The goal of the reporter schema is to
+accommodate multiple types of data and to capture information about the
+reporter execution to diagnose any detected failures.  The reporter schema
+consists of the following elements:
 

### 2007-02-22 pubs/papers/hpdc-gmw-2007/kate.tex
some teragrid text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6543 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-02-22 papers/hpdc-gmw-2007/paper.tex
@@
 (line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
-18, 20) depending on the output of system command.  And finally, the
+18, 20) depending on the output of system command.  Finally, the
 Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
@@
 
+Inca has been deployed on TeraGrid since 2003 to validate and verify 
+its Common TeraGrid Software and Services (CTSS).  TeraGrid's common user 
+environment, supplied via the deployment and monitoring of CTSS, is 
+designed to allow users to more easily run Grid jobs across TeraGrid's 
+distributed, heterogeneous resources.
+
+In 2006, TeraGrid added reporters to collect job usage 
+information from Globus 2 GRAM logs and to detect expired host and CA 
+certificates and CA CRLs to its Inca deployment.
+
 \subsubsection{Usage of Inca}
@@
 
+In 2006, TeraGrid's Inca deployment transitioned over to Inca 2  
+and was deployed on 21 resources.   Each resource regularly executed 
+an average of 109 reporters to perform 48 cross-site, 20 grid, 
+28 cluster, 9 data, 2 user tool, and 2 security tests.
+
 \subsubsection{Results}
@@
 % Consumer view of CTSS, security, etc.
+
+TeraGrid currently has six status pages: a summary of software stack test failures, 
+a detailed grid of software test results, a page showing grid job usage, 
+results for security tests, results for secure mds tests, and a list of all 
+running reporters.
+
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[scale=0.5]{status-page.eps}
+  \caption{TeraGrid CTSS status page.}
+  \label{status_page_fig} 
+\end{figure}
 

### 2007-02-23 papers/hpdc-gmw-2007/kate.tex
tg revisions
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6546 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-02-22 pubs/papers/hpdc-gmw-2007/kate.tex
@@
 
-Inca has been deployed on TeraGrid since 2003 to validate and verify 
-its Common TeraGrid Software and Services (CTSS).  TeraGrid's common user 
-environment, supplied via the deployment and monitoring of CTSS, is 
-designed to allow users to more easily run Grid jobs across TeraGrid's 
-distributed, heterogeneous resources.
+TeraGrid's Coordinated TeraGrid Software and Services (CTSS)
+was designed to allow users to more easily run Grid jobs across its 
+distributed, heterogeneous resources.  CTSS is available 
+from all TeraGrid compute resources and is comprised of approximately 30 
+software packages for Grid services (gridftp, ws gram), Grid jobs (gridshell, myproxy, globus), 
+cluster tools (pacman, tgusage), data management (srb, hdf5) and 
+user applications (mpich, gcc).
 
-In 2006, TeraGrid added reporters to collect job usage 
+In order to validate and verify CTSS functionality from a user perspective, TeraGrid and SDSC 
+developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid transitioned to Inca 2 
+in 2006 and, in addition to CTSS monitoring, began using Inca to collect job usage 
 information from Globus 2 GRAM logs and to detect expired host and CA 
@@
 
-In 2006, TeraGrid's Inca deployment transitioned over to Inca 2  
-and was deployed on 21 resources.   Each resource regularly executed 
+TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on sapa.sdsc.edu, 
+a XX machine.  A reporter repository for TeraGrid is also hosted at SDSC 
+on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources each 
+run a reporter manager and regularly execute
 an average of 109 reporters to perform 48 cross-site, 20 grid, 

### 2007-02-23 pubs/papers/hpdc-gmw-2007/paper.tex
merge tg section into paper.tex
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6547 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
+TeraGrid's Coordinated TeraGrid Software and Services (CTSS) was designed to
+allow users to more easily run Grid jobs across its distributed, heterogeneous
+resources.  CTSS is available from all TeraGrid compute resources and is
+comprised of approximately 30 software packages for Grid services (gridftp, ws
+gram), Grid jobs (gridshell, myproxy, globus), cluster tools (pacman, tgusage),
+data management (srb, hdf5) and user applications (mpich, gcc).
+
+In order to validate and verify CTSS functionality from a user perspective,
+TeraGrid and SDSC developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid
+transitioned to Inca 2 in 2006 and, in addition to CTSS monitoring, began using
+Inca to collect job usage information from Globus 2 GRAM logs and to detect
+expired host and CA certificates and CA CRLs to its Inca deployment.
+
 \subsubsection{Usage of Inca}
@@
 
+TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
+sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
+at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
+each run a reporter manager and regularly execute an average of 109 reporters
+to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
+security tests.
+
 \subsubsection{Results}
@@
 % Consumer view of CTSS, security, etc.
+
+TeraGrid currently has six status pages: a summary of software stack test
+failures, a detailed grid of software test results, a page showing grid job
+usage, results for security tests, results for secure mds tests, and a list of
+all running reporters.
+
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[scale=0.5]{status-page.eps}
+  \caption{TeraGrid CTSS status page.}
+  \label{status_page_fig}
+\end{figure}
 

### 2007-02-23 papers/hpdc-gmw-2007/paper.tex
new reporter repositories section and some features sections
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6549 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-%\documentstyle[times,art10,twocolumn,latex8]{article}
+% Uncomment to check text length -- moves figures to end of paper -- no more
+% than 10 % pages w/o figures
+%\usepackage{endfloat}
 
@@
 % take the % away on next line to produce the final camera-ready version 
+% takes away page numbers
 \pagestyle{empty}
@@
 
+\item The configuration of tests or performance measurements should be managed
+centrally in order to ensure consistent testing of the resources, rather than
+by system administrators who may not use the same information that is
+available to users.
+
 \end{itemize}
@@
 thus the amount of user-level Grid monitoring is often limited by the amount
-of people resources that can be assigned to it.  However, A good goal is to
+of people resources that can be assigned to it.  However, a good goal is to
 test all the commands that exist in the user documentation and/or have at
@@
 % Practical byproducts
-The goal of the Inca 2 design was to
+The main goal of the Inca 2 design was to XXX (general, flexible, easy to
+install, deploy, and
+maintain, scalable, secure).
+The following lists the key features of Inca 2 noting which are new features
+to Inca 1 versus improved.
 
 \begin{enumerate}
-\item A reporter 
-\item logging in reporters
-\item Given the challenges of writing portable tests and benchmarks, Inca 2 
-includes a set of Perl APIs that provide convenience functions to simplify
-this process.
 
-\item Periodic tests executed by the monitoring system should be automated and
-run from a standard user account.  A user GSI credential should be issued and
-used by the monitoring system to test services that require authentication.  
+\item Collects a wide variety of user-level monitoring results (e.g., simple
+test data to more complex performance benchmark output).  (improved)
+
+\item Captures the context of a test or benchmark as it executes (e.g.,
+executable name, inputs, source host, etc.) so that system administrators have
+enough information to understand the result and can troubleshoot system
+problems without having to know the internals of Inca 2. (improved)
+
+\item Provides facilities to ease the process of writing tests or benchmarks
+and deploying them into Inca 2 installations. (improved)
+
+\item Provides facilities for sharing tests or benchmarks with other Inca 2
+users in order to promote sharing of each other's expertise (new)
+
+\item Easily adapts to new resources and monitoring requirements in order to
+facilitate maintenance of a running Inca 2 deployment. (improved)
+
+\item Stores and archives monitoring results (especially any error messages) 
+in order to understand the behavior of a Grid over time. The results
+are available through a flexible querying interface. (improved)
+
 %myproxy stuff
-\item Tests should be executed locally on all Grid resources when appropriate so
-that all Grid access points available to users are tested.  
-\item The configuration of tests should be managed centrally in order to ensure
-consistent testing of the resources, rather than by system administrators who
-may not use the same information that is available to users.
-\item The testing system should easily adapt to new resources and testing
-requirements.  In our experience, testing has an iterative refinement process
-because Grids are dynamic and the software environment changes over time as
-packages are upgraded.  Furthermore, it is often difficult to write and deploy
-a test perfectly the first time because of portability issues and incomplete
-user documentation.   
-\item System administrators should not need to know the details of the
-monitoring system in order to troubleshoot problems.  When a problem is
-detected the monitoring system should provide system administrators with
-sufficient information to locate the problem easily and test repairs.
-\item A history of test results (especially any error messages) should be
-retained in order to understand the behavior of their Grid over time. This
-history should be available through a flexible querying interface.
 \item A running monitoring system should have a limited impact on the resources
@@
 \caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
-availability of a Globus GRAM server and (b) its sample output.}
+availability of a Globus GRAM server and (b) an output sample.}
 \end{figure}
@@
 
-The Inca agent retrieves reporters from collections called reporter
-repositories that consist of reporters, required packages and libraries,
-and a catalog file. Repository contents are accessible using a URL and can
-be shared across multiple Inca deployments. The Inca team publishes a
-reporter repository that contains reporters developed for TeraGrid.
+% What are repositories and their key features
+Reporter repositories are collections that consist of reporters, required
+packages and libraries (including the Perl APIs described in the previous
+section), and a catalog file.  Repository contents are accessible using a URL
+and designed to be shared across multiple Inca deployments.  The catalog file
+follows APT's Packages.gz~\cite{apt} format and thus tar.gz dependencies such
+as non-standard Perl APIs or source code can be added to reporter catalog
+entries.  Inca will then automatically deploy tar.gz dependencies into a
+subdirectory of its installation (more in Section~\ref{agent}).  This enables
+reporters to be deployed to resources with a miniumum of effort.  Furthermore,
+each package specified in the catalog is versioned.  This allows Inca to
+automatically distribute reporter code updates such as bug fixes.  As such,
+Inca administrators maintaining repositories need to be careful to ensure
+their updates are tested and work.
+% XXX Check with Jim on that
+
+% We have a lot of reporters ready to be picked 
+The Inca team publishes a reporter repository that contains 143 reporters
+developed and tested for TeraGrid.  Most reporters are either version
+reporters that collect version information from a softare package and
+serve as a most basic unit test, unit test reporters that run a more involved
+unit test, or performance benchmark reporters.  The unit and version
+reporters cover software such as Grid middleware, compilers, math libraries,
+data tools, and visualization tools.  The performance reporters available
+currently measure data transfer and execute Grid benchmarks as described in
+Section~\ref{grasp}.
 

### 2007-02-23 papers/hpdc-gmw-2007/paper.tex
better figure image, remove machine type
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6550 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
-sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
-at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
+sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
+at SDSC on login-linux.sdsc.edu.  TeraGrid's 20 compute resources
 each run a reporter manager and regularly execute an average of 109 reporters
@@
 
-TeraGrid currently has six status pages: a summary of software stack test
-failures, a detailed grid of software test results, a page showing grid job
+TeraGrid currently has six status pages: a summary of CTSS test
+failures, a detailed grid of CTSS test results, a page showing grid job
 usage, results for security tests, results for secure mds tests, and a list of
 all running reporters.
+
+Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSS test result
+page.  CTSS software packages are listed along the column and TeraGrid
+resources (anonymized) in the header rows.  Test results for each package and
+resource are shown in the table body rows.
 

### 2007-02-24 pubs/papers/hpdc-gmw-2007/paper.tex
tg deployment and text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6551 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\item Provides facilities to ease the process of writing test or benchmarks,
-deploying them into Inca 2 installations, and sharing them with other Inca 2
-users.
+\item Provides facilities to ease the process of writing tests or benchmarks
+and deploying them into Inca 2 installations. (improved)
 
-\item Periodic tests executed by the monitoring system should be automated and
-run from a standard user account.  A user GSI credential should be issued and
-used by the monitoring system to test services that require authentication.  
+\item Provides facilities for sharing tests or benchmarks with other Inca 2
+users in order to promote sharing of each other's expertise (new)
+
+\item Easily adapts to new resources and monitoring requirements in order to
+facilitate maintenance of a running Inca 2 deployment. (improved)
+
+\item Stores and archives monitoring results (especially any error messages) 
+in order to understand the behavior of a Grid over time. The results
+are available through a flexible querying interface. (improved)
+
 %myproxy stuff
-\item Tests should be executed locally on all Grid resources when appropriate so
-that all Grid access points available to users are tested.  
-\item The configuration of tests should be managed centrally in order to ensure
-consistent testing of the resources, rather than by system administrators who
-may not use the same information that is available to users.
-\item The testing system should easily adapt to new resources and testing
-requirements.  In our experience, testing has an iterative refinement process
-because Grids are dynamic and the software environment changes over time as
-packages are upgraded.  Furthermore, it is often difficult to write and deploy
-a test perfectly the first time because of portability issues and incomplete
-user documentation.   
-\item System administrators should not need to know the details of the
-monitoring system in order to troubleshoot problems.  When a problem is
-detected the monitoring system should provide system administrators with
-sufficient information to locate the problem easily and test repairs.
-\item A history of test results (especially any error messages) should be
-retained in order to understand the behavior of their Grid over time. This
-history should be available through a flexible querying interface.
 \item A running monitoring system should have a limited impact on the resources
@@
 TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
-sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
-at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
+sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
+at SDSC on login-linux.sdsc.edu.  TeraGrid's 19 compute resources
 each run a reporter manager and regularly execute an average of 109 reporters
 to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
-security tests.
+security tests.  Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 
+deployment configuration.
+
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[scale=0.6]{tg-deploy.eps}
+  \caption{TeraGrid's Inca 2 Deployment.}
+  \label{tg_deploy_fig}
+\end{figure}
 
@@
 
-TeraGrid currently has six status pages: a summary of software stack test
-failures, a detailed grid of software test results, a page showing grid job
+TeraGrid currently has six status pages: a summary of CTSS test
+failures, a detailed grid of CTSS test results, a page showing grid job
 usage, results for security tests, results for secure mds tests, and a list of
@@
 
+Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSS test result
+page.  CTSS software packages are listed along the column and TeraGrid
+resources (anonymized) in the header rows.  Test results for each package and
+resource are shown in the table body rows.
+
 \begin{figure}[hbt]
   \centering
-  \includegraphics[scale=0.5]{status-page.eps}
+  \includegraphics[scale=0.4]{status-page.eps}
   \caption{TeraGrid CTSS status page.}

### 2007-02-24 pubs/papers/hpdc-gmw-2007/paper.tex
could changes to the intro - still not sure about how to nicely say the sys admins might not be grid experts...
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6552 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 resources and how it should be configured for the set of heterogeneous
-resources.  Each site's system administrators, who are oftentimes not Grid
+resources.  Each site's system administrators, who are not necessarily Grid
 experts, are then responsible for providing the required Grid software
@@
 examined.  This type of monitoring information is useful for showing the
-utilization of Grid resources, however, it does not provide the type of
+utilization of Grid resources but it does not provide the type of
 high-level monitoring needed to detect user problems within the Grid
@@
 they can be fixed before users notice them -- user complaints should not be
-the first indication of Grid failures.  We refer to an executable program that
-tests or measures some aspect of a system or installed software from the
-user-perspective as a reporter.  In our view, the following guidelines 
+the first indication of Grid failures.  In our view, the following guidelines 
 define user-level Grid monitoring:

### 2007-02-25 pubs/papers/hpdc-gmw-2007/paper.tex
additions to arch section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6553 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \usepackage{url}
-
-% Uncomment to check text length -- moves figures to end of paper -- no more
-% than 10 % pages w/o figures
-%\usepackage{endfloat}
 
@@
 
-\SubSection{Inca administration GUI tool (incat)}
+\SubSection{Inca administration tool (incat)}
+%\begin{figure}[htb]
+%  \centering
+%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
+%  \caption{\label{arch_fig} Incat .}
+%\end{figure}
 
-The Inca administrative GUI tool (incat) is the main interface by which an
-Inca administrator interacts with the Inca system.  Incat allows the Inca
-administrator to view the choose which resources to monitor and which tests or 
-benchmarks to deploy to those resources.  The following subsections
-describe the Inca components that are configurable via incat.  
-To configure reporter execution, an Inca administrator launches a GUI tool,
-called incat.  Incat allows the administrator to choose which resources to
-monitor and which reporters to deploy to those resources.  For each
-reporter, the administrator can specify the resources to run on,
-command-line arguments, the runtime environment, the frequency of execution,
-and resource limits. The Inca administrator may also group related reporters
-into suites that can be shared across different Inca deployments.  This can
-be useful to determine interoperability among Grids or to determine whether
-an application's requirements are being fulfilled on a Grid.
+% Incat is interface Inca admin uses to configure reporters to resources
+% introduce series here; why suites are important It is designed to make the
+% effort of configuring and maintaining 100s series on resources easilty
+The Inca administrative tool (incat) is a GUI implemented in Java Swing an
+Inca administrator uses to configure user-level Grid monitoring on their
+resources.  Incat allows an Inca administrator to choose which resources to
+monitor and which reporters to deploy to those resources.  The configuration
+is stored in a XML file and sent to the agent which handles the implementation
+(as described in the next section).  The Inca administrator can reload the
+configuration at any point and make updates.  Incat provides a number of
+conveniences that enable a large number of results to be managed and collected
+with a minimum effort.
 
-\subsubsection{Suites}
-%\subsubsection{Series}
+Once an Inca administrator enters the location of one more reporter
+repositories, incat will load and display the reporters available from them.
+For each reporter, the Inca administrator can specify the resources to run on,
+input arguments, the runtime environment, the frequency of execution, resource
+limits, and email notifications.  The reports that a reporter produces on a
+resource when executed with specific set of input arguments and runtime
+environment are known as a \emph{report series} (or \emph{series} for short).
+Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
+produce one report series when executed with host tg-login.sdsc.edu and
+another report series when executed with dslogin.sdsc.edu.  A set of related
+series can be grouped into \emph{suites} and shared across other Inca
+deployments.  For example, there could be a Globus suite or a data transfer
+performance suite.  Suites can also be useful to determine interoperability
+among Grids or to determine whether an application's requirements are being
+fulfilled on a Grid.
 
-\subsubsection{Resource Macros}
+% Resource information organized to make it easier to maintain
+For each monitored resource, an Inca administrator selects an access method
+(SSH or Globus) to access the resource and start monitoring there (described
+in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
+together and referenced in the series configuration.  This facilitates the
+process of executing the same series on multiple resources.  Furthermore,
+attributes called \emph{macros} can be attached to resources and resource
+groups and similarly be referenced in the series configuration (i.e., inputs
+and runtime environment).  For example, it is useful to have a macro called
+'jobmanager' since the batch system is likely to differ from one machine to
+the next.  A resource macro can also have multiple values in which case the
+series will be executed on the resource once for each macro value.  The
+benefit of resource groups and macros is that when a reporter is executed on a
+resource multiple times with different input arguments, it can be represented
+succintly.  Similarly, when a resource attribute is changed, it only has to be
+changed in one place and then every series that references it will be updated
+as well.  This makes the initial configuration and maintenance easier on the
+Inca administrator and less error prone.
 
@@
 The Inca agent is a server that implements the configuration specified by the
-Inca administrator.  After determining which Inca tests should be executed on
-each resource, the agent stores this configuration information in the depot.
-It then stages and launches a dependent component, called a reporter manager,
-on each resource using either SSH or Globus [13].  Once a reporter manager
-contacts its agent, the agent transmits Inca tests to execute, along with
-their dependencies, configuration and schedule of execution.
+Inca administrator.  When it receives a configuration file from the Inca
+administrator, it will determine which reporters should be executed on each
+resource by expanding the resource macros and groups; it then stores the
+expanded configuration information in the depot.  The agent stages and
+launches an Inca component, called a reporter manager (described in the
+following subsection), on each resource using either SSH or Globus.  Once a
+reporter manager contacts its agent, the agent transmits the reporters to
+execute along with their dependencies and a suite that contains their series
+configuration and schedule of execution.  As an Inca administrator makes
+updates to the configuration, the agent will push out new reporters and/or
+suite changes to each of the effected resources.
+
+To maintain the Inca deployment, the agent regularly pings the reporter
+managers on each resource in order to detect when a reporter manager has
+failed so it can be restarted.  For example, if a resource goes down for a
+planned maintenance, the agent will attempt to restart the reporter manager
+(by default every hour) until it succeeds.  The agent also maintains a local
+cache of reporters and their dependencies; it periodically checks the
+repositories for updates every 4 hours by default and automatically
+distributes them to the reporter managers (if the latest version is desired).  
+The agent is implemented in Java.
+
+% myproxy
 
@@
 The Inca reporter manager is a lightweight process responsible for managing
-the schedule and execution of Inca tests, called reporters, on a single
-resource. The reporter manager receives reporter updates and dependencies
-(e.g., Inca Perl APIs or source code) from the agent along with requests for
-reporter scheduling changes.  Running under a regular user account, the
-reporter manager executes reporters on-demand or using an internal cron
-scheduler, and sends reports to the depot for archiving. The reporter
-manager monitors reporter system usage and enforces limits (e.g., wall clock
-time, CPU time, memory).  System usage information is sent to the depot with
-each report.
+the schedule and execution of Inca reporters on a single resource. The
+reporter manager receives reporter updates and dependencies from the agent
+along with requests for reporter scheduling changes.  Running under a regular
+user account, the reporter manager executes reporters on-demand or using an
+internal cron scheduler, and sends reports to the depot for archiving. The
+reporter manager monitors reporter system usage using the system command
+\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
+System usage information is sent to the depot with each report.
+
+The reporter manager is implemented in Perl since it is available by default
+on UNIX machines.  The cron scheduling is implemented using the CPAN perl
+module Schedule::Cron.
 
@@
 
-The Inca depot server is responsible for storing configuration information
-and the data produced by reporters. The depot maintains a relational
-database via Hibernate [14] so that it can use a variety of databases.  The
+The Inca depot server is responsible for storing configuration information and
+the data produced by reporters. The depot uses a relational database via
+Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
 depot provides full archiving of reporter output and structures its schema
-to reduce redundant data.  Data can be queried using SQL queries. Predefined
-queries exist to return the latest report instances of a suite, a single
-report instance, or a report history.  A Web services interface is also
-available to provide unauthenticated query access to data.
+around series and the minimization of redundant data, i.e., only stores
+changes from one report to another in a report series.  The depot also
+supports comparisons which are executed on a newly received report; 
+currently regular expression matching and version comparisons are 
+supported.  Optionally, an Inca administrator can select to receive
+email notification when the result of the comparison changes.
+
+Data can be queried using SQL queries. Predefined queries exist to return the
+latest report instances of a suite, a single report instance, or a report
+history.  A Web services interface is also available to provide
+unauthenticated query access to data.  The depot is implemented in Java.
 
@@
 The Inca data consumer is a Web application that queries the Inca depot for
-data and displays it in a user-friendly format.  The data consumer is
-packaged with Jetty [15] so that pages can be served immediately without
-deploying Tomcat [16].  A set of JSP tags and pages query the Inca depot for
-data (returned as XML) and a set of XSL stylesheets format the data as HTML.
+data and displays it in a user-friendly format.  The data consumer is packaged
+with Jetty~\cite{jetty} so that pages can be served out of the box.  A set of
+extensible JSP tags and pages query the Inca depot for data (returned as XML)
+and a set of XSL stylesheets format the data as HTML.  An Inca administrator
+can customize the data display by either modifying the XSL stylesheets or
+writing their own JSP tags and pages.
 
-~\newpage
-~\newpage
-~\newpage
+\SubSection{Security}
+
+To reduce the security risk of Inca, all Inca components communicate with each
+other using SSL by default.  Also, sensitive information such as passwords are
+encrypted before being stored to disk on the agent.  To handle reporters that
+require a valid proxy credential to execute, the reporter manager will fetch a
+short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
+administrator) and then destroys the proxy once the reporter has completed.
+The goal is to only have short-term proxies on the machine for the times at
+which they are neeed; this is more secure than maintaining a long-term
+credential on the resource and easier to manage.  Furthermore, the MyProxy
+authentication information is fetched from the agent each time a proxy
+credential is needed and then cleared from memory.
+
+\SubSection{Scalability}
+
 ~\newpage
@@
 sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
-at SDSC on login-linux.sdsc.edu.  TeraGrid's 19 compute resources
+at SDSC on inca.sdsc.edu.  TeraGrid's 19 compute resources
 each run a reporter manager and regularly execute an average of 109 reporters
@@
 \end{figure}
-
-~\newpage
 

### 2007-02-26 papers/hpdc-gmw-2007/paper.tex
modifications to TeraGrid section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6555 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-02-23 papers/hpdc-gmw-2007/paper.tex
@@
 
-\subsubsection{Description and Requirements}
+% Description and Requirements - Describe CTSS
+Requirements for user-level Grid monitoring on TeraGrid initially included the
+validation and verification of CTSS on each resource.  As described in the
+introduction, CTSS was designed to
+allow users to more easily run Grid jobs across its distributed, heterogeneous
+resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
+resources and is comprised of approximately 30 software packages that provide
+Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
+tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
+Inca was originally
+deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
+November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
+to collect job usage information from Globus 2 GRAM logs and to detect expired
+host and CA certificates and CA CRLs.
 
-% Describe CTSS
+% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
+To provide user-level monitoring of CTSSv3, a number of version and unit
+test reporters were developed to test the software packages in CTSS.
+Currently, there are 56 such reporters executing an average of 109 series on
+each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
+GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
+application tool-related tests, and 2 security-related tests.  
+Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
+configuration.  The
+agent, depot and consumer components are hosted at SDSC on 
+sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
+at SDSC on inca.sdsc.edu.
 
-TeraGrid's Coordinated TeraGrid Software and Services (CTSS) was designed to
-allow users to more easily run Grid jobs across its distributed, heterogeneous
-resources.  CTSS is available from all TeraGrid compute resources and is
-comprised of approximately 30 software packages for Grid services (gridftp, ws
-gram), Grid jobs (gridshell, myproxy, globus), cluster tools (pacman, tgusage),
-data management (srb, hdf5) and user applications (mpich, gcc).
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[scale=0.6]{tg-deploy.eps}
+  \caption{TeraGrid's Inca 2 Deployment.}
+  \label{tg_deploy_fig}
+\end{figure}
 
-In order to validate and verify CTSS functionality from a user perspective,
-TeraGrid and SDSC developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid
-transitioned to Inca 2 in 2006 and, in addition to CTSS monitoring, began using
-Inca to collect job usage information from Globus 2 GRAM logs and to detect
-expired host and CA certificates and CA CRLs to its Inca deployment.
-
-\subsubsection{Usage of Inca}
-
-% Describe reporters, configuration, and deployment.  Figure.
-
-TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
-sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
-at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
-each run a reporter manager and regularly execute an average of 109 reporters
-to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
-security tests.
-
-\subsubsection{Results}
-
-% Consumer view of CTSS, security, etc.
-
-TeraGrid currently has six status pages: a summary of software stack test
-failures, a detailed grid of software test results, a page showing grid job
+% Results - Consumer view of CTSS, security, etc.
+TeraGrid currently has six status pages to display the Inca monitoring
+information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
+results, a page showing grid job
 usage, results for security tests, results for secure mds tests, and a list of
@@
 
+Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSSv3 
+test result
+page.  CTSSv3 software packages are listed along the column and TeraGrid
+resources (anonymized) in the header rows.  Test results for each package and
+resource are shown in the table body rows.
+
 \begin{figure}[hbt]
   \centering
-  \includegraphics[scale=0.5]{status-page.eps}
-  \caption{TeraGrid CTSS status page.}
+  \includegraphics[scale=0.4]{status-page.eps}
+  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
+  resources anonymized.}
   \label{status_page_fig}
 \end{figure}
-
-~\newpage
 

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
global grammar edits
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6557 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 requiring a significant amount of coordination.  This is typically performed by
-a group of Grid operators who take into account local site policies 
+a group of Grid administrators or operators who consider local site policies and
+resource heterogeneity
 and decide when software (including updates and patches) should be deployed to
-resources and how it should be configured for the set of heterogeneous
-resources.  Each site's system administrators, who are not necessarily Grid
+resources and how it should be configured.  
+Each site's system administrators, who are not necessarily Grid
 experts, are then responsible for providing the required Grid software
@@
 inconvenience the user or prevent them from using particular resources
-together.  Second, as a large distributed system, failures will occur over
+together.  A second challenge is that failures will occur over
 time in the Grid services due to network or system failures, software
-misconfiguration, or software bugs.  In order to detect such problems, 
-monitoring of the resources is required.
+misconfiguration, or software bugs.  In order to address these challenges,
+Grid monitoring can be used to detect such problems leading to a more
+stable and dependable Grid infrastructure.
 
@@
 display data from existing cluster or system administrator monitoring tools
-such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, and
+such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
 Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
@@
 detected failures are the result of a faulty test, fault user documentation,
-or a faulty system.  Realistically, this is a labor-intensive activity and
-thus the amount of user-level Grid monitoring is often limited by the amount
-of people resources that can be assigned to it.  However, a good goal is to
-test all the commands that exist in the user documentation and/or have at
-least one basic test for each software component of the Grid infrastructure.
+or a faulty system.  As such, this can be a labor-intensive activity and
+therefore difficult to achieve full test coverage.  In practice, 
+either
+testing all the commands that exist in the user documentation and/or having at
+least one basic test for each software component of the Grid infrastructure
+achieves a reasonable subset of testing.
 
@@
 In 2003, SDSC, in partnership with TeraGrid, began developing Inca
-1~\cite{inca1} to implement a user-level monitoring system with the above
+1~\cite{inca1} to implement a user-level Grid monitoring system with the above
 features and started using it to validate and
@@
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
-GITS~\cite{gits}, scripts that run a fixed number of Grid tests and output
+GITS~\cite{gits}, scripts that ran a fixed number of Grid tests and formatted
 results in HTML.  Although these tools were easy to install and produced
-useful information, they showed only the view of the Grid from a single
+useful information, they showed the view of the Grid from a single
 resource, lacked automation, and were not easily extensible.  The initial
@@
 accessible from a Web services interface, and data display though Web status
-pages.  Inca was first deployed to TeraGrid in mid 2003 and released in late
+pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
 2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
@@
 % This motivated our development of a new version of Inca.
-In the next section, we describe the features of Inca 2 and note which
-are new features based on our experiences with deploying Inca 1 on TeraGrid.
+In the next section, we describe the design goals and features of Inca 2. 
 We then describe the Inca 2 architecture and how it can be used to provide
@@
 maintain, scalable, secure).
+Inca benefits ...
 The following lists the key features of Inca 2 noting which are new features
@@
 enough information to understand the result and can troubleshoot system
-problems without having to know the internals of Inca 2. (improved)
+problems without having to know the internals of Inca. (improved)
 
-\item Provides facilities to ease the process of writing tests or benchmarks
-and deploying them into Inca 2 installations. (improved)
+\item Eases the process of writing tests or benchmarks and deploying them into
+Inca installations. (improved)
 
-\item Provides facilities for sharing tests or benchmarks with other Inca 2
+\item Provides means for sharing tests or benchmarks with other Inca 
 users in order to promote sharing of each other's expertise (new)
@@
 \item Easily adapts to new resources and monitoring requirements in order to
-facilitate maintenance of a running Inca 2 deployment. (improved)
+facilitate maintenance of a running Inca deployment. (improved)
 
@@
 
-%myproxy stuff
-\item A running monitoring system should have a limited impact on the resources
-it measures and should be secure.
+\item Securely manages short-term proxies for testing of Grid services using
+MyProxy~\cite{myproxy}.
+
+\item Measures the system impact of tests and benchmarks executing on
+the monitored resources in order to tune their execution frequency to
+reduce the impact on the resources.
+
 \end{enumerate}
@@
     \item creates a reporter manager on each resource
-    \item sends the reporters and instruction for executed them to each reporter manager.
+    \item sends the reporters and instructions for executing them to each reporter manager.
   \end{enumerate}
@@
 easy to produce and can be run outside of the Inca system (e.g., by a system
-administrator).  A reporter should be written following the user-level
+administrator).  A reporter should be written using the user-level
 monitoring guidelines described in the introduction and could be a simple
@@
 or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
-support certain command line options and produce an XML document or report
+support certain command line options and produce an XML document or
+\emph{report}
 according to the Inca reporter schema.  The goal of the reporter schema is to
-accommodate multiple types of data and to capture information about the
+accommodate multiple types of data and to capture enough information about the
 reporter execution to diagnose any detected failures.  The reporter schema
@@
 
-We provide an extensible set of Perl APIs to handle much of the effort of
+An extensible set of Perl APIs is provided to handle much of the effort of
 writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
@@
 (lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
-1-9,43-46).  It also includes some informational and debug logging functions
+1-9, 43-46).  It also includes some informational and debug logging functions
 again similar to log4j; the log output has been very useful to system
@@
 short-term proxy before running this reporter (this is discussed further in
-Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
-fewer than 30 lines of code.
+Section~\ref{security}).  Most current reporters use the Perl APIs and consist
+of fewer than 30 lines of code.
 
@@
 subdirectory of its installation (more in Section~\ref{agent}).  This enables
-reporters to be deployed to resources with a miniumum of effort.  Furthermore,
+reporters to be deployed to resources with a minimum of effort.  Furthermore,
 each package specified in the catalog is versioned.  This allows Inca to
@@
 their updates are tested and work.
-% XXX Check with Jim on that
 
@@
 developed and tested for TeraGrid.  Most reporters are either version
-reporters that collect version information from a softare package and
+reporters that collect version information from a software package and
 serve as a most basic unit test, unit test reporters that run a more involved
@@
 % effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a GUI implemented in Java Swing an
+The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
 Inca administrator uses to configure user-level Grid monitoring on their
@@
 monitor and which reporters to deploy to those resources.  The configuration
-is stored in a XML file and sent to the agent which handles the implementation
+is stored in a XML file and sent to the agent, which handles the implementation
 (as described in the next section).  The Inca administrator can reload the
@@
 
-Once an Inca administrator enters the location of one more reporter
-repositories, incat will load and display the reporters available from them.
+To begin reporter configuration, the Inca administrator enters the location of
+one more reporter repositories and incat will load and display the reporters
+available from them.
 For each reporter, the Inca administrator can specify the resources to run on,
@@
 Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
-produce one report series when executed with host tg-login.sdsc.edu and
-another report series when executed with dslogin.sdsc.edu.  A set of related
+produce one report series when executed with host 'tg-login.sdsc.edu' and
+another report series when executed with 'dslogin.sdsc.edu'.  A set of related
 series can be grouped into \emph{suites} and shared across other Inca
-deployments.  For example, there could be a Globus suite or a data transfer
+deployments, e.g.,  a Globus suite or a data transfer
 performance suite.  Suites can also be useful to determine interoperability
@@
 'jobmanager' since the batch system is likely to differ from one machine to
-the next.  A resource macro can also have multiple values in which case the
-series will be executed on the resource once for each macro value.  The
+the next and multiple tests will require its value.  A resource macro can also
+have multiple values in which case the series will be executed on the resource
+once for each macro value.  The
 benefit of resource groups and macros is that when a reporter is executed on a
 resource multiple times with different input arguments, it can be represented
-succintly.  Similarly, when a resource attribute is changed, it only has to be
+succinctly.  Similarly, when a resource attribute is changed, it only has to be
 changed in one place and then every series that references it will be updated
@@
 \SubSection{Agent}
+\label{agent}
 
@@
 updates to the configuration, the agent will push out new reporters and/or
-suite changes to each of the effected resources.
+suite changes to each of the affected resources.
 
-To maintain the Inca deployment, the agent regularly pings the reporter
+To further manage the Inca deployment, the agent regularly pings the reporter
 managers on each resource in order to detect when a reporter manager has
@@
 \SubSection{Reporter Manager}
+\label{rm}
 
@@
 
-The reporter manager is implemented in Perl since it is available by default
-on UNIX machines.  The cron scheduling is implemented using the CPAN perl
+The reporter manager is implemented in Perl since Perl is available by default
+on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
 module Schedule::Cron.
@@
 changes from one report to another in a report series.  The depot also
-supports comparisons which are executed on a newly received report; 
+supports comparisons that are executed on a newly received report; 
 currently regular expression matching and version comparisons are 
@@
 data and displays it in a user-friendly format.  The data consumer is packaged
-with Jetty~\cite{jetty} so that pages can be served out of the box.  A set of
-extensible JSP tags and pages query the Inca depot for data (returned as XML)
+with Jetty~\cite{jetty} so that Web pages can be served out of the box.  A set
+of extensible JSP tags and pages query the Inca depot for data (returned as
+XML)
 and a set of XSL stylesheets format the data as HTML.  An Inca administrator
@@
 \SubSection{Security}
+\label{security}
 
 To reduce the security risk of Inca, all Inca components communicate with each
-other using SSL by default.  Also, sensitive information such as passwords are
+other using SSL by default.  Also, sensitive information such as passwords is
 encrypted before being stored to disk on the agent.  To handle reporters that
@@
 The goal is to only have short-term proxies on the machine for the times at
-which they are neeed; this is more secure than maintaining a long-term
+which they are needed; this is more secure than maintaining a long-term
 credential on the resource and easier to manage.  Furthermore, the MyProxy
@@
 
-\subsubsection{Description and Requirements}
+% Description and Requirements - Describe CTSS
+Requirements for user-level Grid monitoring on TeraGrid initially included the
+validation and verification of CTSS on each resource.  As described in the
+introduction, CTSS was designed to
+allow users to more easily run Grid jobs across its distributed, heterogeneous
+resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
+resources and contains approximately 30 software packages that provide
+Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
+tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
+Inca was originally
+deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
+November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
+to collect job usage information from Globus 2 GRAM logs and to detect expired
+host and CA certificates and CA CRLs.
 
-% Describe CTSS
-
-TeraGrid's Coordinated TeraGrid Software and Services (CTSS) was designed to
-allow users to more easily run Grid jobs across its distributed, heterogeneous
-resources.  CTSS is available from all TeraGrid compute resources and is
-comprised of approximately 30 software packages for Grid services (gridftp, ws
-gram), Grid jobs (gridshell, myproxy, globus), cluster tools (pacman, tgusage),
-data management (srb, hdf5) and user applications (mpich, gcc).
-
-In order to validate and verify CTSS functionality from a user perspective,
-TeraGrid and SDSC developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid
-transitioned to Inca 2 in 2006 and, in addition to CTSS monitoring, began using
-Inca to collect job usage information from Globus 2 GRAM logs and to detect
-expired host and CA certificates and CA CRLs to its Inca deployment.
-
-\subsubsection{Usage of Inca}
-
-% Describe reporters, configuration, and deployment.  Figure.
-
-TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
+% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
+To provide user-level monitoring of CTSSv3, a number of version and unit
+test reporters were developed to test the software packages in CTSS.
+Currently, there are 56 such reporters executing an average of 109 series on
+each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
+GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
+application tool-related tests, and 2 security-related tests.  The TeraGrid
+Inca configuration makes extensive use of macros and resource groups and
+currently uses 80 series and 82 resource macros to manage the total of 1928
+series executing on TeraGrid resources.
+Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
+configuration.  The
+agent, depot and consumer components are hosted at SDSC on 
 sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
-at SDSC on inca.sdsc.edu.  TeraGrid's 19 compute resources
-each run a reporter manager and regularly execute an average of 109 reporters
-to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
-security tests.  Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 
-deployment configuration.
+at SDSC on inca.sdsc.edu.
 
@@
 
-\subsubsection{Results}
-
-% Consumer view of CTSS, security, etc.
-
-TeraGrid currently has six status pages: a summary of CTSS test
-failures, a detailed grid of CTSS test results, a page showing grid job
-usage, results for security tests, results for secure mds tests, and a list of
+% Results - Consumer view of CTSS, security, etc.
+TeraGrid currently has six status pages to display the Inca monitoring
+information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
+results, a page showing grid job
+usage, results for security tests, results for secure MDS tests, and a list of
 all running reporters.
 
-Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSS test result
-page.  CTSS software packages are listed along the column and TeraGrid
+Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed grid of
+CTSSv3 test results
+page.  CTSSv3 software packages are listed along the column and TeraGrid
 resources (anonymized) in the header rows.  Test results for each package and
@@
   \includegraphics[scale=0.4]{status-page.eps}
-  \caption{TeraGrid CTSS status page.}
+  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
+  resources anonymized.}
   \label{status_page_fig}
@@
 \SubSection{GrASP}
+\label{grasp}
 

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
add future work section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6558 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \SubSection{Inca administration tool (incat)}
-%\begin{figure}[htb]
-%  \centering
-%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
-%  \caption{\label{arch_fig} Incat .}
-%\end{figure}
+
+\begin{figure*}[htb]
+  \centering
+  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
+  \caption{\label{arch_fig} Screenshot of incat that shows the reporters
+  and their attributes available from the provided reporter repository.}
+\end{figure*}
 
@@
 
-\SubSection{Graphing and Summary Statistics}
+In order to improve problem detection and diagnosis for system administrators,
+we plan to enhance the data consumer with graph rendering and statistical
+analysis capabilities.  This will improve troubleshooting capabilities by
+allowing errors to be understood in a historical context.  It will also enable
+summary displays analogous to those generated by Web page statistics packages
+like Webalizer~\cite{webalizer} that provide a number of useful "Top"
+statistics.  We expect feedback from TeraGrid and other Inca users on the
+exact types of statistics and graphs that will prove to be most useful.  Our
+goal is to offer a default set of statistics and graphs that can be used out
+of the box and provide the capability to add others.
 
-\SubSection{Knowledge Base}
+Also in order to make it easier for system administrators to troubleshoot
+problems, we plan to enhance Inca with a knowledge base that can be used to
+suggest solutions to problems (or point to known bugs if there is no solution
+available).  The knowledge base would be populated by solutions provided by
+system administrators, and the content would be self-moderated in order to
+improve its quality (by voting or adding comments to each other's
+contributions).  This knowledge base represents a potentially vital resource
+for system administrators and provides a forum to share each other's
+invaluable experience and skills.
 
-\SubSection{Fault Tolerance}
-~\newpage
+Finally, we plan to improve the fault tolerance of Inca by enhancing the
+reporter manager so that it caches reports locally if it is unable to
+contact the depot or sends reports to a backup depot if one is available.
+The agent will similarly be enhanced to cache configuration changes locally or
+send configuration to a backup depot if one is available in case of a depot
+failure.
 

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
fix intro of features section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6559 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-% Philosophy of user-level testing
-% Practical byproducts
-The main goal of the Inca 2 design was to XXX (general, flexible, easy to
-install, deploy, and
-maintain, scalable, secure).
-Inca benefits ...
-The following lists the key features of Inca 2 noting which are new features
-to Inca 1 versus improved.
+% Implements user-level Grid monitoring and who it benefits
+Inca 2 is a system that provides user-level monitoring of Grid functionality
+and performance described in the previous section.  It was designed to be
+general, flexible, scalable, and secure in addition to being easy to deploy
+and maintain.  Inca benefits Grid operators who oversee the day-to-day
+operation of a Grid; system administrators who provide and manage resources;
+and users who run applications on a Grid.  The key features of Inca 2 are
+listed below.  The '*' after the feature description indicates it is a new
+feature of Inca 2 while no '*' indicates an improvement to an Inca 1 feature.
 
@@
 \item Collects a wide variety of user-level monitoring results (e.g., simple
-test data to more complex performance benchmark output).  (improved)
+test data to more complex performance benchmark output).
 
@@
 enough information to understand the result and can troubleshoot system
-problems without having to know the internals of Inca. (improved)
+problems without having to know the internals of Inca.
 
 \item Eases the process of writing tests or benchmarks and deploying them into
-Inca installations. (improved)
+Inca installations.
 
 \item Provides means for sharing tests or benchmarks with other Inca 
-users in order to promote sharing of each other's expertise (new)
+users in order to promote sharing of each other's expertise. *
 
 \item Easily adapts to new resources and monitoring requirements in order to
-facilitate maintenance of a running Inca deployment. (improved)
+facilitate maintenance of a running Inca deployment.
 
@@
 in order to understand the behavior of a Grid over time. The results
-are available through a flexible querying interface. (improved)
+are available through a flexible querying interface.
 
 \item Securely manages short-term proxies for testing of Grid services using
-MyProxy~\cite{myproxy}.
+MyProxy~\cite{myproxy}. *
 
@@
 the monitored resources in order to tune their execution frequency to
-reduce the impact on the resources.
+reduce the impact on the resources. *
 
 \end{enumerate}
+
+\noindent The following section describes how the above features are
+implemented.
 
@@
   \centering
-  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
+  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
   \caption{\label{arch_fig} Inca architecture.}
@@
   \mbox{\epsfig{file=incat.eps, width=\textwidth}}
-  \caption{\label{arch_fig} Screenshot of incat that shows the reporters
+  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
   and their attributes available from the provided reporter repository.}
@@
 one more reporter repositories and incat will load and display the reporters
-available from them.
+available from them as shown in Figure~\ref{incat_fig}.
 For each reporter, the Inca administrator can specify the resources to run on,

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
fixes to print floats in order
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6560 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
I put in my first draft
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6562 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \documentclass[times,10pt,twocolumn]{article} 
+\usepackage{dblfloatfix}
 \usepackage{epsfig}
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[tbp]
   \centering
@@
   showstringspaces=false} 
-\begin{figure}
+\begin{figure}[tbp]
 \lstset{language=Perl} 
@@
 
-\begin{figure}[hbt]
+\begin{figure}[tbp]
   \centering
@@
 % Describe GrASP probes
+The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
+serve as simple grid application kernel exemplars as well as a 
+set of diagnostic tools. They test and measure performance of 
+basic grid functions including file transfers, remote execution, 
+and Grid Information Services response.  There are two basic probes: i.  The
+circle probe takes a 100 MB file and passes it in a ring through a given set
+of grid nodes, measuring transfer time at each step.  ii.  The gather probe
+transfers a 100 MB file from some number of source nodes to a compute node,
+runs a computation through the job queue on the compute resource and then
+transfers a 100 MB file to a single destination node.  The transfer of the
+first set of files is executed in parallel.  Once again all tranfers times, as
+well as compute and queue times are recorded.
+
+The GrASP probes yield useful data on the performance and reliability of the
+grid infrastructure that they are run on, but in order to gather a large
+amount of data over time we found it necessary to run them on a schedule and
+gather any error messages that took place during the execution.  In order to
+fulfill the last 2 requirements we deployed the GrASP probes as reporters
+within the Inca framework.
 
@@
 
-% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
-% right in future as though we already included GrASP as a dependency cause
-% it should be done by June.
+The GrASP probes have been written to follow the specifications of an Inca
+reporter.  Porting the original code to follow the specifications proved to be
+trivial.  Inca was also used to store all of the GrASP data and related error
+messages.
 
@@
 
-% A paper.  Interesting that error messages were important.  Predictions?
+Using Inca GrASP was deployed on TeraGrid and Geon for a period of over 6
+months.  The data gathered during that period yielded a paper, Measuring the
+Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
+Through the running of the GrASP probes over such an extended period of time
+we were able to identify a recurring Globus 2 bug and were able to predict the
+execution time of Preco, a Grid application run on the TeraGrid within 12\%
+excluding setup and cleanup time.
 

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
OK shava your turn on this text... let me know when you want me to take it back.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6565 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 The GrASP probes yield useful data on the performance and reliability of the
-grid infrastructure that they are run on, but in order to gather a large
-amount of data over time we found it necessary to run them on a schedule and
-gather any error messages that took place during the execution.  In order to
+grid infrastructure that they are run on.  In order for the data gathered to
+be useful, it must gathered repeatedly over time and stored in a manner
+appropriate for querying.  In addition to storing the measurements available
+we also required that any error messages encountered be stored as well.    
+In order to
 fulfill the last 2 requirements we deployed the GrASP probes as reporters
 within the Inca framework.
-
-\subsubsection{Usage of Inca}
 
@@
 
+\begin{figure*}[tbp]
+  \centering
+  \mbox{\epsfig{file=errorHistogramTG.eps, width=.7\textwidth}}
+  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
+\end{figure*}
+
 \subsubsection{Results}
 
-Using Inca GrASP was deployed on TeraGrid and Geon for a period of over 6
+GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
 months.  The data gathered during that period yielded a paper, Measuring the
 Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
-Through the running of the GrASP probes over such an extended period of time
-we were able to identify a recurring Globus 2 bug and were able to predict the
-execution time of Preco, a Grid application run on the TeraGrid within 12\%
-excluding setup and cleanup time.
+By the running of the GrASP probes over such an extended period of time
+we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
+benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
+error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
+the Globus 2 GRAM server.  We were also able to predict the
+execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).
 

### 2007-02-26 papers/hpdc-gmw-2007/paper.tex
add other uses section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6567 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 distributed, heterogeneous resources. The organization of TeraGrid software
-and services is referred to as the Common TeraGrid Software and Services
+and services is referred to as the Coordinated TeraGrid Software and Services
 (CTSS).  TeraGrid's software and services uniformity simplifies access to its
@@
 
-% Philosophy of user-level testing
-% Practical byproducts
-The main goal of the Inca 2 design was to XXX (general, flexible, easy to
-install, deploy, and
-maintain, scalable, secure).
-The following lists the key features of Inca 2 noting which are new features
-to Inca 1 versus improved.
+% Implements user-level Grid monitoring and who it benefits
+Inca 2 is a system that provides user-level monitoring of Grid functionality
+and performance described in the previous section.  It was designed to be
+general, flexible, scalable, and secure in addition to being easy to deploy
+and maintain.  Inca benefits Grid operators who oversee the day-to-day
+operation of a Grid; system administrators who provide and manage resources;
+and users who run applications on a Grid.  The key features of Inca 2 are
+listed below.  The '*' after the feature description indicates it is a new
+feature of Inca 2 while no '*' indicates an improvement to an Inca 1 feature.
 
@@
 enough information to understand the result and can troubleshoot system
-problems without having to know the internals of Inca 2. (improved)
+problems without having to know the internals of Inca.
 
-\item Provides facilities to ease the process of writing tests or benchmarks
-and deploying them into Inca 2 installations. (improved)
+\item Eases the process of writing tests or benchmarks and deploying them into
+Inca installations.
 
-\item Provides facilities for sharing tests or benchmarks with other Inca 2
-users in order to promote sharing of each other's expertise (new)
+\item Provides means for sharing tests or benchmarks with other Inca 
+users in order to promote sharing of each other's expertise. *
 
 \item Easily adapts to new resources and monitoring requirements in order to
-facilitate maintenance of a running Inca 2 deployment. (improved)
+facilitate maintenance of a running Inca deployment.
 
@@
 in order to understand the behavior of a Grid over time. The results
-are available through a flexible querying interface. (improved)
+are available through a flexible querying interface.
 
-%myproxy stuff
-\item A running monitoring system should have a limited impact on the resources
-it measures and should be secure.
+\item Securely manages short-term proxies for testing of Grid services using
+MyProxy~\cite{myproxy}. *
+
+\item Measures the system impact of tests and benchmarks executing on
+the monitored resources in order to tune their execution frequency to
+reduce the impact on the resources. *
+
 \end{enumerate}
+
+\noindent The following section describes how the above features are
+implemented.
 
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[tbp]
   \centering
-  \mbox{\epsfig{file=arch.eps, width=.8\textwidth}}
+  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
   \caption{\label{arch_fig} Inca architecture.}
@@
 \SubSection{Inca administration tool (incat)}
-%\begin{figure}[htb]
-%  \centering
-%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
-%  \caption{\label{arch_fig} Incat .}
-%\end{figure}
+
+\begin{figure*}[tbp]
+  \centering
+  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
+  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
+  and their attributes available from the provided reporter repository.}
+\end{figure*}
 
@@
 
-Once an Inca administrator enters the location of one more reporter
-repositories, incat will load and display the reporters available from them.
+To begin reporter configuration, the Inca administrator enters the location of
+one more reporter repositories and incat will load and display the reporters
+available from them as shown in Figure~\ref{incat_fig}.
 For each reporter, the Inca administrator can specify the resources to run on,
@@
 
-% myproxy
-
 \SubSection{Reporter Manager}
+\label{rm}
 
@@
 \SubSection{Scalability}
+
+% depot designed to support mirror depot or hierchical support
+% coordinating Inca deployments
 
@@
 resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
-resources and is comprised of approximately 30 software packages that provide
+resources and contains approximately 30 software packages that provide
 Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
@@
 GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
-application tool-related tests, and 2 security-related tests.  
+application tool-related tests, and 2 security-related tests.  The TeraGrid
+Inca configuration makes extensive use of macros and resource groups and
+currently uses 80 series and 82 resource macros to manage the total of 1928
+series executing on TeraGrid resources.
 Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
@@
 
-\begin{figure}[hbt]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.6]{tg-deploy.eps}
+  \includegraphics[width=\columnwidth]{tg-deploy.eps}
   \caption{TeraGrid's Inca 2 Deployment.}
@@
 results, a page showing grid job
-usage, results for security tests, results for secure mds tests, and a list of
+usage, results for security tests, results for secure MDS tests, and a list of
 all running reporters.
 
-Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSSv3 
-test result
+Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed grid of
+CTSSv3 test results
 page.  CTSSv3 software packages are listed along the column and TeraGrid
@@
 
-\begin{figure}[hbt]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.4]{status-page.eps}
+  \includegraphics[width=\columnwidth]{status-page.eps}
   \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
@@
 % Describe GrASP probes
+The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
+serve as simple grid application kernel exemplars as well as a 
+set of diagnostic tools. They test and measure performance of 
+basic grid functions including file transfers, remote execution, 
+and Grid Information Services response.  There are two basic probes: i.  The
+circle probe takes a 100 MB file and passes it in a ring through a given set
+of grid nodes, measuring transfer time at each step.  ii.  The gather probe
+transfers a 100 MB file from some number of source nodes to a compute node,
+runs a computation through the job queue on the compute resource and then
+transfers a 100 MB file to a single destination node.  The transfer of the
+first set of files is executed in parallel.  Once again all tranfers times, as
+well as compute and queue times are recorded.
 
-\subsubsection{Usage of Inca}
+The GrASP probes yield useful data on the performance and reliability of the
+grid infrastructure that they are run on.  In order for the data gathered to
+be useful, it must gathered repeatedly over time and stored in a manner
+appropriate for querying.  In addition to storing the measurements available
+we also required that any error messages encountered be stored as well.    
+In order to
+fulfill the last 2 requirements we deployed the GrASP probes as reporters
+within the Inca framework.
 
-% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
-% right in future as though we already included GrASP as a dependency cause
-% it should be done by June.
+The GrASP probes have been written to follow the specifications of an Inca
+reporter.  Porting the original code to follow the specifications proved to be
+trivial.  Inca was also used to store all of the GrASP data and related error
+messages.
+
+\begin{figure}[tbp]
+  \centering
+  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
+  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
+\end{figure}
 
@@
 
-% A paper.  Interesting that error messages were important.  Predictions?
+GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
+months.  The data gathered during that period yielded a paper, Measuring the
+Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
+By the running of the GrASP probes over such an extended period of time
+we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
+benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
+error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
+the Globus 2 GRAM server.  We were also able to predict the
+execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).
 
-~\newpage
+\SubSection{Other Uses}
 
-\SubSection{Other uses}
-~\newpage
+Other Inca users include the European DEISA Grid and the UK National Grid
+Service (NGS).  Similar to TeraGrid, DEISA uses Inca to verify their Common
+Production Environment (DCPE) across their 11 heterogenous resources.  They
+currently have 40 version reporters to verify each of the packages included in
+DCPE.  In addition, they have unit reporters for the DEISA Applications Test
+Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
+library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
+party application.  DEISA is currently using Inca 1 and will transition to
+Inca 2 in the next few months.
+
+NGS currently has Inca 2 deployed on 8 resources to verify their Grid services 
+and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
+API developed by the GITS developer.  The GITS reporters include 17 tests 
+that verify Globus and GSI-SSH functionality such as executing small job
+submissions and data transfers.  NGS also has 12 tests for their compilers and
+utilize 2 security reporters from the Inca repository.
+
 %------------------------------------------------------------------------- 

### 2007-02-26 papers/hpdc-gmw-2007/paper.tex
some scalability text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6571 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-% depot designed to support mirror depot or hierchical support
-% coordinating Inca deployments
+% Should illustrate that we've thought about how Inca can scale
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\columnwidth]{vo.eps}
+  \caption{TeraGrid's Inca 2 Deployment.}
+  \label{tg_coord_fig}
+\end{figure}
 
-~\newpage
+Inca was designed to distribute the control and storage workload among
+multiple Inca components if needed.  For example, one depot could forward
+storage requests and queries to another depot to distribute its workload or to
+maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
+complex scenario where two Inca deployments coordinate with each other.  For
+example, application communities like GEON have their own Grid but also have
+access to resources on TeraGrid.   Two separate Inca deployments can result in
+duplicate testing. Instead, one Inca deployment can coordinate the execution
+of a suite with another deployment as shown in Figure~\ref{tg_coord_fig}.
+Grid B that has its own resources but also has access to resources in Grid A.
+When an Inca administrator submits a suite to Grid B, the Inca agent running
+on Grid B will determine which reporters run from Grid A resources and forward
+them as a suite request to Grid A's agent.  If Grid B has permission to submit
+suites, Grid A's agent will execute the suite and configure its depot to
+forwards results back to Grid B's depot.
+
 %-------------------------------------------------------------------------
@@
 Service (NGS).  Similar to TeraGrid, DEISA uses Inca to verify their Common
-Production Environment (DCPE) across their 11 heterogenous resources.  They
+Production Environment (DCPE) across their 11 heterogeneous resources.  They
 currently have 40 version reporters to verify each of the packages included in

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
my mods to grasp section -- cathie can you do a quick pass on this for accuracy to make sure I didn't change the content in a bad way
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6576 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 serve as simple grid application kernel exemplars as well as a 
-set of diagnostic tools. They test and measure performance of 
-basic grid functions including file transfers, remote execution, 
-and Grid Information Services response.  There are two basic probes: i.  The
-circle probe takes a 100 MB file and passes it in a ring through a given set
-of grid nodes, measuring transfer time at each step.  ii.  The gather probe
+set of diagnostic tools. They test and measure the performance of 
+basic Grid functions including file transfers, remote execution, 
+and information services queries.  There are two basic probes: circle and 
+gather.  The circle probe transfers a 100 MB file around a ring of
+Grid nodes and measures the transfer time at each step.  The gather probe
 transfers a 100 MB file from some number of source nodes to a compute node,
-runs a computation through the job queue on the compute resource and then
+runs a computation through the job queue on the compute resource, and then
 transfers a 100 MB file to a single destination node.  The transfer of the
@@
 The GrASP probes yield useful data on the performance and reliability of the
-grid infrastructure that they are run on.  In order for the data gathered to
-be useful, it must gathered repeatedly over time and stored in a manner
-appropriate for querying.  In addition to storing the measurements available
-we also required that any error messages encountered be stored as well.    
+Grid infrastructure that they are run on.  As such, data must be gathered 
+repeatedly over time and archived.
+In addition to storing the performance measurements,
+any error messages encountered must be stored as well.    
 In order to
-fulfill the last 2 requirements we deployed the GrASP probes as reporters
-within the Inca framework.
-
-The GrASP probes have been written to follow the specifications of an Inca
-reporter.  Porting the original code to follow the specifications proved to be
-trivial.  Inca was also used to store all of the GrASP data and related error
-messages.
+fulfill the last two requirements, the GrASP probes were modified
+to follow the reporter specifications and deployed using Inca.
+Porting the original code to follow the reporter specifications proved to be
+trivial.  A number of scripts were then written to graph and analyze the GrASP
+data and related error messages stored in the Inca depot.
 
@@
   \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
-  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
+  \caption{\label{errorHist_fig} Number and types of errors collected by
+  GrASP benchmark execution over a six-month period on TeraGrid.}
 \end{figure}
 
-\subsubsection{Results}
-
-GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
-months.  The data gathered during that period yielded a paper, Measuring the
-Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
-By the running of the GrASP probes over such an extended period of time
-we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
-benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
+Using Inca, GrASP was deployed on TeraGrid and GEON for a period of over 6
+months.  The data gathered during that period yielded a paper~\cite{grasp2}.
+One result was that a recurring Globus 2 bug was identified as shown in Figure ~\ref{errorHist_fig}.
+The figure shows the types (shortened) and number of system errors that were detected while executing
+GrASP on TeraGrid in 2005. The highest occurring
 error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
-the Globus 2 GRAM server.  We were also able to predict the
-execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).
+the Globus 2 GRAM server.  Furthermore, the execution time of Preco, a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
 

### 2007-02-27 pubs/papers/hpdc-gmw-2007/paper.tex
Grammar improvements.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6577 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
@@
 arise.  Well-defined requirements and good communication are required in this
-model.  Otherwise inconsistencies between the resources arise that either
-inconvenience the user or prevent them from using particular resources
-together.  A second challenge is that failures will occur over
+model.  Otherwise, inconsistencies between the resources arise that either
+inconvenience the user or prevent them from using a particular resource
+altogether.  A second challenge is that failures will occur over
 time in the Grid services due to network or system failures, software
 misconfiguration, or software bugs.  In order to address these challenges,
-Grid monitoring can be used to detect such problems leading to a more
+Grid monitoring can be used to detect such problems, leading to a more
 stable and dependable Grid infrastructure.
@@
 examined.  This type of monitoring information is useful for showing the
-utilization of Grid resources but it does not provide the type of
-high-level monitoring needed to detect user problems within the Grid
-infrastructure, such as incompatible software versions.
+utilization of Grid resources, but it does not provide the type of
+high-level monitoring needed to detect user problems, such as incompatible
+software versions, within the Grid infrastructure.
 
@@
 measurements of the Grid infrastructure should be done from a standard user
-account.  In fact, it is important to not execute under a system
-administrator's account because they may be privileged and often have custom
-shell initialization files.
+account.  It is important to not execute from a system administrator's account,
+since it may have special privileges and use custom shell initialization files.
 
@@
 when documentation and testing are done in parallel in a pre-production
-environment but they should be closely coordinated activities.
+environment, but they should be closely coordinated activities.
 
@@
 \noindent In our experience, writing and maintaining user-level tests and
-performance measurements is an iterative refinement process since Grids are
+performance measurements is an iterative refinement process, since Grids are
 dynamic and the software environment changes over time as packages are
 upgraded.  It is also difficult to write and deploy a test perfectly the first
-time because of portability issues and sometimes incomplete user
+time because of portability issues and incomplete user
 documentation.  For example, it may take a few iterations to determine whether
 detected failures are the result of a faulty test, fault user documentation,
-or a faulty system.  As such, this can be a labor-intensive activity and
-therefore difficult to achieve full test coverage.  In practice, 
-either
-testing all the commands that exist in the user documentation and/or having at
-least one basic test for each software component of the Grid infrastructure
-achieves a reasonable subset of testing.
+or a faulty system.  As such, this can be a labor-intensive activity, making it
+difficult to achieve full test coverage.  In practice, testing all the commands
+listed in the user documentation and/or having at least one basic test for each
+software component of the Grid infrastructure typically yields a representative
+set of tests.
 
@@
 % developed Inca 2.
-In 2003, SDSC, in partnership with TeraGrid, began developing Inca
+In 2003 SDSC, in partnership with TeraGrid, began developing Inca
 1~\cite{inca1} to implement a user-level Grid monitoring system with the above
-features and started using it to validate and
+features and started using it to
 verify that CTSS was deployed consistently across all TeraGrid resources and
@@
 contains a number of substantial improvements over Inca 1 with respect to
-security, installation and maintenance, and storage capabilities.  A
-production release of Inca 2 was provided in February 2007 and has been
-running on TeraGrid since November 2006.  Currently, seven other Grids in the
+security, installation and maintenance, and storage capabilities.  Inca 2 has
+been running on TeraGrid since November 2006, and in February 2007 a production
+version of the software was released.  Currently, seven other Grids in the
 U.S., Europe, and Australia use Inca.
@@
 and performance described in the previous section.  It was designed to be
-general, flexible, scalable, and secure in addition to being easy to deploy
+general, flexible, scalable, and secure, in addition to being easy to deploy
 and maintain.  Inca benefits Grid operators who oversee the day-to-day
@@
 and users who run applications on a Grid.  The key features of Inca 2 are
-listed below.  The '*' after the feature description indicates it is a new
-feature of Inca 2 while no '*' indicates an improvement to an Inca 1 feature.
+listed below.  A '*' after the feature description indicates it is a new
+feature of Inca 2; other items note improvements to Inca 1 features.
 
@@
 
-\item Provides means for sharing tests or benchmarks with other Inca 
-users in order to promote sharing of each other's expertise. *
+\item Provides means for sharing tests and benchmarks between Inca users. *
 
@@
 
-\noindent The following section describes how the above features are
-implemented.
+\noindent The following section describes how the Inca architecture implements
+these features.
 
@@
 % overview description of components
-Figure~\ref{arch_fig} shows the architecture of Inca 2 designed to implement
-the features described in the previous section.  Inca 2 is composed of 3 core
+Figure~\ref{arch_fig} shows the architecture of Inca 2.
+Inca 2 is composed of 3 core
 components (in highlighted box):  the agent, depot, and reporter manager.
@@
 or more \textit{reporter repositories} that contain user-level tests and
-benchmarks called \textit{reporters} and a configuration file describing how
-to execute them on the Grid resources created using an administration GUI tool
+benchmarks, called \textit{reporters}, and a configuration file describing how
+to execute them on the Grid resources.  This configuration is normally created
+using an administration GUI tool
 called \textit{incat} (Inca Administration Tool).  The output or results
@@
 displayed to users.  The following steps describe how an Inca administrator
-would deploy user-level test and/or performance measurements to their
+would deploy user-level tests and/or performance measurements to their
 resources.
@@
 \noindent The following subsections describe the Inca components in more
-detail using the order of the steps above.
+detail, using the order of the steps above.
 
@@
 \item an exit status tag
-indicating whether the reporter was able to complete its test or measurement
+indicating whether the reporter was able to complete its test or measurement,
 and an optional error message.  
@@
 executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
+Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
 Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
@@
 (lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
-1-9, 43-46).  It also includes some informational and debug logging functions
-again similar to log4j; the log output has been very useful to system
-administrators who can view a summary of the test or benchmark that the
+1-9, 43-46).  It also includes some informational and debug logging functions,
+again similar to log4j.  The log output has been very useful to system
+administrators, who can view a summary of the test or benchmark that the
 reporter performed without reading the reporter source code.  Line
@@
 Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
-dependency to the reporter telling the Inca system to download a
+dependency to the reporter, telling the Inca system to download a
 short-term proxy before running this reporter (this is discussed further in
@@
 section), and a catalog file.  Repository contents are accessible using a URL
-and designed to be shared across multiple Inca deployments.  The catalog file
-follows APT's Packages.gz~\cite{apt} format and thus tar.gz dependencies such
-as non-standard Perl APIs or source code can be added to reporter catalog
-entries.  Inca will then automatically deploy tar.gz dependencies into a
-subdirectory of its installation (more in Section~\ref{agent}).  This enables
-reporters to be deployed to resources with a minimum of effort.  Furthermore,
-each package specified in the catalog is versioned.  This allows Inca to
-automatically distribute reporter code updates such as bug fixes.  As such,
-Inca administrators maintaining repositories need to be careful to ensure
-their updates are tested and work.
+and designed to be shared across multiple Inca deployments.  The catalog file,
+patterned after APT's Packages.gz~\cite{apt}, allows the user to indicate
+reporter dependencies on CPAN modules, tar.gz packages, and other external
+sources.  Inca automatically deploys dependencies into a
+subdirectory of its installation (more in Section~\ref{agent}); this enables
+reporters to be deployed to resources with minimumal effort.  Each package
+specified in the catalog is versioned, allowing Inca to
+automatically distribute reporter code updates such as bug fixes.  Because of
+this, Inca administrators who maintain repositories need to ensure
+that updates to reporters work properly before committing them to a repository.
 
@@
 To begin reporter configuration, the Inca administrator enters the location of
-one more reporter repositories and incat will load and display the reporters
-available from them as shown in Figure~\ref{incat_fig}.
+one more reporter repositories, and incat loads and displays the reporters
+available from them, as shown in Figure~\ref{incat_fig}.
 For each reporter, the Inca administrator can specify the resources to run on,
@@
 process of executing the same series on multiple resources.  Furthermore,
-attributes called \emph{macros} can be attached to resources and resource
-groups and similarly be referenced in the series configuration (i.e., inputs
+attributes called \emph{macros} can be attached to resource groups for
+reference in series configuration (i.e., inputs
 and runtime environment).  For example, it is useful to have a macro called
@@
 The agent is implemented in Java.
-
-% myproxy
 
@@
 
-~\newpage
+% Should illustrate that we've thought about how Inca can scale
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\columnwidth]{vo.eps}
+  \caption{TeraGrid's Inca 2 Deployment.}
+  \label{tg_coord_fig}
+\end{figure}
+
+Inca was designed to distribute the control and storage workload among
+multiple Inca components if needed.  For example, one depot could forward
+storage requests and queries to another depot to distribute its workload or to
+maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
+complex scenario where two Inca deployments coordinate with each other.  For
+example, application communities like GEON have their own Grid but also have
+access to resources on TeraGrid.   Two separate Inca deployments can result in
+duplicate testing. Instead, one Inca deployment can coordinate the execution
+of a suite with another deployment as shown in Figure~\ref{tg_coord_fig}.
+Grid B that has its own resources but also has access to resources in Grid A.
+When an Inca administrator submits a suite to Grid B, the Inca agent running
+on Grid B will determine which reporters run from Grid A resources and forward
+them as a suite request to Grid A's agent.  If Grid B has permission to submit
+suites, Grid A's agent will execute the suite and configure its depot to
+forwards results back to Grid B's depot.
+
 %-------------------------------------------------------------------------
@@
 % Describe GrASP probes
+The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
+serve as simple grid application kernel exemplars as well as a 
+set of diagnostic tools. They test and measure the performance of 
+basic Grid functions including file transfers, remote execution, 
+and information services queries.  There are two basic probes: circle and 
+gather.  The circle probe transfers a 100 MB file around a ring of
+Grid nodes and measures the transfer time at each step.  The gather probe
+transfers a 100 MB file from some number of source nodes to a compute node,
+runs a computation through the job queue on the compute resource, and then
+transfers a 100 MB file to a single destination node.  The transfer of the
+first set of files is executed in parallel.  Once again all tranfers times, as
+well as compute and queue times are recorded.
 
-\subsubsection{Usage of Inca}
+The GrASP probes yield useful data on the performance and reliability of the
+Grid infrastructure that they are run on.  As such, data must be gathered 
+repeatedly over time and archived.
+In addition to storing the performance measurements,
+any error messages encountered must be stored as well.    
+In order to
+fulfill the last two requirements, the GrASP probes were modified
+to follow the reporter specifications and deployed using Inca.
+Porting the original code to follow the reporter specifications proved to be
+trivial.  A number of scripts were then written to graph and analyze the GrASP
+data and related error messages stored in the Inca depot.
 
-% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
-% right in future as though we already included GrASP as a dependency cause
-% it should be done by June.
+\begin{figure}[tbp]
+  \centering
+  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
+  \caption{\label{errorHist_fig} Number and types of errors collected by
+  GrASP benchmark execution over a six-month period on TeraGrid.}
+\end{figure}
 
-\subsubsection{Results}
+Using Inca, GrASP was deployed on TeraGrid and GEON for a period of over 6
+months.  The data gathered during that period yielded a paper~\cite{grasp2}.
+One result was that a recurring Globus 2 bug was identified as shown in Figure ~\ref{errorHist_fig}.
+The figure shows the types (shortened) and number of system errors that were detected while executing
+GrASP on TeraGrid in 2005. The highest occurring
+error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
+the Globus 2 GRAM server.  Furthermore, the execution time of Preco, a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
 
-% A paper.  Interesting that error messages were important.  Predictions?
+\SubSection{Other Uses}
 
-~\newpage
+Other Inca users include the European DEISA Grid and the UK National Grid
+Service (NGS).  Similar to TeraGrid, DEISA uses Inca to verify their Common
+Production Environment (DCPE) across their 11 heterogeneous resources.  They
+currently have 40 version reporters to verify each of the packages included in
+DCPE.  In addition, they have unit reporters for the DEISA Applications Test
+Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
+library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
+party application.  DEISA is currently using Inca 1 and will transition to
+Inca 2 in the next few months.
 
-\SubSection{Other uses}
-~\newpage
+NGS currently has Inca 2 deployed on 8 resources to verify their Grid services 
+and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
+API developed by the GITS developer.  The GITS reporters include 17 tests 
+that verify Globus and GSI-SSH functionality such as executing small job
+submissions and data transfers.  NGS also has 12 tests for their compilers and
+utilize 2 security reporters from the Inca repository.
+
 %------------------------------------------------------------------------- 

### 2007-02-27 pubs/papers/hpdc-gmw-2007/paper.tex
took out subsubsection header in grasp section and corrected mispelling
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6579 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
added abstract
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6580 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \begin{abstract}
-User-level Grid monitoring is valuable, how it relates to other Grid
-monitoring,  and what are its implementation challenges.
-Inca 1 good but had limitations.  In this paper, we introduce Inca 2 and
-describe its features and architecture.  We then show a few use cases for Inca
-is being deployed on TeraGrid and XXX?  System impact results and performance
-results.  Finally, we discuss our future work.  
+The primary goal in the creation of Grids is to provide unified and coherent
+access to distributed computing, data storage and analysis, instruments, and
+other resources to advance scientific exploration.  Grids combine multiple
+complex and interdependent systems that span several administrative domains.
+This complexity poses challenges for both the administrators who build and
+maintain the Grid resources and the scientists who use them.  While other Grid
+monitoring tools provide system-level information on the utilization of Grid
+resources, the Inca system provides user-level Grid monitoring with periodic,
+automated user-level testing of the software and services required to support
+Grid operation.  Inca can be used by Grid operators, system administrators,
+and application users to identify, analyze, and troubleshoot user-level Grid
+failures thereby improving Grid stability.  In this paper, we describe the new
+features of our current Inca release, Inca 2.  We then describe the
+architecture of the Inca 2 system, in addition to use cases that describe two
+Inca 2 deployments in production environments.  
 \end{abstract}
@@
 
-\subsubsection{Description and Requirements}
-
 % Describe GrASP probes
@@
 transfers a 100 MB file to a single destination node.  The transfer of the
-first set of files is executed in parallel.  Once again all tranfers times, as
+first set of files is executed in parallel.  Once again all transfers times, as
 well as compute and queue times are recorded.

### 2007-02-27 pubs/papers/hpdc-gmw-2007/paper.tex
revisions throughout
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6582 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \Section{Introduction}
+\label{intro}
 
@@
 % What user-level monitoring provides and why we think it is good
-User-level Grid monitoring approaches testing and performance measurement of
-the Grid infrastructure from the user perspective.  The goal is to act as an
-impartial test user of the Grid and detect problems with the infrastructure so
-they can be fixed before users notice them -- user complaints should not be
-the first indication of Grid failures.  In our view, the following guidelines 
-define user-level Grid monitoring:
+User-level Grid monitoring is Grid infrastructure testing and performance measurement 
+from a generic, impartial user's perspective.  The goal of user-level monitoring is 
+to detect and fix Grid infrastructure problems before users notice them -- 
+user complaints should not be the first indication of Grid failures.  
+In our view, the following guidelines define user-level Grid monitoring:
 
@@
 measurements of the Grid infrastructure should be done from a standard user
-account.  It is important to not execute from a system administrator's account,
+account.  It is important not to execute from a system administrator's account,
 since it may have special privileges and use custom shell initialization files.
@@
 should be automated and executed periodically.
+
+\item User-level tests and performance measurements should be written and
+maintained within an iterative refinement process.  An iterative process is
+required since Grids are dynamic and software environments change over time as
+packages are upgraded.  It is also difficult to write and deploy a test
+correctly the first time because of portability issues and incomplete user
+documentation.  For example, it may take some iterations to determine whether a
+detected failure is the result of a faulty test, user document, or Grid
+resource.
+
+\item In order to determine overall Grid health, monitoring must be flexible
+enough to include many types of user-level tests and performance measurements.
+Typically all of the commands listed in the user documentation and/or at least
+one basic test for each software component of the Grid infrastructure is
+required.
 
@@
 
-\noindent In our experience, writing and maintaining user-level tests and
-performance measurements is an iterative refinement process, since Grids are
-dynamic and the software environment changes over time as packages are
-upgraded.  It is also difficult to write and deploy a test perfectly the first
-time because of portability issues and incomplete user
-documentation.  For example, it may take a few iterations to determine whether
-detected failures are the result of a faulty test, fault user documentation,
-or a faulty system.  As such, this can be a labor-intensive activity, making it
-difficult to achieve full test coverage.  In practice, testing all the commands
-listed in the user documentation and/or having at least one basic test for each
-software component of the Grid infrastructure typically yields a representative
-set of tests.
-
 % Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
@@
 % developed Inca 2.
-In 2003 SDSC, in partnership with TeraGrid, began developing Inca
+
+\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
 1~\cite{inca1} to implement a user-level Grid monitoring system with the above
@@
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
-GITS~\cite{gits}, scripts that ran a fixed number of Grid tests and formatted
+Grid Integration Test Script~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
 results in HTML.  Although these tools were easy to install and produced
 useful information, they showed the view of the Grid from a single
-resource, lacked automation, and were not easily extensible.  The initial
+resource, lacked automation, and were not easily extensible.
+
+The initial
 version of Inca was implemented as a client-server architecture.  It provided
-data collection, data storage (with limited archiving capabilities) that was
-accessible from a Web services interface, and data display though Web status
+data collection, data storage (accessible from a Web services interface and with 
+limited archiving capabilities), and data display though Web status
 pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
@@
 Inca 2 is a system that provides user-level monitoring of Grid functionality
-and performance described in the previous section.  It was designed to be
+and performance.  It was designed to be
 general, flexible, scalable, and secure, in addition to being easy to deploy
@@
 operation of a Grid; system administrators who provide and manage resources;
-and users who run applications on a Grid.  The key features of Inca 2 are
+and users who run applications on a Grid.  Besides meeting the guidelines 
+described in Section~\ref{intro}, Inca 2 has additional features
 listed below.  A '*' after the feature description indicates it is a new
-feature of Inca 2; other items note improvements to Inca 1 features.
+feature of Inca 2; other items note improvements to Inca 1 features.  The 
+Inca system:
 
@@
 \caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
-availability of a Globus GRAM server and (b) an output sample.}
+availability of a Globus GRAM server and (b) sample output from a Globus GRAM 
+reporter.}
 \end{figure}
@@
 \end{itemize} 
-\noindent Because the body of the report can be any XML sequence, it enables
+\noindent Because the body of a report can be any XML sequence, it enables
 reporters to express a wide variety of information.  Today, we have four
@@
 executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
-Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
+Inca::Reporter::SimpleUnit and
+Inca::Reporter::GridProxy (both subclasses of Inca::Reporter).  The Inca::Reporter API provides convenience
 functions for handling the required input arguments
-(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
+(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
 10-31) and printing the Inca-compliant header and exit status XML tags
-(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
-1-9, 43-46).  It also includes some informational and debug logging functions,
-again similar to log4j.  The log output has been very useful to system
+(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
+1-9, 43-46).  It also includes some informational and debug logging functions
+similar to log4j.  The log output has been very useful to system
 administrators, who can view a summary of the test or benchmark that the
@@
 executes a system command (using a 30 second timeout) and logs to the 'system'
-level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
+level of the log XML output (producing lines \ref{pingReporter}(b) 32-36).  The subclass
 Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
-standard reporter body schema -- reporting software functionality or service
+standard reporter body schema to report software functionality or service
 tests results; it handles the printing of the small body XML
-(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
-(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
-18, 20) depending on the output of system command.  Finally, the
-Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
+(lines~\ref{pingReporter}(b) 39-41).  Finally, the
+Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
 dependency to the reporter, telling the Inca system to download a
@@
 packages and libraries (including the Perl APIs described in the previous
-section), and a catalog file.  Repository contents are accessible using a URL
+section), and a catalog file.  Repository contents are usually accessible using a URL
 and designed to be shared across multiple Inca deployments.  The catalog file,
@@
 reporters that collect version information from a software package and
-serve as a most basic unit test, unit test reporters that run a more involved
-unit test, or performance benchmark reporters.  The unit and version
+serve as a most basic functionality test, unit test reporters that run a more involved
+functionality test, or performance benchmark reporters.  The unit and version
 reporters cover software such as Grid middleware, compilers, math libraries,
-data tools, and visualization tools.  The performance reporters available
-currently measure data transfer and execute Grid benchmarks as described in
+data tools, and visualization tools.  Current performance reporters
+measure data transfer and execute Grid benchmarks as described in
 Section~\ref{grasp}.
@@
 deployments, e.g.,  a Globus suite or a data transfer
-performance suite.  Suites can also be useful to determine interoperability
-among Grids or to determine whether an application's requirements are being
+performance suite.  Suites can also be useful in determining interoperability
+among Grids or whether an application's requirements are being
 fulfilled on a Grid.
@@
 resource multiple times with different input arguments, it can be represented
-succinctly.  Similarly, when a resource attribute is changed, it only has to be
-changed in one place and then every series that references it will be updated
-as well.  This makes the initial configuration and maintenance easier on the
-Inca administrator and less error prone.
+succinctly.  Similarly, when a resource attribute is changed it only has to be
+changed in one place for every series that references it to be updated.
+Inca's initial configuration and maintenance is therefore easier and less error prone.
 
@@
 cache of reporters and their dependencies; it periodically checks the
-repositories for updates every 4 hours by default and automatically
-distributes them to the reporter managers (if the latest version is desired).  
+repositories for updates (every 4 hours by default) and automatically
+distributes them to the reporter managers if the latest version is desired.  
 The agent is implemented in Java.
@@
 supports comparisons that are executed on a newly received report; 
-currently regular expression matching and version comparisons are 
+% need Jim's help with this sentence
+currently regular expression matching and greater than/less than comparisons are 
 supported.  Optionally, an Inca administrator can select to receive
@@
 To reduce the security risk of Inca, all Inca components communicate with each
-other using SSL by default.  Also, sensitive information such as passwords is
+other using SSL by default.  Sensitive information such as passwords is
 encrypted before being stored to disk on the agent.  To handle reporters that
-require a valid proxy credential to execute, the reporter manager will fetch a
+require a valid proxy credential to execute, the reporter manager fetches a
 short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
 administrator) and then destroys the proxy once the reporter has completed.
-The goal is to only have short-term proxies on the machine for the times at
-which they are needed; this is more secure than maintaining a long-term
-credential on the resource and easier to manage.  Furthermore, the MyProxy
-authentication information is fetched from the agent each time a proxy
-credential is needed and then cleared from memory.
+MyProxy authentication information is fetched from the agent each time a proxy
+credential is needed and then cleared from memory.  Generating short-term 
+proxies only when needed is more secure than maintaining long-term
+credentials and is easier to manage.
 
@@
   \includegraphics[width=\columnwidth]{vo.eps}
-  \caption{TeraGrid's Inca 2 Deployment.}
+  \caption{Coordinated Inca Deployments.}
   \label{tg_coord_fig}
@@
 
-Inca was designed to distribute the control and storage workload among
+Inca was designed to distribute control and storage workload among
 multiple Inca components if needed.  For example, one depot could forward
@@
 duplicate testing. Instead, one Inca deployment can coordinate the execution
-of a suite with another deployment as shown in Figure~\ref{tg_coord_fig}.
-Grid B that has its own resources but also has access to resources in Grid A.
+of a suite with another deployment.
+Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
+has its own resources but also has access to resources in Grid A.
 When an Inca administrator submits a suite to Grid B, the Inca agent running
-on Grid B will determine which reporters run from Grid A resources and forward
+on Grid B will determine which reporters run on Grid A resources and forward
 them as a suite request to Grid A's agent.  If Grid B has permission to submit
@@
 tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
-Inca was originally
+
+To provide user-level monitoring of CTSSv3, Inca was originally
 deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
@@
 % Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
-To provide user-level monitoring of CTSSv3, a number of version and unit
-test reporters were developed to test the software packages in CTSS.
+A number of version and unit test reporters were developed to test the software packages in CTSS.
 Currently, there are 56 such reporters executing an average of 109 series on
@@
 GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
-application tool-related tests, and 2 security-related tests.  The TeraGrid
+application tool-related tests, and 2 security-related tests.
+
+The TeraGrid
 Inca configuration makes extensive use of macros and resource groups and
-currently uses 80 series and 82 resource macros to manage the total of 1928
+currently uses 80 series and 82 resource macros to manage the total of 1,928
 series executing on TeraGrid resources.
@@
 transfers a 100 MB file to a single destination node.  The transfer of the
-first set of files is executed in parallel.  Once again all transfers times, as
-well as compute and queue times are recorded.
+first set of files is executed in parallel.  Transfer, compute, and queue times are recorded.
 
-The GrASP probes yield useful data on the performance and reliability of the
-Grid infrastructure that they are run on.  As such, data must be gathered 
+The GrASP probes yield data about Grid infrastructure performance and reliability.
+In order to be most useful, probe data must be gathered 
 repeatedly over time and archived.
@@
 In order to
-fulfill the last two requirements, the GrASP probes were modified
+gather historical data, the GrASP probes were modified
 to follow the reporter specifications and deployed using Inca.
@@
 Using Inca, GrASP was deployed on TeraGrid and GEON for a period of over 6
-months.  The data gathered during that period yielded a paper~\cite{grasp2}.
-One result was that a recurring Globus 2 bug was identified as shown in Figure ~\ref{errorHist_fig}.
-The figure shows the types (shortened) and number of system errors that were detected while executing
+months~\cite{grasp2}.  During this deployment, the execution time of Preco, 
+a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
+A recurring Globus 2 bug was also identified as shown in Figure ~\ref{errorHist_fig}.  The figure shows the frequency and types (shortened) of 
+system errors that were detected while executing 
 GrASP on TeraGrid in 2005. The highest occurring
 error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
-the Globus 2 GRAM server.  Furthermore, the execution time of Preco, a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
+the Globus 2 GRAM server.
 
@@
 Other Inca users include the European DEISA Grid and the UK National Grid
-Service (NGS).  Similar to TeraGrid, DEISA uses Inca to verify their Common
+Service (NGS).  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
+Similar to TeraGrid, DEISA uses Inca to verify their Common
 Production Environment (DCPE) across their 11 heterogeneous resources.  They
@@
 and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
-API developed by the GITS developer.  The GITS reporters include 17 tests 
-that verify Globus and GSI-SSH functionality such as executing small job
-submissions and data transfers.  NGS also has 12 tests for their compilers and
+API developed by the GITS developer.  The GITS reporters include 17 tests, 
+such as small job submissions and data transfers, that verify Globus and GSI-SSH functionality.
+NGS also has 12 tests for their compilers and
 utilize 2 security reporters from the Inca repository.
@@
 In order to improve problem detection and diagnosis for system administrators,
-we plan to enhance the data consumer with graph rendering and statistical
-analysis capabilities.  This will improve troubleshooting capabilities by
+we plan to add graph rendering and statistical
+analysis capabilities to the Inca data consumer.  This will improve troubleshooting capabilities by
 allowing errors to be understood in a historical context.  It will also enable
@@
 
-Also in order to make it easier for system administrators to troubleshoot
-problems, we plan to enhance Inca with a knowledge base that can be used to
+Also to aid system administrator troubleshooting,
+we plan to enhance Inca with a knowledge base that can be used to
 suggest solutions to problems (or point to known bugs if there is no solution
 available).  The knowledge base would be populated by solutions provided by
-system administrators, and the content would be self-moderated in order to
+system administrators -- the content would be self-moderated in order to
 improve its quality (by voting or adding comments to each other's
-contributions).  This knowledge base represents a potentially vital resource
-for system administrators and provides a forum to share each other's
+contributions).  A knowledge base could provide a potentially vital resource
+for system administrators and offer a forum for sharing
 invaluable experience and skills.

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
my mods to kate's mods
few grammar changes and the following content changes:

- Inca::Reporter::GridProxy is not a subclass of Inca::Reporter
- URLs also include file paths so repositories are always accessible via
  a URL



git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6583 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 examined.  This type of monitoring information is useful for showing the
-utilization of Grid resources but it does not provide the type of
-high-level monitoring needed to detect user problems within the Grid
-infrastructure, such as incompatible software versions.
+utilization of Grid resources, but it does not provide the type of
+high-level monitoring needed to detect user problems, such as incompatible
+software versions, within the Grid infrastructure.
 
 % What user-level monitoring provides and why we think it is good
-User-level Grid monitoring approaches testing and performance measurement of
-the Grid infrastructure from the user perspective.  The goal is to act as an
-impartial test user of the Grid and detect problems with the infrastructure so
-they can be fixed before users notice them -- user complaints should not be
-the first indication of Grid failures.  In our view, the following guidelines 
-define user-level Grid monitoring:
+User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
+from a generic, impartial user's perspective.  The goal of user-level monitoring is 
+to detect and fix Grid infrastructure problems before users notice them -- 
+user complaints should not be the first indication of Grid failures.  
+In our view, the following guidelines define user-level Grid monitoring:
 
@@
 measurements of the Grid infrastructure should be done from a standard user
-account.  In fact, it is important to not execute under a system
-administrator's account because they may be privileged and often have custom
-shell initialization files.
+account.  It is important not to execute from a system administrator's account,
+since it may have special privileges and use custom shell initialization files.
 
@@
 
-\noindent In our experience, writing and maintaining user-level tests and
-performance measurements is an iterative refinement process since Grids are
-dynamic and the software environment changes over time as packages are
-upgraded.  It is also difficult to write and deploy a test perfectly the first
-time because of portability issues and sometimes incomplete user
-documentation.  For example, it may take a few iterations to determine whether
-detected failures are the result of a faulty test, fault user documentation,
-or a faulty system.  As such, this can be a labor-intensive activity and
-therefore difficult to achieve full test coverage.  In practice, 
-either
-testing all the commands that exist in the user documentation and/or having at
-least one basic test for each software component of the Grid infrastructure
-achieves a reasonable subset of testing.
-
 % Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
@@
 % developed Inca 2.
-In 2003, SDSC, in partnership with TeraGrid, began developing Inca
+
+\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
 1~\cite{inca1} to implement a user-level Grid monitoring system with the above
-features and started using it to validate and
+features and started using it to
 verify that CTSS was deployed consistently across all TeraGrid resources and
@@
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
-GITS~\cite{gits}, scripts that ran a fixed number of Grid tests and formatted
+Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
 results in HTML.  Although these tools were easy to install and produced
 useful information, they showed the view of the Grid from a single
-resource, lacked automation, and were not easily extensible.  The initial
+resource, lacked automation, and were not easily extensible.
+
+The initial
 version of Inca was implemented as a client-server architecture.  It provided
-data collection, data storage (with limited archiving capabilities) that was
-accessible from a Web services interface, and data display though Web status
+data collection, data storage (accessible from a Web services interface and with 
+limited archiving capabilities), and data display though Web status
 pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
@@
 Inca 2 is a system that provides user-level monitoring of Grid functionality
-and performance described in the previous section.  It was designed to be
-general, flexible, scalable, and secure in addition to being easy to deploy
+and performance.  It was designed to be
+general, flexible, scalable, and secure, in addition to being easy to deploy
 and maintain.  Inca benefits Grid operators who oversee the day-to-day
 operation of a Grid; system administrators who provide and manage resources;
-and users who run applications on a Grid.  The key features of Inca 2 are
-listed below.  The '*' after the feature description indicates it is a new
-feature of Inca 2 while no '*' indicates an improvement to an Inca 1 feature.
+and users who run applications on a Grid.  Besides meeting the guidelines 
+described in Section~\ref{intro}, Inca 2 has additional features
+listed below.  A '*' after the feature description indicates it is a new
+feature of Inca 2; other items note improvements to Inca 1 features.  The 
+Inca system:
 
@@
 \item an exit status tag
-indicating whether the reporter was able to complete its test or measurement
+indicating whether the reporter was able to complete its test or measurement,
 and an optional error message.  
 \end{itemize} 
-\noindent Because the body of the report can be any XML sequence, it enables
+\noindent Because the body of a report can be any XML sequence, it enables
 reporters to express a wide variety of information.  Today, we have four
@@
 executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
+Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
 Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
 functions for handling the required input arguments
-(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
+(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
 10-31) and printing the Inca-compliant header and exit status XML tags
-(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
+(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
 1-9, 43-46).  It also includes some informational and debug logging functions
-again similar to log4j; the log output has been very useful to system
-administrators who can view a summary of the test or benchmark that the
+similar to log4j.  The log output has been very useful to system
+administrators, who can view a summary of the test or benchmark that the
 reporter performed without reading the reporter source code.  Line
@@
 executes a system command (using a 30 second timeout) and logs to the 'system'
-level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
+level of the log XML output (producing lines \ref{pingReporter}(b) 32-36).  The subclass
 Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
-standard reporter body schema -- reporting software functionality or service
+standard reporter body schema to report software functionality or service
 tests results; it handles the printing of the small body XML
-(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
-(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
-18, 20) depending on the output of system command.  Finally, the
-Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
-dependency to the reporter telling the Inca system to download a
+(lines~\ref{pingReporter}(b) 39-41).  Finally, the
+Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
+dependency to the reporter, telling Inca to download a
 short-term proxy before running this reporter (this is discussed further in
@@
 resource multiple times with different input arguments, it can be represented
-succinctly.  Similarly, when a resource attribute is changed, it only has to be
-changed in one place and then every series that references it will be updated
-as well.  This makes the initial configuration and maintenance easier on the
-Inca administrator and less error prone.
+succinctly.  Similarly, when a resource attribute is changed it only has to be
+changed in one place for every series that references it to be updated.
+Initial Inca configuration and maintenance is therefore easier and less error prone.
 
@@
 transfers a 100 MB file to a single destination node.  The transfer of the
-first set of files is executed in parallel.  Once again all tranfers times, as
-well as compute and queue times are recorded.
+first set of files is executed in parallel.  Transfer, compute, and queue times are recorded.
 
-The GrASP probes yield useful data on the performance and reliability of the
-Grid infrastructure that they are run on.  As such, data must be gathered 
+The GrASP probes yield data about Grid infrastructure performance and reliability.
+In order to be most useful, probe data must be gathered 
 repeatedly over time and archived.

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
added summary
added note about scalability not yet being implemented

corrected NGS deployment

added acknowledgement section so we don't forget


git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6584 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 suites, Grid A's agent will execute the suite and configure its depot to
-forwards results back to Grid B's depot.
+forwards results back to Grid B's depot.  Forwarding is not yet implemented 
+in Inca 2.
 
@@
 
-NGS currently has Inca 2 deployed on 8 resources to verify their Grid services 
-and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
+NGS currently has Inca 2 deployed on four resources to verify their Grid services (on eight sites) and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
 API developed by the GITS developer.  The GITS reporters include 17 tests, 
@@
 
-~\newpage
+%1.  Motivate and differentiate the Grid monitoring Inca does 2. Describe Inca
+%2 design and its benefits 3. Illustrate that Inca 2 design is mature and
+%being used in production by several Grids 4. Be different from Inca 1 paper
+The goal of user-level Grid monitoring is to test and measure the Grid
+infrastructure from an impartial user perspective and detect problems before
+users notice them.  Inca 2 implements such a user-level Grid monitoring system
+and provides a number of new and improved features over our first version,
+Inca 1.  The architecture and features of Inca 2 enable an Inca administrator
+to easily write and deploy tests and performance measurements to Grid
+resources and maintain them in a changing Grid environment.  The storage,
+archiving, and querying capabilities also enable in-depth analysis of Grid
+errors and performance now in a historical context, which will benefit Grid
+operators and system administrators.  Inca 2 also provides a number of
+security features such as short-term proxy management and supports
+scalability.  A production version of Inca 2 was released in February 2007 and
+has been used in production environments to verify the common user environment
+of TeraGrid and to execute and collect data for a set of Grid benchmarks on
+both TeraGrid and GEON.  Future enhancements of Inca 2 will improve its fault
+tolerance and enable more in-depth analysis of the overall Grid health and
+behavior.  They should also make it easier to resolve, in addition to detect
+errors and understand them in a historical context.  The features that Inca
+provides and its proposed enhancements should improve the stability of the
+Grid infrastructure it monitors, ultimately improving the productivity of
+scientists who conduct research on a Grid.
+
+%------------------------------------------------------------------------- 
+\Section{Acknowledgements}
 

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
just suggestions
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6586 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 require the careful coordination of software packages, services, and
-configurations across multiple, heterogeneous resources.  The TeraGrid
+configurations across multiple, potentially heterogeneous, resources.  The TeraGrid
 project~\cite{teragrid}, for example, manages the coordination of software and
@@
 time in the Grid services due to network or system failures, software
-misconfiguration, or software bugs.  In order to address these challenges,
+misconfiguration, or software bugs. 
 Grid monitoring can be used to detect such problems, leading to a more
@@
 account.  It is important not to execute from a system administrator's account,
-since it may have special privileges and use custom shell initialization files.
+because it may have special privileges and use custom shell initialization files.
 
@@
 maintained within an iterative refinement process.  An iterative process is
-required since Grids are dynamic and software environments change over time as
+required because Grids are dynamic and software environments change over time as
 packages are upgraded.  It is also difficult to write and deploy a test
@@
 % effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
+The Inca administrative tool (incat) is a GUI, implemented using Java Swing, which an
 Inca administrator uses to configure user-level Grid monitoring on their
@@
 and runtime environment).  For example, it is useful to have a macro called
-'jobmanager' since the batch system is likely to differ from one machine to
+'jobmanager' because the batch system is likely to differ from one machine to
 the next and multiple tests will require its value.  A resource macro can also
@@
 distributes them to the reporter managers if the latest version is desired.  
-The agent is implemented in Java.
+The agent is implemented using Java.
 
@@
 
-The reporter manager is implemented in Perl since Perl is available by default
+The reporter manager is implemented using Perl because Perl is available by default
 on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
@@
 the data produced by reporters. The depot uses a relational database via
-Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
-depot provides full archiving of reporter output and structures its schema
+Hibernate~\cite{hibernate} enabling the use of a variety of database backends.  The depot provides full archiving of reporter output and structures its schema
 around series and the minimization of redundant data, i.e., only stores
@@
 history.  A Web services interface is also available to provide
-unauthenticated query access to data.  The depot is implemented in Java.
+unauthenticated query access to data.  The depot is implemented using Java.
 

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
small changes to summary and tg in intro
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6587 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 services by deploying and monitoring a common user environment across
-distributed, heterogeneous resources. The organization of TeraGrid software
-and services is referred to as the Coordinated TeraGrid Software and Services
-(CTSS).  TeraGrid's software and services uniformity simplifies access to its
+distributed, heterogeneous resources. 
+TeraGrid's software and services uniformity simplifies access to its
 resources, which consist of more than 102 teraflops of compute capability and
@@
 Requirements for user-level Grid monitoring on TeraGrid initially included the
-validation and verification of CTSS on each resource.  As described in the
-introduction, CTSS was designed to
+validation and verification of Coordinated TeraGrid Software and Services (CTSS) 
+on each TeraGrid resource.  As described in the introduction, CTSS was designed to
 allow users to more easily run Grid jobs across its distributed, heterogeneous
@@
 %being used in production by several Grids 4. Be different from Inca 1 paper
-The goal of user-level Grid monitoring is to test and measure the Grid
+The goal of user-level Grid monitoring is to test and measure Grid
 infrastructure from an impartial user perspective and detect problems before
@@
 archiving, and querying capabilities also enable in-depth analysis of Grid
-errors and performance now in a historical context, which will benefit Grid
+errors and performance in a historical context, which benefit Grid
 operators and system administrators.  Inca 2 also provides a number of
@@
 tolerance and enable more in-depth analysis of the overall Grid health and
-behavior.  They should also make it easier to resolve, in addition to detect
-errors and understand them in a historical context.  The features that Inca
-provides and its proposed enhancements should improve the stability of the
+behavior.  They will also make it easier to detect and resolve errors
+and understand them in a historical context.  The features that Inca
+provides and its proposed enhancements improve the stability of the
 Grid infrastructure it monitors, ultimately improving the productivity of

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
figure changes to fit on 10 pages.  made subfigure for TG figs.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6590 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \pagestyle{empty}
+
+% some unnecessary whitespace still -- these suggestions from
+% http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/squeeze.html
+\renewcommand\dblfloatpagefraction{.95}
+\renewcommand\dbltopfraction{.95}
+\renewcommand\bottomfraction{.95}
+\renewcommand\textfraction{.05}   
+\setcounter{totalnumber}{50}
+\setcounter{dbltopnumber}{50}
+\setcounter{bottomnumber}{50}
 
@@
 
+\begin{figure*}[tbp]
+  \centering
+  \includegraphics[width=.6\textwidth]{arch.eps}
+  \caption{\label{arch_fig} Inca architecture.}
+\end{figure*}
+
 % Implements user-level Grid monitoring and who it benefits
@@
 \Section{Inca 2 Architecture}
-
-\begin{figure*}[tbp]
-  \centering
-  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
-  \caption{\label{arch_fig} Inca architecture.}
-\end{figure*}
 
@@
   \centering
-  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
+  \mbox{\epsfig{file=incat.eps, width=.9\textwidth}}
   \caption{\label{incat_fig} Screenshot of incat that shows the reporters
@@
 % Should illustrate that we've thought about how Inca can scale
-\begin{figure}[tbp]
+\begin{figure*}[tbp]
   \centering
-  \includegraphics[width=\columnwidth]{vo.eps}
-  \caption{Coordinated Inca Deployments.}
-  \label{tg_coord_fig}
-\end{figure}
+  \includegraphics[width=.6\textwidth]{vo.eps}
+  \caption{\label{tg_coord_fig} Coordinated Inca deployments.}
+\end{figure*}
 
@@
 \SubSection{TeraGrid}
+
+%\begin{figure}[tbp]
+%  \centering
+%  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
+%  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
+%\end{figure}
+%\begin{figure}[tbp]
+%  \centering
+%  \includegraphics[width=.4\textwidth]{status-page.eps}
+%  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
+%\end{figure}
+
+\begin{figure*}[tbp]
+\subfigure[]{\includegraphics[width=.8\columnwidth]{tg-deploy.eps}}
+\subfigure[]{\includegraphics[width=.6\textwidth]{status-page.eps}}
+  \caption{\label{tg_deploy_fig}\label{status_page_fig} (a) TeraGrid's Inca 2
+  deployment and (b) portion of the TeraGrid CTSSv3 detailed status page with
+  the resources anonymized.}
+\end{figure*}
 
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\columnwidth]{tg-deploy.eps}
-  \caption{TeraGrid's Inca 2 Deployment.}
-  \label{tg_deploy_fig}
-\end{figure}
-
 % Results - Consumer view of CTSS, security, etc.
@@
 resource are shown in the table body rows.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\columnwidth]{status-page.eps}
-  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
-  resources anonymized.}
-  \label{status_page_fig}
-\end{figure}
 
@@
 
-\begin{figure}[tbp]
+\begin{figure*}[tbp]
   \centering
-  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
+  \mbox{\epsfig{file=errorHistogramTG.eps, width=.6\textwidth}}
   \caption{\label{errorHist_fig} Number and types of errors collected by
   GrASP benchmark execution over a six-month period on TeraGrid.}
-\end{figure}
+\end{figure*}
 

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
Update.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6591 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 arise.  Well-defined requirements and good communication are required in this
-model.  Otherwise, inconsistencies between the resources arise that either
+model.  Otherwise, inconsistencies arise between the resources that either
 inconvenience the user or prevent them from using a particular resource
@@
 correctly the first time because of portability issues and incomplete user
-documentation.  For example, it may take some iterations to determine whether a
-detected failure is the result of a faulty test, user document, or Grid
-resource.
+documentation.  It often requires multiple iterations to determine whether a
+detected failure stems from a faulty test, user document, or Grid resource.
 
@@
 enough to include many types of user-level tests and performance measurements.
-Typically all of the commands listed in the user documentation and/or at least
-one basic test for each software component of the Grid infrastructure is
-required.
+Typically, tests for each command listed in the user documentation and/or for
+each software component of the Grid infrastructure are required.
 
@@
 \noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
-1~\cite{inca1} to implement a user-level Grid monitoring system with the above
-features and started using it to
-verify that CTSS was deployed consistently across all TeraGrid resources and
-to monitor its status.  At that time, the only available user-level Grid
+1~\cite{inca1} to implement a user-level Grid monitoring system that followed
+the above guidelines.  At that time, the only available user-level Grid
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
@@
 useful information, they showed the view of the Grid from a single
-resource, lacked automation, and were not easily extensible.
+resource, lacked automation, and were not easily extensible.  Inca 1 provided
+the means to verify that CTSS was deployed consistently across all TeraGrid
+resources and to monitor its status.
 
@@
 pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
-2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
-valuable lessons and designed Inca 2, our current release.  Inca 2
+2003. Running Inca 1 for a year and a half on TeraGrid taught 
+valuable lessons that have been incorporated into the design of Inca 2, our
+current release.  Inca 2
 contains a number of substantial improvements over Inca 1 with respect to
@@
 version of the software was released.  Currently, seven other Grids in the
-U.S., Europe, and Australia use Inca.
+U.S., Europe, and Australia use Inca 2.
 
@@
 operation of a Grid; system administrators who provide and manage resources;
-and users who run applications on a Grid.  Besides meeting the guidelines 
+and users who run applications on a Grid.  Besides following the guidelines 
 described in Section~\ref{intro}, Inca 2 has additional features
@@
 Figure~\ref{arch_fig} shows the architecture of Inca 2.
-Inca 2 is composed of 3 core
-components (in highlighted box):  the agent, depot, and reporter manager.
+Inca 2 incorporates three core
+components (highlighted box):  the agent, depot, and reporter manager.
 The \textit{agent} and \textit{reporter managers} coordinate the execution of
@@
 
-\item The agent
-  \begin{enumerate}
-    \item fetches reporters from the reporter repository
-    \item creates a reporter manager on each resource
-    \item sends the reporters and instructions for executing them to each reporter manager.
-  \end{enumerate}
+\item The agent fetches reporters from the reporter repository, creates a
+reporter manager on each resource, and sends the reporters and instructions for
+executing them to each reporter manager.
 
 \item Each reporter manager executes reporters according to its schedule and
-sends results (reports) to the depot
+sends results (reports) to the depot.
 
-\item Data consumers display collected data (reports) by querying the depot
+\item Data consumers display collected data (reports) by querying the depot.
 \end{enumerate}
@@
 easy to produce and can be run outside of the Inca system (e.g., by a system
-administrator).  A reporter should be written using the user-level
-monitoring guidelines described in the introduction and could be a simple
-Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
-or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
-support certain command line options and produce an XML document or
-\emph{report}
+administrator).  Existing reporters range from a simple Globus~\cite{globus}
+GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
+to complex Grid application benchmarks~\cite{grasp}.  Reporters must
+support certain command line options and produce an XML document, or
+\emph{report},
 according to the Inca reporter schema.  The goal of the reporter schema is to
@@
 \item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
-\item a body containing the results expressed as any XML sequence; and
+\item a body containing the results expressed as an XML sequence; and
 \item an exit status tag
@@
 \ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
-executes a system command (using a 30 second timeout) and logs to the 'system'
-level of the log XML output (producing lines \ref{pingReporter}(b) 32-36).  The subclass
+executes a system command (using a 30 second timeout) after logging it to the
+'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
 Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
@@
 dependency to the reporter, telling Inca to download a
-short-term proxy before running this reporter (this is discussed further in
+short-term proxy before running this reporter. (As discussed in
 Section~\ref{security}).  Most current reporters use the Perl APIs and consist
@@
 subdirectory of its installation (more in Section~\ref{agent}); this enables
-reporters to be deployed to resources with minimumal effort.  Each package
+reporters to be deployed to resources with minimal delay.  Each package
 specified in the catalog is versioned, allowing Inca to
@@
 developed and tested for TeraGrid.  Most reporters are either version
-reporters that collect version information from a software package and
-serve as a most basic functionality test, unit test reporters that run a more involved
+reporters that collect version information from a software package,
+unit test reporters that run a more involved
 functionality test, or performance benchmark reporters.  The unit and version
@@
 % effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a GUI, implemented using Java Swing, which an
+The Inca administrative tool (incat) is a Java Swing GUI that an
 Inca administrator uses to configure user-level Grid monitoring on their
@@
 one more reporter repositories, and incat loads and displays the reporters
-available from them, as shown in Figure~\ref{incat_fig}.
+available from them (Figure~\ref{incat_fig}).
 For each reporter, the Inca administrator can specify the resources to run on,
@@
 Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
-produce one report series when executed with host 'tg-login.sdsc.edu' and
-another report series when executed with 'dslogin.sdsc.edu'.  A set of related
+produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
 series can be grouped into \emph{suites} and shared across other Inca
@@
 (SSH or Globus) to access the resource and start monitoring there (described
-in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
-together and referenced in the series configuration.  This facilitates the
-process of executing the same series on multiple resources.  Furthermore,
-attributes called \emph{macros} can be attached to resource groups for
-reference in series configuration (i.e., inputs
-and runtime environment).  For example, it is useful to have a macro called
-'jobmanager' because the batch system is likely to differ from one machine to
-the next and multiple tests will require its value.  A resource macro can also
-have multiple values in which case the series will be executed on the resource
-once for each macro value.  The
-benefit of resource groups and macros is that when a reporter is executed on a
-resource multiple times with different input arguments, it can be represented
-succinctly.  Similarly, when a resource attribute is changed it only has to be
-changed in one place for every series that references it to be updated.
-Initial Inca configuration and maintenance is therefore easier and less error prone.
+in Sections~\ref{agent} and ~\ref{rm}).  Resources can be aggregated into
+groups for reference in the series configuration, facilitating the
+process of executing the same series on multiple resources.  Also,
+input and runtime environment attributes can be attached to resource groups
+for reference in series configuration.
+These resource \emph{macros} can have multiple values, in which
+case the series will be executed on the resource once for each macro value.
+Resource groups and macros ease the process of defining and maintaining
+multiple similar series.
 

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
fixed two user-level grid monitoring bullets that were bugging me
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6597 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\item User-level tests and performance measurements should be written and
-maintained within an iterative refinement process.  An iterative process is
-required because Grids are dynamic and software environments change over time as
-packages are upgraded.  It is also difficult to write and deploy a test
-correctly the first time because of portability issues and incomplete user
-documentation.  It often requires multiple iterations to determine whether a
-detected failure stems from a faulty test, user document, or Grid resource.
+\item User-level tests and performance measurements should be easy to update
+and maintain as they are often revised due to Grid infrastructure upgrades.
+It is also difficult to write and deploy a test correctly the first time
+because of portability issues and incomplete user documentation.  Multiple
+iterations are usually required to determine whether a detected failure stems
+from a faulty test, user documentation, or Grid resource.
 
-\item In order to determine overall Grid health, monitoring must be flexible
-enough to include many types of user-level tests and performance measurements.
-Typically, tests for each command listed in the user documentation and/or for
-each software component of the Grid infrastructure are required.
+\item Many types of user-level tests and benchmarks can be used to monitor 
+Grid infrastructure.  Testing documented user commands and individual Grid
+software components provides a representative indication of Grid status.
 

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
Update.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6598 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 The Inca agent is a server that implements the configuration specified by the
-Inca administrator.  When it receives a configuration file from the Inca
-administrator, it will determine which reporters should be executed on each
-resource by expanding the resource macros and groups; it then stores the
-expanded configuration information in the depot.  The agent stages and
+Inca administrator.  When the agent receives a configuration from incat,
+it expands any resource group and macro references to determine
+the series to execute on each resource and stores this
+information in the depot.  The agent stages and
 launches an Inca component, called a reporter manager (described in the
-following subsection), on each resource using either SSH or Globus.  Once a
+following subsection), on each resource, using either SSH or Globus.  After a
 reporter manager contacts its agent, the agent transmits the reporters to
-execute along with their dependencies and a suite that contains their series
-configuration and schedule of execution.  As an Inca administrator makes
+execute, any dependencies, and a suite that contains series
+configuration and an execution schedule.  As an Inca administrator makes
 updates to the configuration, the agent will push out new reporters and/or
@@
 
-To further manage the Inca deployment, the agent regularly pings the reporter
-managers on each resource in order to detect when a reporter manager has
-failed so it can be restarted.  For example, if a resource goes down for a
-planned maintenance, the agent will attempt to restart the reporter manager
-(by default every hour) until it succeeds.  The agent also maintains a local
-cache of reporters and their dependencies; it periodically checks the
-repositories for updates (every 4 hours by default) and automatically
-distributes them to the reporter managers if the latest version is desired.  
-The agent is implemented using Java.
+The agent regularly pings its reporter managers in order to detect when one has
+failed (for example, when a system is taken down for maintenance) and so must
+be restarted.  The agent also maintains a local cache of reporters and their
+dependencies; it periodically checks repositories (every 4 hours by default)
+and automatically distributes reporter updates to the reporter managers as
+needed.  The agent is implemented using Java.
 
@@
 user account, the reporter manager executes reporters on-demand or using an
-internal cron scheduler, and sends reports to the depot for archiving. The
-reporter manager monitors reporter system usage using the system command
-\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
+internal cron scheduler and sends reports to the depot for archiving. The
+reporter manager monitors reporter system usage 
+and enforces limits (e.g., wall clock time, CPU time, memory).
 System usage information is sent to the depot with each report. 
-
-The reporter manager is implemented using Perl because Perl is available by default
-on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
-module Schedule::Cron.
+The reporter manager is implemented using Perl to make it easy to install on
+a wide variety of UNIX systems.
 
@@
 the data produced by reporters. The depot uses a relational database via
-Hibernate~\cite{hibernate} enabling the use of a variety of database backends.  The depot provides full archiving of reporter output and structures its schema
-around series and the minimization of redundant data, i.e., only stores
-changes from one report to another in a report series.  The depot also
-supports comparisons that are executed on a newly received report; 
-% need Jim's help with this sentence
-currently regular expression matching and greater than/less than comparisons are 
-supported.  Optionally, an Inca administrator can select to receive
-email notification when the result of the comparison changes.
+Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
+The depot provides full archiving of reporter output, and the DB schema is
+tuned to minimize redundant data.  Inca administrators can specify comparison
+tests to run on reports as they are received, and the depot will send email
+when the results of these comparisons change.  This provides the administrator
+with quick notification of problems as they appear and of the results of
+repairs.
 

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
reordering of user-level monitoring guidelines and some other minor doc fixes
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6601 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 Grid systems poses challenges for both administrators who build and
-maintain Grid resources and scientists who use them.  First, system
+maintain Grid resources and scientists who use them.  System
 administration is distributed across multiple administrative domains 
@@
 
-\item In order to reflect regular user experiences, tests or performance
-measurements of the Grid infrastructure should be done from a standard user
-account.  It is important not to execute from a system administrator's account,
+\item User-level tests or performance measurements of the Grid infrastructure
+should be run from a standard user
+account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
 because it may have special privileges and use custom shell initialization files.
 
-\item Also in order to reflect regular user experiences, tests should be
+\item User-level tests or performance measurements that interact with Grid services
+require authentication and should be executed using a standard user GSI
+credential that is mapped to the standard user account.
+
+\item User-level tests should be
 written and configured using information directly from user documentation
-(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
+(e.g., hostnames, ports, pathnames, etc.) to emulate a regular user.  
+This may not always be possible
 when documentation and testing are done in parallel in a pre-production
@@
 
-\item Since Grids are dynamic, user-level tests or performance measurements
-should be automated and executed periodically.
+\item The configuration of user-level tests or performance measurements should be managed
+centrally in order to ensure consistent testing of the resources, rather than
+by system administrators who may not use the same information that is
+available to users.
 
@@
 
-\item Tests or performance measurements that interact with Grid services
-require authentication and should be executed using a standard user GSI
-credential that is mapped to the standard user account.
+\item Since Grids are dynamic, user-level tests or performance measurements
+should be automated and executed periodically.
 
-\item Tests or performance measurements should be executed locally on all Grid
+\item User-level tests or performance measurements should be executed locally on all Grid
 resources when appropriate so that all Grid access points available to users
@@
 problems.
-
-\item The configuration of tests or performance measurements should be managed
-centrally in order to ensure consistent testing of the resources, rather than
-by system administrators who may not use the same information that is
-available to users.
 
@@
 1~\cite{inca1} to implement a user-level Grid monitoring system that followed
-the above guidelines.  At that time, the only available user-level Grid
+the defined guidelines.  At that time, the only available user-level Grid
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
@@
 resource, lacked automation, and were not easily extensible.  Inca 1 provided
-the means to verify that CTSS was deployed consistently across all TeraGrid
-resources and to monitor its status.
+the means to verify the common user environment was deployed consistently across all TeraGrid
+resources and monitored its status.
 
@@
 security, installation and maintenance, and storage capabilities.  Inca 2 has
-been running on TeraGrid since November 2006, and in February 2007 a production
-version of the software was released.  Currently, seven other Grids in the
+been running on TeraGrid since November 2006 and a production
+version of the software was released in February 2007.  Currently, seven other Grids in the
 U.S., Europe, and Australia use Inca 2.
@@
 dependency to the reporter, telling Inca to download a
-short-term proxy before running this reporter. (As discussed in
+short-term proxy before running this reporter (as discussed in
 Section~\ref{security}).  Most current reporters use the Perl APIs and consist
@@
 Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
-The depot provides full archiving of reporter output, and the DB schema is
+The depot provides full archiving of reporter output, and the database schema is
 tuned to minimize redundant data.  Inca administrators can specify comparison
@@
 
+This work was supported by the following NSF grants:  Cooperative Agreement
+Award \#0503944 SCI: TeraGrid Resource Partners,
+
 %------------------------------------------------------------------------- 

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
reformatted intro bullets to start with verb and removed use of "guidelines" in following text -- Kate, can you make a pass on these updates (specifically, the 5th and 7th bullets)
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6602 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 require the careful coordination of software packages, services, and
-configurations across multiple, heterogeneous resources.  The TeraGrid
+configurations across multiple, potentially heterogeneous, resources.  The TeraGrid
 project~\cite{teragrid}, for example, manages the coordination of software and
 services by deploying and monitoring a common user environment across
-distributed, heterogeneous resources. The organization of TeraGrid software
-and services is referred to as the Coordinated TeraGrid Software and Services
-(CTSS).  TeraGrid's software and services uniformity simplifies access to its
+distributed, heterogeneous resources. 
+TeraGrid's software and services uniformity simplifies access to its
 resources, which consist of more than 102 teraflops of compute capability and
@@
 % What user-level monitoring provides and why we think it is good
-User-level Grid monitoring is Grid infrastructure testing and performance measurement 
+User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
 from a generic, impartial user's perspective.  The goal of user-level monitoring is 
@@
 user complaints should not be the first indication of Grid failures.  
-In our view, the following guidelines define user-level Grid monitoring:
+In our view, the following are features of user-level Grid monitoring:
 
@@
 
-\item In order to reflect regular user experiences, tests or performance
-measurements of the Grid infrastructure should be done from a standard user
-account.  It is important not to execute from a system administrator's account,
-since it may have special privileges and use custom shell initialization files.
+\item Runs from a standard user
+account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
+because it may have special privileges and use custom shell initialization files.
 
-\item Also in order to reflect regular user experiences, tests should be
-written and configured using information directly from user documentation
-(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
+\item Executes with a standard user GSI
+credential, which is mapped to the standard user account, when tests or performance measurements require authentication to Grid services.
+
+\item Emulates a regular user using tests and performance
+measurements that are written and configured using information directly from user documentation
+(e.g., hostnames, ports, pathnames, etc.). 
+This may not always be possible
 when documentation and testing are done in parallel in a pre-production
@@
 
-\item Since Grids are dynamic, user-level tests or performance measurements
-should be automated and executed periodically.
+\item Centrally manages the configuration of user-level tests or performance measurements in order to ensure consistent testing of the resources, rather than
+by system administrators who may not use the same information that is
+available to users.
 
-\item User-level tests and performance measurements should be written and
-maintained within an iterative refinement process.  An iterative process is
-required since Grids are dynamic and software environments change over time as
-packages are upgraded.  It is also difficult to write and deploy a test
-correctly the first time because of portability issues and incomplete user
-documentation.  For example, it may take some iterations to determine whether a
-detected failure is the result of a faulty test, user document, or Grid
-resource.
+\item Is easy to update
+and maintain as user-level tests and performance measurements often need
+to be updated when the Grid infrastructure is upgraded.
+It is also difficult to write and deploy a test correctly the first time
+because of portability issues and incomplete user documentation.  Multiple
+iterations are usually required to determine whether a detected failure stems
+from a faulty test, user documentation, or Grid resource.
 
-\item In order to determine overall Grid health, monitoring must be flexible
-enough to include many types of user-level tests and performance measurements.
-Typically all of the commands listed in the user documentation and/or at least
-one basic test for each software component of the Grid infrastructure is
-required.
+\item Provides a representative indication of Grid status by testing
+documented user commands and individual Grid software components.
 
-\item Tests or performance measurements that interact with Grid services
-require authentication and should be executed using a standard user GSI
-credential that is mapped to the standard user account.
+\item Automates the execution of user-level tests or performance measurements
+periodically since Grids are dynamic.
 
-\item Tests or performance measurements should be executed locally on all Grid
+\item Executes locally on all Grid
 resources when appropriate so that all Grid access points available to users
@@
 \noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
-1~\cite{inca1} to implement a user-level Grid monitoring system with the above
-features and started using it to
-verify that CTSS was deployed consistently across all TeraGrid resources and
-to monitor its status.  At that time, the only available user-level Grid
+1~\cite{inca1} to implement a user-level Grid monitoring system that provided
+these features.  At that time, the only available user-level Grid
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
-Grid Integration Test Script~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
+Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
 results in HTML.  Although these tools were easy to install and produced
 useful information, they showed the view of the Grid from a single
-resource, lacked automation, and were not easily extensible.
+resource, lacked automation, and were not easily extensible.  Inca 1 provided
+the means to verify the common user environment was deployed consistently across all TeraGrid
+resources and monitored its status.
 
@@
 pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
-2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
-valuable lessons and designed Inca 2, our current release.  Inca 2
+2003. Running Inca 1 for a year and a half on TeraGrid taught 
+valuable lessons that have been incorporated into the design of Inca 2, our
+current release.  Inca 2
 contains a number of substantial improvements over Inca 1 with respect to
 security, installation and maintenance, and storage capabilities.  Inca 2 has
-been running on TeraGrid since November 2006, and in February 2007 a production
-version of the software was released.  Currently, seven other Grids in the
-U.S., Europe, and Australia use Inca.
+been running on TeraGrid since November 2006 and a production
+version of the software was released in February 2007.  Currently, seven other Grids in the
+U.S., Europe, and Australia use Inca 2.
 
@@
 operation of a Grid; system administrators who provide and manage resources;
-and users who run applications on a Grid.  Besides meeting the guidelines 
+and users who run applications on a Grid.  Besides implementing the features
 described in Section~\ref{intro}, Inca 2 has additional features
@@
 
-\begin{figure*}[tbp]
-  \centering
-  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
-  \caption{\label{arch_fig} Inca architecture.}
-\end{figure*}
-
 % overview description of components
 Figure~\ref{arch_fig} shows the architecture of Inca 2.
-Inca 2 is composed of 3 core
-components (in highlighted box):  the agent, depot, and reporter manager.
+Inca 2 incorporates three core
+components (highlighted box):  the agent, depot, and reporter manager.
 The \textit{agent} and \textit{reporter managers} coordinate the execution of
@@
 
-\item Using the guidelines described in the introduction, the Inca
-administrator either writes reporters to monitor their Grid or uses existing
+\item The Inca
+administrator either writes reporters to monitor the user-level functionality
+and performance of their Grid or uses existing
 reporters in a published repository.
@@
 executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit and
-Inca::Reporter::GridProxy (both subclasses of Inca::Reporter).  The Inca::Reporter API provides convenience
+Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
+Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
 functions for handling the required input arguments
@@
 Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
-dependency to the reporter, telling the Inca system to download a
-short-term proxy before running this reporter (this is discussed further in
+dependency to the reporter, telling Inca to download a
+short-term proxy before running this reporter (as discussed in
 Section~\ref{security}).  Most current reporters use the Perl APIs and consist
@@
 packages and libraries (including the Perl APIs described in the previous
-section), and a catalog file.  Repository contents are usually accessible using a URL
+section), and a catalog file.  Repository contents are accessible using a URL
 and designed to be shared across multiple Inca deployments.  The catalog file,
@@
 % effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
+The Inca administrative tool (incat) is a Java Swing GUI that an
 Inca administrator uses to configure user-level Grid monitoring on their
@@
 (SSH or Globus) to access the resource and start monitoring there (described
-in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
-together and referenced in the series configuration.  This facilitates the
-process of executing the same series on multiple resources.  Furthermore,
-attributes called \emph{macros} can be attached to resource groups for
-reference in series configuration (i.e., inputs
-and runtime environment).  For example, it is useful to have a macro called
-'jobmanager' since the batch system is likely to differ from one machine to
-the next and multiple tests will require its value.  A resource macro can also
-have multiple values in which case the series will be executed on the resource
-once for each macro value.  The
-benefit of resource groups and macros is that when a reporter is executed on a
-resource multiple times with different input arguments, it can be represented
-succinctly.  Similarly, when a resource attribute is changed it only has to be
-changed in one place for every series that references it to be updated.
-Inca's initial configuration and maintenance is therefore easier and less error prone.
+in Sections~\ref{agent} and ~\ref{rm}).  Resources can be aggregated into
+groups for reference in the series configuration, facilitating the
+process of executing the same series on multiple resources.  Also,
+input and runtime environment attributes can be attached to resource groups
+for reference in series configuration.
+These resource \emph{macros} can have multiple values, in which
+case the series will be executed on the resource once for each macro value.
+Resource groups and macros ease the process of defining and maintaining
+multiple similar series.
 
@@
 
-To further manage the Inca deployment, the agent regularly pings the reporter
-managers on each resource in order to detect when a reporter manager has
-failed so it can be restarted.  For example, if a resource goes down for a
-planned maintenance, the agent will attempt to restart the reporter manager
-(by default every hour) until it succeeds.  The agent also maintains a local
-cache of reporters and their dependencies; it periodically checks the
-repositories for updates (every 4 hours by default) and automatically
-distributes them to the reporter managers if the latest version is desired.  
-The agent is implemented in Java.
+The agent regularly pings its reporter managers in order to detect when one has
+failed (for example, when a system is taken down for maintenance) and so must
+be restarted.  The agent also maintains a local cache of reporters and their
+dependencies; it periodically checks repositories (every 4 hours by default)
+and automatically distributes reporter updates to the reporter managers as
+needed.  The agent is implemented using Java.
 
@@
 user account, the reporter manager executes reporters on-demand or using an
-internal cron scheduler, and sends reports to the depot for archiving. The
-reporter manager monitors reporter system usage using the system command
-\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
+internal cron scheduler and sends reports to the depot for archiving. The
+reporter manager monitors reporter system usage 
+and enforces limits (e.g., wall clock time, CPU time, memory).
 System usage information is sent to the depot with each report. 
-
-The reporter manager is implemented in Perl since Perl is available by default
-on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
-module Schedule::Cron.
+The reporter manager is implemented using Perl to make it easy to install on
+a wide variety of UNIX systems.
 
@@
 the data produced by reporters. The depot uses a relational database via
-Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
-depot provides full archiving of reporter output and structures its schema
-around series and the minimization of redundant data, i.e., only stores
-changes from one report to another in a report series.  The depot also
-supports comparisons that are executed on a newly received report; 
-% need Jim's help with this sentence
-currently regular expression matching and greater than/less than comparisons are 
-supported.  Optionally, an Inca administrator can select to receive
-email notification when the result of the comparison changes.
+Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
+The depot provides full archiving of reporter output, and the database schema is
+tuned to minimize redundant data.  Inca administrators can specify comparison
+tests to run on reports as they are received, and the depot will send email
+when the results of these comparisons change.  This provides the administrator
+with quick notification of problems as they appear and of the results of
+repairs.
 
@@
 
+%\begin{figure}[tbp]
+%  \centering
+%  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
+%  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
+%\end{figure}
+%\begin{figure}[tbp]
+%  \centering
+%  \includegraphics[width=.4\textwidth]{status-page.eps}
+%  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
+%\end{figure}
+
+\begin{figure*}[tbp]
+\subfigure[]{\includegraphics[width=.8\columnwidth]{tg-deploy.eps}}
+\subfigure[]{\includegraphics[width=.6\textwidth]{status-page.eps}}
+  \caption{\label{tg_deploy_fig}\label{status_page_fig} (a) TeraGrid's Inca 2
+  deployment and (b) portion of the TeraGrid CTSSv3 detailed status page with
+  the resources anonymized.}
+\end{figure*}
+
 % Description and Requirements - Describe CTSS
 Requirements for user-level Grid monitoring on TeraGrid initially included the
-validation and verification of CTSS on each resource.  As described in the
-introduction, CTSS was designed to
+validation and verification of Coordinated TeraGrid Software and Services (CTSS) 
+on each TeraGrid resource.  As described in the introduction, CTSS was designed to
 allow users to more easily run Grid jobs across its distributed, heterogeneous
@@
 
-~\newpage
+%1.  Motivate and differentiate the Grid monitoring Inca does 2. Describe Inca
+%2 design and its benefits 3. Illustrate that Inca 2 design is mature and
+%being used in production by several Grids 4. Be different from Inca 1 paper
+The goal of user-level Grid monitoring is to test and measure Grid
+infrastructure from an impartial user perspective and detect problems before
+users notice them.  Inca 2 implements such a user-level Grid monitoring system
+and provides a number of new and improved features over our first version,
+Inca 1.  The architecture and features of Inca 2 enable an Inca administrator
+to easily write and deploy tests and performance measurements to Grid
+resources and maintain them in a changing Grid environment.  The storage,
+archiving, and querying capabilities also enable in-depth analysis of Grid
+errors and performance in a historical context, which benefit Grid
+operators and system administrators.  Inca 2 also provides a number of
+security features such as short-term proxy management and supports
+scalability.  A production version of Inca 2 was released in February 2007 and
+has been used in production environments to verify the common user environment
+of TeraGrid and to execute and collect data for a set of Grid benchmarks on
+both TeraGrid and GEON.  Future enhancements of Inca 2 will improve its fault
+tolerance and enable more in-depth analysis of the overall Grid health and
+behavior.  They will also make it easier to detect and resolve errors
+and understand them in a historical context.  The features that Inca
+provides and its proposed enhancements improve the stability of the
+Grid infrastructure it monitors, ultimately improving the productivity of
+scientists who conduct research on a Grid.
+
+%------------------------------------------------------------------------- 
+\Section{Acknowledgements}
+
+This work was supported by the following NSF grants:  Cooperative Agreement
+Award \#0503944 SCI: TeraGrid Resource Partners,
 

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
changes to features
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6603 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
-because it may have special privileges and use custom shell initialization files.
+which may have special privileges and use custom shell initialization files.
 
-\item Executes with a standard user GSI
-credential, which is mapped to the standard user account, when tests or performance measurements require authentication to Grid services.
+\item Executes with a standard user GSI credential mapped to a standard user
+account when tests or performance measurements require authentication to Grid
+services.
 
-\item Emulates a regular user using tests and performance
-measurements that are written and configured using information directly from user documentation
-(e.g., hostnames, ports, pathnames, etc.). 
-This may not always be possible
-when documentation and testing are done in parallel in a pre-production
-environment, but they should be closely coordinated activities.
+\item Creates and configures tests and performance measurements based on user
+documentation rather than on system administrator knowledge (of hostnames,
+ports, pathnames, etc.).  This may not always be possible when documentation
+and tests are developed simultaneously during pre-production, but they should
+be closely coordinated activities.
 
-\item Centrally manages the configuration of user-level tests or performance measurements in order to ensure consistent testing of the resources, rather than
-by system administrators who may not use the same information that is
-available to users.
+\item Centrally manages the configuration of user-level tests or performance
+measurements in order to ensure consistent testing across resources.
 
-\item Is easy to update
-and maintain as user-level tests and performance measurements often need
-to be updated when the Grid infrastructure is upgraded.
-It is also difficult to write and deploy a test correctly the first time
-because of portability issues and incomplete user documentation.  Multiple
-iterations are usually required to determine whether a detected failure stems
-from a faulty test, user documentation, or Grid resource.
+\item Easily updates and maintains user-level tests and performance
+measurements.  This is important because tests and measurements are often
+updated when Grid infrastructure is upgraded.  Also, it is difficult to write
+and deploy a test correctly the first time due to portability issues and
+incomplete user documentation.  Multiple iterations are usually required to
+determine whether a detected failure stems from a faulty test, user
+documentation, or Grid resource.
 
-\item Provides a representative indication of Grid status by testing
+\item Represents overall Grid status by testing a variety of 
 documented user commands and individual Grid software components.
 
-\item Automates the execution of user-level tests or performance measurements
-periodically since Grids are dynamic.
+\item Automates the periodic execution of user-level tests or performance
+measurements to capture dynamic Grid status.
 
-\item Executes locally on all Grid
-resources when appropriate so that all Grid access points available to users
-are verified.  Similarly, it is important to execute some tests all-to-all
-in order to detect site-to-site configuration errors such as authentication
-problems.
+\item Executes locally on Grid resources to verify user accessible Grid access
+points.  Executes from each resource to every other resource (all-to-all) to
+detect site-to-site configuration errors such as authentication problems.
 

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
global edits - grammar changes and added citations
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6605 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\item Creates and configures tests and performance measurements based on user
+\item Emulates a regular user by using tests and performance measurements created and configured based on user
 documentation rather than on system administrator knowledge (of hostnames,
@@
 
-\item Represents overall Grid status by testing a variety of 
+\item Provides a representative indication of Grid status by testing
 documented user commands and individual Grid software components.
@@
 \item Automates the periodic execution of user-level tests or performance
-measurements to capture dynamic Grid status.
+measurements to understand Grid behavior over time.
 
@@
 \item Measures the system impact of tests and benchmarks executing on
-the monitored resources in order to tune their execution frequency to
-reduce the impact on the resources. *
+the monitored resources in order to tune their execution frequency and
+reduce the impact on resources if needed. *
 
@@
 % overview description of components
-Figure~\ref{arch_fig} shows the architecture of Inca 2.
-Inca 2 incorporates three core
+Figure~\ref{arch_fig} shows the architecture of Inca 2, which
+incorporates three core
 components (highlighted box):  the agent, depot, and reporter manager.
@@
 executes a system command (using a 30 second timeout) after logging it to the
-'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
+'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-37).  The subclass
 Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
-standard reporter body schema to report software functionality or service
+standard reporter body schema that reports software functionality or service
 tests results; it handles the printing of the small body XML
@@
 functionality test, or performance benchmark reporters.  The unit and version
-reporters cover software such as Grid middleware, compilers, math libraries,
+reporters cover software such as Grid middleware and tools, compilers, math libraries,
 data tools, and visualization tools.  Current performance reporters
@@
 complex scenario where two Inca deployments coordinate with each other.  For
-example, application communities like GEON have their own Grid but also have
+example, application communities like GEON~\cite{geon} have their own Grid but also have
 access to resources on TeraGrid.   Two separate Inca deployments can result in
@@
 
-To provide user-level monitoring of CTSSv3, Inca was originally
+To provide user-level monitoring of CTSS, Inca was originally
 deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
@@
 
-Other Inca users include the European DEISA Grid and the UK National Grid
-Service (NGS).  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
+Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
+Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
 Similar to TeraGrid, DEISA uses Inca to verify their Common

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
figure pass
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6606 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\item User-level tests or performance measurements of the Grid infrastructure
-should be run from a standard user
+\item Runs from a standard user
 account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
-because it may have special privileges and use custom shell initialization files.
+which may have special privileges and use custom shell initialization files.
 
-\item User-level tests or performance measurements that interact with Grid services
-require authentication and should be executed using a standard user GSI
-credential that is mapped to the standard user account.
+\item Executes with a standard user GSI credential mapped to a standard user
+account when tests or performance measurements require authentication to Grid
+services.
 
-\item User-level tests should be
-written and configured using information directly from user documentation
-(e.g., hostnames, ports, pathnames, etc.) to emulate a regular user.  
-This may not always be possible
-when documentation and testing are done in parallel in a pre-production
-environment, but they should be closely coordinated activities.
+\item Emulates a regular user by using tests and performance measurements created and configured based on user
+documentation rather than on system administrator knowledge (of hostnames,
+ports, pathnames, etc.).  This may not always be possible when documentation
+and tests are developed simultaneously during pre-production, but they should
+be closely coordinated activities.
 
-\item The configuration of user-level tests or performance measurements should be managed
-centrally in order to ensure consistent testing of the resources, rather than
-by system administrators who may not use the same information that is
-available to users.
+\item Centrally manages the configuration of user-level tests or performance
+measurements in order to ensure consistent testing across resources.
 
-\item User-level tests and performance measurements should be easy to update
-and maintain as they are often revised due to Grid infrastructure upgrades.
-It is also difficult to write and deploy a test correctly the first time
-because of portability issues and incomplete user documentation.  Multiple
-iterations are usually required to determine whether a detected failure stems
-from a faulty test, user documentation, or Grid resource.
+\item Easily updates and maintains user-level tests and performance
+measurements.  This is important because tests and measurements are often
+updated when Grid infrastructure is upgraded.  Also, it is difficult to write
+and deploy a test correctly the first time due to portability issues and
+incomplete user documentation.  Multiple iterations are usually required to
+determine whether a detected failure stems from a faulty test, user
+documentation, or Grid resource.
 
-\item Many types of user-level tests and benchmarks can be used to monitor 
-Grid infrastructure.  Testing documented user commands and individual Grid
-software components provides a representative indication of Grid status.
+\item Provides a representative indication of Grid status by testing
+documented user commands and individual Grid software components.
 
-\item Since Grids are dynamic, user-level tests or performance measurements
-should be automated and executed periodically.
+\item Automates the periodic execution of user-level tests or performance
+measurements to understand Grid behavior over time.
 
-\item User-level tests or performance measurements should be executed locally on all Grid
-resources when appropriate so that all Grid access points available to users
-are verified.  Similarly, it is important to execute some tests all-to-all
-in order to detect site-to-site configuration errors such as authentication
-problems.
+\item Executes locally on Grid resources to verify user accessible Grid access
+points.  Executes from each resource to every other resource (all-to-all) to
+detect site-to-site configuration errors such as authentication problems.
 
@@
 \noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
-1~\cite{inca1} to implement a user-level Grid monitoring system that followed
-the defined guidelines.  At that time, the only available user-level Grid
+1~\cite{inca1} to implement a user-level Grid monitoring system that provided
+these features.  At that time, the only available user-level Grid
 monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
@@
 operation of a Grid; system administrators who provide and manage resources;
-and users who run applications on a Grid.  Besides following the guidelines 
+and users who run applications on a Grid.  Besides implementing the features
 described in Section~\ref{intro}, Inca 2 has additional features
@@
 \caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
-availability of a Globus GRAM server and (b) sample output from a Globus GRAM 
-reporter.}
+availability of a Globus GRAM server and (b) sample of its output.}
 \end{figure}
@@
   \caption{\label{incat_fig} Screenshot of incat that shows the reporters
-  and their attributes available from the provided reporter repository.}
+  and their attributes available from the reporter repository.}
 \end{figure*}
@@
 series executing on TeraGrid resources.
-Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
+Figure~\ref{tg_deploy_fig}(a) illustrates TeraGrid's Inca 2 deployment
 configuration.  The
@@
 
-Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed grid of
+Figure~\ref{status_page_fig}(b) shows a portion of the TeraGrid detailed grid of
 CTSSv3 test results

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
Update.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6617 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 and a set of XSL stylesheets format the data as HTML.  An Inca administrator
-can customize the data display by either modifying the XSL stylesheets or
+can customize the data display, either by modifying the XSL stylesheets or by
 writing their own JSP tags and pages.
@@
 
-To reduce the security risk of Inca, all Inca components communicate with each
-other using SSL by default.  Sensitive information such as passwords is
-encrypted before being stored to disk on the agent.  To handle reporters that
-require a valid proxy credential to execute, the reporter manager fetches a
+To provide for security, all Inca components communicate with each other using
+SSL, and sensitive information is encrypted before being stored to disk.  To
+handle reporters that
+require a proxy credential to execute, the reporter manager fetches a
 short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
-administrator) and then destroys the proxy once the reporter has completed.
+administrator), then destroys the proxy once the reporter has completed.
 MyProxy authentication information is fetched from the agent each time a proxy
 credential is needed and then cleared from memory.  Generating short-term 
-proxies only when needed is more secure than maintaining long-term
+proxies as needed is more secure than maintaining long-term
 credentials and is easier to manage.
@@
 
-Inca was designed to distribute control and storage workload among
-multiple Inca components if needed.  For example, one depot could forward
-storage requests and queries to another depot to distribute its workload or to
-maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
-complex scenario where two Inca deployments coordinate with each other.  For
-example, application communities like GEON~\cite{geon} have their own Grid but also have
-access to resources on TeraGrid.   Two separate Inca deployments can result in
-duplicate testing. Instead, one Inca deployment can coordinate the execution
-of a suite with another deployment.
+A planned extension to Inca 2 supports the distribution of control and storage
+workload among multiple Inca components.  Figure~\ref{tg_coord_fig} shows a
+scenario where two Inca deployments coordinate with each other.  This could
+occur in application communities like GEON~\cite{geon}, which maintains its
+own Grid but also has access to TeraGrid resources.   Running two Inca
+deployments independently could result in duplicate testing.  Instead, we plan
+to eliminate redundancy by allowing multiple deployments to coordinate suite
+execution.
 Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
@@
 suites, Grid A's agent will execute the suite and configure its depot to
-forwards results back to Grid B's depot.  Forwarding is not yet implemented 
-in Inca 2.
+forwards results back to Grid B's depot.
 
@@
 on each TeraGrid resource.  As described in the introduction, CTSS was designed to
-allow users to more easily run Grid jobs across its distributed, heterogeneous
-resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
+allow users to run Grid jobs more easily across its distributed, heterogeneous
+resources.  CTSS version 3 (CTSSv3) is available on all TeraGrid compute
 resources and contains approximately 30 software packages that provide
@@
 
-To provide user-level monitoring of CTSS, Inca was originally
-deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
+To provide user-level monitoring of CTSS, Inca 1 was deployed on TeraGrid in
+2003 using Inca 1; TeraGrid transition to Inca 2 completed in
 November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
@@
 gather historical data, the GrASP probes were modified
-to follow the reporter specifications and deployed using Inca.
+to follow the Inca reporter specifications and deployed using Inca.
 Porting the original code to follow the reporter specifications proved to be
@@
 like Webalizer~\cite{webalizer} that provide a number of useful "Top"
-statistics.  We expect feedback from TeraGrid and other Inca users on the
-exact types of statistics and graphs that will prove to be most useful.  Our
-goal is to offer a default set of statistics and graphs that can be used out
-of the box and provide the capability to add others.
+statistics.  We expect to follow recommendations from TeraGrid and other Inca
+users on the types of statistics and graphs that will prove to be most useful.
+Our plan is to offer a default set of statistics and graphs that can be used
+directly and to provide the capability to add others.
 

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
changed scalability section title
added acknowledgements


git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6619 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-To reduce the security risk of Inca, all Inca components communicate with each
-other using SSL by default.  Sensitive information such as passwords is
-encrypted before being stored to disk on the agent.  To handle reporters that
-require a valid proxy credential to execute, the reporter manager fetches a
+To provide for security, all Inca components communicate with each other using
+SSL, and sensitive information is encrypted before being stored to disk.  To
+handle reporters that
+require a proxy credential to execute, the reporter manager fetches a
 short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
-administrator) and then destroys the proxy once the reporter has completed.
+administrator), then destroys the proxy once the reporter has completed.
 MyProxy authentication information is fetched from the agent each time a proxy
 credential is needed and then cleared from memory.  Generating short-term 
-proxies only when needed is more secure than maintaining long-term
+proxies as needed is more secure than maintaining long-term
 credentials and is easier to manage.
 
-\SubSection{Scalability}
+\SubSection{Coordinating Inca Deployments}
 
@@
 suites, Grid A's agent will execute the suite and configure its depot to
-forwards results back to Grid B's depot.  Forwarding is not yet implemented 
-in Inca 2.
+forwards results back to Grid B's depot.  This extension is also expected
+to provide the mechanisms for scalability and fault tolerance in the Inca
+system.
 
@@
 
-This work was supported by the following NSF grants:  Cooperative Agreement
-Award \#0503944 SCI: TeraGrid Resource Partners,
+The authors would like to thank Denis Girou and David Spence for providing
+details for the DEISA and NGS Inca deployments respectively.  This work was
+supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.
 

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
Update.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6664 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 and application users to identify, analyze, and troubleshoot user-level Grid
-failures thereby improving Grid stability.  In this paper, we describe the new
+failures, thereby improving Grid stability.  In this paper, we describe the new
 features of our current Inca release, Inca 2.  We then describe the
@@
 require the careful coordination of software packages, services, and
-configurations across multiple, potentially heterogeneous, resources.  The TeraGrid
-project~\cite{teragrid}, for example, manages the coordination of software and
-services by deploying and monitoring a common user environment across
-distributed, heterogeneous resources. 
+configurations across multiple, potentially heterogeneous, resources.  For
+example, the TeraGrid project~\cite{teragrid} manages the coordination of
+software and services by deploying and monitoring a common user environment
+across distributed, heterogeneous resources. 
 TeraGrid's software and services uniformity simplifies access to its
@@
 arise.  Well-defined requirements and good communication are required in this
-model.  Otherwise, inconsistencies arise between the resources that either
+model; otherwise, inconsistencies arise between the resources that either
 inconvenience the user or prevent them from using a particular resource
-altogether.  A second challenge is that failures will occur over
-time in the Grid services due to network or system failures, software
-misconfiguration, or software bugs. 
-Grid monitoring can be used to detect such problems, leading to a more
-stable and dependable Grid infrastructure.
+altogether.  Periodic failures that occur in Grid services due to network or
+system failures, software misconfiguration, or software bugs also present a
+challenge.  Grid monitoring can be used to detect such problems, leading to a
+more stable and dependable Grid infrastructure.
 
@@
 user complaints should not be the first indication of Grid failures.  
-In our view, the following are features of user-level Grid monitoring:
+In our view, a successful user-level Grid monitoring system needs to include
+these features:
 
@@
 
-\item Emulates a regular user by using tests and performance measurements created and configured based on user
-documentation rather than on system administrator knowledge (of hostnames,
-ports, pathnames, etc.).  This may not always be possible when documentation
-and tests are developed simultaneously during pre-production, but they should
-be closely coordinated activities.
+\item Emulates a regular user by using tests and performance measurements
+created and configured based on user
+documentation, rather than on system administrator knowledge (of hostnames,
+ports, pathnames, etc.).  In cases where documentation and tests are developed
+simultaneously during pre-production, test development should
+be closely coordinated with the documentation as it is written.
 
@@
 measurements.  This is important because tests and measurements are often
-updated when Grid infrastructure is upgraded.  Also, it is difficult to write
-and deploy a test correctly the first time due to portability issues and
-incomplete user documentation.  Multiple iterations are usually required to
-determine whether a detected failure stems from a faulty test, user
-documentation, or Grid resource.
+updated when Grid infrastructure changes.
+Also, multiple iterations of test development are often required to
+determine whether a detected test failure stems from a faulty test,
+incomplete user documentation, or a failed Grid resource.
 
@@
 resource, lacked automation, and were not easily extensible.  Inca 1 provided
-the means to verify the common user environment was deployed consistently across all TeraGrid
-resources and monitored its status.
+the means to verify that the common user environment was deployed consistently
+across all TeraGrid resources and to monitor its status.
 
@@
 security, installation and maintenance, and storage capabilities.  Inca 2 has
-been running on TeraGrid since November 2006 and a production
+been running on TeraGrid since November 2006, and a production
 version of the software was released in February 2007.  Currently, seven other Grids in the
@@
 and maintain.  Inca benefits Grid operators who oversee the day-to-day
-operation of a Grid; system administrators who provide and manage resources;
+operation of a Grid, system administrators who provide and manage resources,
 and users who run applications on a Grid.  Besides implementing the features
 described in Section~\ref{intro}, Inca 2 has additional features
-listed below.  A '*' after the feature description indicates it is a new
+listed below.  A '*' after a feature description indicates it is a new
 feature of Inca 2; other items note improvements to Inca 1 features.  The 
@@
 the monitored resources in order to tune their execution frequency and
-reduce the impact on resources if needed. *
+reduce the impact on resources as needed. *
 
@@
 incorporates three core
-components (highlighted box):  the agent, depot, and reporter manager.
+components (highlighted box) -- the agent, depot, and reporter manager.
 The \textit{agent} and \textit{reporter managers} coordinate the execution of
@@
 \item Each reporter manager executes reporters according to its schedule and
-sends results (reports) to the depot.
+sends data to the depot.
 
-\item Data consumers display collected data (reports) by querying the depot.
+\item Data consumers display collected data by querying the depot.
 \end{enumerate}
@@
 % What are repositories and their key features
-Reporter repositories are collections that consist of reporters, required
+Reporter repositories are collections of reporters, required
 packages and libraries (including the Perl APIs described in the previous
@@
 sources.  Inca automatically deploys dependencies into a
-subdirectory of its installation (more in Section~\ref{agent}); this enables
+subdirectory of its installation (see Section~\ref{agent}); this enables
 reporters to be deployed to resources with minimal delay.  Each package
@@
 The Inca team publishes a reporter repository that contains 143 reporters
-developed and tested for TeraGrid.  Most reporters are either version
+developed for TeraGrid.  Most reporters are either version
 reporters that collect version information from a software package,
@@
 % effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a Java Swing GUI that an
-Inca administrator uses to configure user-level Grid monitoring on their
+The Inca administrative tool (incat) is a Java Swing GUI that
+Inca administrators use to configure user-level Grid monitoring on their
 resources.  Incat allows an Inca administrator to choose which resources to
 monitor and which reporters to deploy to those resources.  The configuration
-is stored in a XML file and sent to the agent, which handles the implementation
-(as described in the next section).  The Inca administrator can reload the
-configuration at any point and make updates.  Incat provides a number of
+is stored in a XML file and sent to the agent, which handles its implementation
+(described in the next section).  The Inca administrator can reload the
+configuration to make updates.  Incat provides a number of
 conveniences that enable a large number of results to be managed and collected
@@
 input arguments, the runtime environment, the frequency of execution, resource
-limits, and email notifications.  The reports that a reporter produces on a
-resource when executed with specific set of input arguments and runtime
-environment are known as a \emph{report series} (or \emph{series} for short).
+limits, and email notifications.  The sequence of reports that a reporter
+produces on a resource when executed with specific set of input arguments and
+runtime environment is known as a \emph{report series} (or \emph{series} for
+short).
 Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
@@
 be restarted.  The agent also maintains a local cache of reporters and their
-dependencies; it periodically checks repositories (every 4 hours by default)
+dependencies; it periodically checks repositories
 and automatically distributes reporter updates to the reporter managers as
@@
 System usage information is sent to the depot with each report. 
-The reporter manager is implemented using Perl to make it easy to install on
+The reporter manager is implemented using Perl to allow execution on
 a wide variety of UNIX systems.
@@
 tests to run on reports as they are received, and the depot will send email
-when the results of these comparisons change.  This provides the administrator
+when the results of these tests change.  This provides the administrator
 with quick notification of problems as they appear and of the results of
@@
 
-Data can be queried using SQL queries. Predefined queries exist to return the
+Data can be retrieved using SQL queries. Predefined queries exist to return the
 latest report instances of a suite, a single report instance, or a report
@@
 To provide for security, all Inca components communicate with each other using
-SSL, and sensitive information is encrypted before being stored to disk.  To
+SSL, and sensitive information is encrypted before being written to disk.  To
 handle reporters that
@@
 To provide user-level monitoring of CTSS, Inca 1 was deployed on TeraGrid in
-2003 using Inca 1; TeraGrid transition to Inca 2 completed in
+2003; TeraGrid transition to Inca 2 completed in
 November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
@@
 agent, depot and consumer components are hosted at SDSC on 
-sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
+sapa.sdsc.edu.  A reporter repository for TeraGrid is hosted
 at SDSC on inca.sdsc.edu.
@@
 Similar to TeraGrid, DEISA uses Inca to verify their Common
-Production Environment (DCPE) across their 11 heterogeneous resources.  They
+Production Environment (DCPE) across 11 heterogeneous resources.  They
 currently have 40 version reporters to verify each of the packages included in
@@
 summary displays analogous to those generated by Web page statistics packages
-like Webalizer~\cite{webalizer} that provide a number of useful "Top"
+like Webalizer~\cite{webalizer} that provide a number of useful
 statistics.  We expect to follow recommendations from TeraGrid and other Inca
-users on the types of statistics and graphs that will prove to be most useful.
+users on the types of statistics and graphs that will be most useful.
 Our plan is to offer a default set of statistics and graphs that can be used
@@
 we plan to enhance Inca with a knowledge base that can be used to
-suggest solutions to problems (or point to known bugs if there is no solution
-available).  The knowledge base would be populated by solutions provided by
-system administrators -- the content would be self-moderated in order to
-improve its quality (by voting or adding comments to each other's
-contributions).  A knowledge base could provide a potentially vital resource
+discuss problems and suggest solutions.
+The knowledge base will be populated by solutions provided by
+system administrators, self-moderated to
+improve quality.
+This knowledge base could provide a vital resource
 for system administrators and offer a forum for sharing
-invaluable experience and skills.
+valuable experience and skills.
 
@@
 operators and system administrators.  Inca 2 also provides a number of
-security features such as short-term proxy management and supports
-scalability.  A production version of Inca 2 was released in February 2007 and
+security features such as short-term proxy management
+A production version of Inca 2 was released in February 2007 and
 has been used in production environments to verify the common user environment
@@
 The authors would like to thank Denis Girou and David Spence for providing
-details for the DEISA and NGS Inca deployments respectively.  This work was
+details for the DEISA and NGS Inca deployments, respectively.  This work was
 supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
minor corrections - perhaps the last!
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6665 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 input arguments, the runtime environment, the frequency of execution, resource
-limits, and email notifications.  The reports that a reporter produces on a
-resource when executed with specific set of input arguments and runtime
-environment are known as a \emph{report series} (or \emph{series} for short).
+limits, and email notifications.  The sequence of reports that a reporter
+produces on a resource when executed with a specific set of input arguments and
+runtime environment is known as a \emph{report series} (or \emph{series} for
+short).
 Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
@@
 The depot provides full archiving of reporter output, and the database schema is
-tuned to minimize redundant data.  Inca administrators can specify comparison
+tuned to minimize redundant data.  Inca administrators can specify pattern
 tests to run on reports as they are received, and the depot will send email
-when the results of these comparisons change.  This provides the administrator
+when the results of these tests change.  This provides the administrator
 with quick notification of problems as they appear and of the results of
@@
 
-\SubSection{Scalability}
+\SubSection{Coordinating Inca Deployments}
 
@@
 suites, Grid A's agent will execute the suite and configure its depot to
-forwards results back to Grid B's depot.
+forwards results back to Grid B's depot.  This extension is also expected
+to provide the mechanisms for scalability and fault tolerance in the Inca
+system.
 
@@
 Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
-Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
+Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005, respectively.  
 Similar to TeraGrid, DEISA uses Inca to verify their Common
-Production Environment (DCPE) across their 11 heterogeneous resources.  They
+Production Environment (DCPE) across 11 heterogeneous resources.  They
 currently have 40 version reporters to verify each of the packages included in
@@
 we plan to enhance Inca with a knowledge base that can be used to
-suggest solutions to problems (or point to known bugs if there is no solution
-available).  The knowledge base would be populated by solutions provided by
-system administrators -- the content would be self-moderated in order to
-improve its quality (by voting or adding comments to each other's
-contributions).  A knowledge base could provide a potentially vital resource
+discuss problems and suggest solutions.
+The knowledge base will be populated by solutions provided by
+system administrators and self-moderated to
+improve quality.
+This knowledge base could provide a vital resource
 for system administrators and offer a forum for sharing
-invaluable experience and skills.
+valuable experience and skills.
 
@@
 
-This work was supported by the following NSF grants:  Cooperative Agreement
-Award \#0503944 SCI: TeraGrid Resource Partners,
+The authors would like to thank Denis Girou and David Spence for providing
+details for the DEISA and NGS Inca deployments, respectively.  This work was
+supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.
 

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
last changes!
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6666 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 user complaints should not be the first indication of Grid failures.  
-In our view, a successful user-level Grid monitoring system needs to include
+In our view, successful user-level Grid monitoring needs to include
 these features:
@@
 To provide user-level monitoring of CTSS, Inca 1 was deployed on TeraGrid in
-2003; TeraGrid transition to Inca 2 completed in
+2003; TeraGrid's transition to Inca 2 completed in
 November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
@@
 operators and system administrators.  Inca 2 also provides a number of
-security features such as short-term proxy management
+security features such as short-term proxy management.
 A production version of Inca 2 was released in February 2007 and

### 2007-04-16 papers/hpdc-gmw-2007/paper.tex
modification to add industry tools
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6852 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 high-level monitoring needed to detect user problems, such as incompatible
-software versions, within the Grid infrastructure.
+software components, within the Grid infrastructure.  Industry monitoring
+tools are also available such as IBM Tivoli Monitoring~\cite{tivoli} and
+Microsoft Operations Manager~\cite{mom}, which monitor and manage large
+networks of services.  However, these tools depend on proprietary software and
+are targeted to a single administrative domain, which is unsuitable for Grid
+systems that span multiple administrative domains.
 
@@
 from a generic, impartial user's perspective.  The goal of user-level monitoring is 
-to detect and fix Grid infrastructure problems before users notice them -- 
+to detect and fix Grid infrastructure problems before users notice them by
+notifying site system administrators and providing them with the error details -- 
 user complaints should not be the first indication of Grid failures.  
-In our view, a successful user-level Grid monitoring system needs to include
+In our view, successful user-level Grid monitoring needs to include
 these features:
@@
 limits, and email notifications.  The sequence of reports that a reporter
-produces on a resource when executed with specific set of input arguments and
+produces on a resource when executed with a specific set of input arguments and
 runtime environment is known as a \emph{report series} (or \emph{series} for
@@
 The depot provides full archiving of reporter output, and the database schema is
-tuned to minimize redundant data.  Inca administrators can specify comparison
+tuned to minimize redundant data.  Inca administrators can specify pattern
 tests to run on reports as they are received, and the depot will send email
@@
 Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
-Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
+Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005, respectively.  
 Similar to TeraGrid, DEISA uses Inca to verify their Common
@@
 The knowledge base will be populated by solutions provided by
-system administrators, self-moderated to
+system administrators and self-moderated to
 improve quality.

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
template changes for final version to be printed
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6855 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\documentclass[times,10pt,twocolumn]{article} 
-\usepackage{dblfloatfix}
+\documentclass{sig-alternate}
 \usepackage{epsfig}
-\usepackage{latex8}
 \usepackage{listings}
 \usepackage{subfigure}
-\usepackage{times}
 \usepackage{url}
@@
 %------------------------------------------------------------------------- 
-% take the % away on next line to produce the final camera-ready version 
-% takes away page numbers
-\pagestyle{empty}
+% Begin patch area for accents in 'Author Block' area - may be needed by
+% some authors / but not all
+\DeclareFixedFont{\auacc}{OT1}{phv}{m}{n}{12}   % Needed for "Author Block" accents - Patch by Gerry 3/21/07
+\DeclareFixedFont{\afacc}{OT1}{phv}{m}{n}{10}   % Needed for "Author Block" accents in the affiliation/address line - Patch by Gerry 3/21/07
+%-------------------------------------------------------------------------
 
-% some unnecessary whitespace still -- these suggestions from
-% http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/squeeze.html
-\renewcommand\dblfloatpagefraction{.95}
-\renewcommand\dbltopfraction{.95}
-\renewcommand\bottomfraction{.95}
-\renewcommand\textfraction{.05}   
-\setcounter{totalnumber}{50}
-\setcounter{dbltopnumber}{50}
-\setcounter{bottomnumber}{50}
+\begin{document}
 
-%------------------------------------------------------------------------- 
-\begin{document}
+\conferenceinfo{HPDC'07,} {June 25--29, 2007, Monterey, California, USA.}
+\CopyrightYear{2007}
+\crdata{978-1-59593-673-8/07/0006}
 
@@
 
-\author{Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
-San Diego Supercomputer Center\\ University of California, San Diego\\ 
-9500 Gilman Drive, La Jolla, CA 92093-0505, USA\\ 
-\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu\\
+\numberofauthors{1}
+
+\author{
+\alignauthor
+Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
+\affaddr{San Diego Supercomputer Center} \\ 
+\affaddr{University of California, San Diego} \\ 
+\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
+\email{\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu}\\
 }
@@
 \maketitle
-\thispagestyle{empty}
 
@@
 %-------------------------------------------------------------------------
-\Section{Introduction}
+
+% A category with the (minimum) three required fields
+\category{C.4}{Performance Of Systems}{Performance attributes, Reliability,
+availability, and serviceability}
+
+\terms{Performance, Reliability, Verification}
+
+\keywords{User-level Grid monitoring, Grid monitoring, TeraGrid}
+
+%------------------------------------------------------------------------- 
+\section{Introduction}
 \label{intro}
@@
 from a generic, impartial user's perspective.  The goal of user-level monitoring is 
-to detect and fix Grid infrastructure problems before users notice them -- 
+to detect and fix Grid infrastructure problems before users notice them by
+notifying site system administrators and providing them with the error details -- 
 user complaints should not be the first indication of Grid failures.  
@@
 %------------------------------------------------------------------------- 
-\Section{Inca 2 Features}
+\section{Inca 2 Features}
 
@@
 %------------------------------------------------------------------------- 
-\Section{Inca 2 Architecture}
+\section{Inca 2 Architecture}
 
@@
 
-\SubSection{Reporters}
+\subsection{Reporters}
 
@@
 
-\SubSection{Reporter Repositories}
+\subsection{Reporter Repositories}
 
@@
 
-\SubSection{Inca administration tool (incat)}
+\subsection{Inca administration tool (incat)}
 
@@
 
-\SubSection{Agent}
+\subsection{Agent}
 \label{agent}
@@
 
-\SubSection{Reporter Manager}
+\subsection{Reporter Manager}
 \label{rm}
@@
 
-\SubSection{Depot}
+\subsection{Depot}
 
@@
 
-\SubSection{Data Consumer}
+\subsection{Data Consumer}
 
@@
 
-\SubSection{Security}
+\subsection{Security}
 \label{security}
@@
 
-\SubSection{Coordinating Inca Deployments}
+\subsection{Coordinating Inca Deployments}
 
@@
 
-\Section{Use Cases}
+\section{Use Cases}
 \label{usecases}
 
-\SubSection{TeraGrid}
+\subsection{TeraGrid}
 
@@
 
-\SubSection{GrASP}
+\subsection{GrASP}
 \label{grasp}
@@
 
-\SubSection{Other Uses}
+\subsection{Other Uses}
 
@@
 %------------------------------------------------------------------------- 
-\Section{Future Work}
+\section{Future Work}
 
@@
 %------------------------------------------------------------------------- 
-\Section{Summary}
+\section{Summary}
 
@@
 %------------------------------------------------------------------------- 
-\Section{Acknowledgements}
+\section{Acknowledgements}
 
@@
 %------------------------------------------------------------------------- 
-\bibliographystyle{latex8}
+\bibliographystyle{abbrv}
 \bibliography{paper}

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
split figure 5 into two figures since we have the space
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6856 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-%\begin{figure}[tbp]
-%  \centering
-%  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
-%  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
-%\end{figure}
-%\begin{figure}[tbp]
-%  \centering
-%  \includegraphics[width=.4\textwidth]{status-page.eps}
-%  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
-%\end{figure}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
+  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
+\end{figure}
 
 \begin{figure*}[tbp]
-\subfigure[]{\includegraphics[width=.8\columnwidth]{tg-deploy.eps}}
-\subfigure[]{\includegraphics[width=.6\textwidth]{status-page.eps}}
-  \caption{\label{tg_deploy_fig}\label{status_page_fig} (a) TeraGrid's Inca 2
-  deployment and (b) portion of the TeraGrid CTSSv3 detailed status page with
-  the resources anonymized.}
+  \centering
+  \includegraphics[width=.75\textwidth]{status-page.eps}
+  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
 \end{figure*}

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
fix font in code listings
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6857 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \lstset{
-  basicstyle=\scriptsize\ttfamily, 
+  basicstyle=\scriptsize\fontfamily{phv}\selectfont, 
   frame=single,
@@
   identifierstyle=, 
-  commentstyle=\scriptsize\ttfamily, 
-  stringstyle=\ttfamily, 
+  commentstyle=\scriptsize, 
+  stringstyle=, 
   numbers=left, 

### 2007-04-17 papers/hpdc-gmw-2007/gmw01c-smallen.tex
rename to include last name not email address
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6861 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
more name changes
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6862 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
embed bbl into tex as asked by sheridan
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6863 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
@@
 executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
+\linebreak Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter)
+\linebreak and
 Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
@@
 %-------------------------------------------------------------------------
+
 \bibliographystyle{abbrv}
-\bibliography{paper}
+\begin{thebibliography}{10}
+
+\bibitem{gridice}
+S.~Andreozzi, N.~D. Bortoli, S.~Fantinel, A.~Ghiselli, G.~L. Rubini,
+  G.~Tortone, and M.~C. Vistoli.
+\newblock {GridICE: a monitoring service for Grid systems}.
+\newblock {\em {Future Generation Computer Systems}}, 21(4):559--571, 2005.
+
+\bibitem{grasp}
+G.~Chun, H.~Dail, H.~Casanova, and A.~Snavely.
+\newblock {Benchmark Probes for Grid Assessment}.
+\newblock April 2004.
+
+\bibitem{clumon}
+{Clumon Web page}.
+\newblock \url{http://clumon.ncsa.uiuc.edu}, 2007.
+
+\bibitem{apt}
+{Debian -- The Universal Operating System}.
+\newblock \url{http://www.debian.org}, 2007.
+
+\bibitem{deisa}
+{Deisa - Distributed European Infrastructure for Supercomputing Appications}.
+\newblock \url{http://www.deisa.eu/}, 2007.
+
+\bibitem{globus}
+I.~Foster and C.~Kesselman.
+\newblock {Globus: A Metacomputing Infrastructure Toolkit}.
+\newblock {\em International Journal of Supercomputer Applications},
+  11(2):115--128, 1997.
+
+\bibitem{hibernate}
+{Hibernate Web page}.
+\newblock \url{http://www.hibernate.org}, 2007.
+
+\bibitem{jetty}
+{Jetty Web page}.
+\newblock \url{http://jetty.mortbay.org}, 2007.
+
+\bibitem{grasp2}
+O.~Khalili, J.~He, C.~Olschanowsky, A.~Snavely, and H.~Casanova.
+\newblock {Measuring the Performance and Reliability of Production
+  Computational Grids}.
+\newblock September 2006.
+
+\bibitem{monalisa}
+I.~Legrand, H.~Newman, R.~Voicu, C.~Cirstoiu, C.~Grigoras, M.~Toarta, and
+  C.~Dobre.
+\newblock {MonALISA: An Agent based, Dynamic Service System to Monitor, Control
+  and Optimize Grid based Applications}.
+\newblock In {\em CHEP 2004}, Interlaken, Switzerland, September 2004.
+
+\bibitem{log4j}
+{Log4J Project Web page}.
+\newblock \url{http://logging.apache.org/log4j}, 2007.
+
+\bibitem{ganglia}
+M.~Massie, B.~Chun, and D.~Culler.
+\newblock { The Ganglia Distributed Monitoring System: Design, Implementation,
+  and Experience}.
+\newblock {\em Parallel Computing}, April 2004.
+
+\bibitem{mom}
+{Microsoft Operations Manager}.
+\newblock \url{http://www.microsoft.com/mom}, 2007.
+
+\bibitem{myproxy}
+{MyProxy Credential Management Service}.
+\newblock \url{http://myproxy.ncsa.uiuc.edu}, 2007.
+
+\bibitem{ngs}
+{NGS Web page}.
+\newblock \url{http://www.grid-support.ac.uk}, 2007.
+
+\bibitem{ncsa-test}
+{NCSA TestGrid Project}.
+\newblock \url{http://grid.ncsa.uiuc.edu/test}, 2007.
+
+\bibitem{nagios}
+{Nagios Web page}.
+\newblock \url{http://www.nagios.org}, 2007.
+
+\bibitem{geon}
+A.~K. Sinha, B.~Ludaescher, B.~Brodaric, C.~Baru, D.~Seber, A.~Snoke, and
+  C.~Barnes.
+\newblock { GEON: Developing the Cyberinfrastructure for the Earth Sciences - A
+  Workshop Report on Intrusive Igneous Rocks, Wilson Cycle and Concept Spaces}.
+\newblock {\em Submitted to GSA Today}.
+
+\bibitem{inca1}
+S.~Smallen, C.~Olschanowsky, K.~Ericson, P.~Beckman, and J.~M. Schopf.
+\newblock {The Inca Test Harness and Reporting Framework}.
+\newblock In {\em Proceedings of Supercomputing 04}, November 2004.
+
+\bibitem{teragrid}
+{The TeraGrid Project Web page}.
+\newblock \url{http://www.teragrid.org}, 2007.
+
+\bibitem{tivoli}
+{IBM Tivoli Monitoring Web page}.
+\newblock \url{http://www.ibm.com/software/tivoli/products/monitor/}, 2007.
+
+\bibitem{gits}
+{The UK Grid Integration Test Script - GITS}.
+\newblock \url{http://www.soton.ac.uk/~djb1/gits.html}, 2007.
+
+\bibitem{webalizer}
+{Webalizer Web page}.
+\newblock \url{http://www.mrunix.net/webalizer/}, 2007.
+
+\end{thebibliography}
 

### 2012-07-13 pubs/papers/inca-analysis/Inca-anaylsis.tex
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@14851 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

--- 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
@@
-%
-%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
-%
-%  $Author: ienne $
-%  $Date: 1995/09/15 15:20:59 $
-%  $Revision: 1.4 $
-%
-
 \documentclass{sig-alternate}
-\usepackage{epsfig}
-\usepackage{listings}
-\usepackage{subfigure}
-\usepackage{url}
-
-%------------------------------------------------------------------------- 
-% Begin patch area for accents in 'Author Block' area - may be needed by
-% some authors / but not all
-\DeclareFixedFont{\auacc}{OT1}{phv}{m}{n}{12}   % Needed for "Author Block" accents - Patch by Gerry 3/21/07
-\DeclareFixedFont{\afacc}{OT1}{phv}{m}{n}{10}   % Needed for "Author Block" accents in the affiliation/address line - Patch by Gerry 3/21/07
-%-------------------------------------------------------------------------
+\usepackage{subfigure,url}
 
@@
 
-\conferenceinfo{HPDC'07,} {June 25--29, 2007, Monterey, California, USA.}
-\CopyrightYear{2007}
-\crdata{978-1-59593-673-8/07/0006}
-
-\title{User-level Grid Monitoring with Inca 2}
+\title{}
 
@@
 \alignauthor
-Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
-\affaddr{San Diego Supercomputer Center} \\ 
+Shava Smallen, Sameer Tilak, etc. \\
 \affaddr{University of California, San Diego} \\ 
 \affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
-\email{\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu}\\
+\email{\{ssmallen,sameer\}@sdsc.edu}\\
 }
@@
 
-%1.  Motivate and differentiate the Grid monitoring Inca does
-%2. Describe Inca 2 design and its benefits
-%3. Illustrate that Inca 2 design is mature and being used in production by
-%several Grids
-%4. Be different from Inca 1 paper
+\begin{abstract}
 
-\begin{abstract}
-The primary goal in the creation of Grids is to provide unified and coherent
-access to distributed computing, data storage and analysis, instruments, and
-other resources to advance scientific exploration.  Grids combine multiple
-complex and interdependent systems that span several administrative domains.
-This complexity poses challenges for both the administrators who build and
-maintain the Grid resources and the scientists who use them.  While other Grid
-monitoring tools provide system-level information on the utilization of Grid
-resources, the Inca system provides user-level Grid monitoring with periodic,
-automated user-level testing of the software and services required to support
-Grid operation.  Inca can be used by Grid operators, system administrators,
-and application users to identify, analyze, and troubleshoot user-level Grid
-failures, thereby improving Grid stability.  In this paper, we describe the new
-features of our current Inca release, Inca 2.  We then describe the
-architecture of the Inca 2 system, in addition to use cases that describe two
-Inca 2 deployments in production environments.  
 \end{abstract}
 
-%-------------------------------------------------------------------------
-
-% A category with the (minimum) three required fields
-\category{C.4}{Performance Of Systems}{Performance attributes, Reliability,
-availability, and serviceability}
-
-\terms{Performance, Reliability, Verification}
-
-\keywords{User-level Grid monitoring, Grid monitoring, TeraGrid}
-
-%------------------------------------------------------------------------- 
-\section{Introduction}
-\label{intro}
-
-% Standard "Grids are good" intro paragraph.  But are complex.  
-Grid systems provide unified and coherent access to distributed computing,
-data storage and analysis, instruments, and other resources.  These systems
-require the careful coordination of software packages, services, and
-configurations across multiple, potentially heterogeneous, resources.  For
-example, the TeraGrid project~\cite{teragrid} manages the coordination of
-software and services by deploying and monitoring a common user environment
-across distributed, heterogeneous resources. 
-TeraGrid's software and services uniformity simplifies access to its
-resources, which consist of more than 102 teraflops of compute capability and
-more than 15 petabytes of online storage, all interconnected by a network that
-can transfer a terabyte of data in under 10 minutes.
-
-% Complex means they are difficult to provide and maintain. Describe the
-% stakeholders.   Monitoring is needed.
-Providing and maintaining a stable infrastructure for these complex 
-Grid systems poses challenges for both administrators who build and
-maintain Grid resources and scientists who use them.  System
-administration is distributed across multiple administrative domains 
-requiring a significant amount of coordination.  This is typically performed by
-a group of Grid administrators or operators who consider local site policies and
-resource heterogeneity
-and decide when software (including updates and patches) should be deployed to
-resources and how it should be configured.  
-Each site's system administrators, who are not necessarily Grid
-experts, are then responsible for providing the required Grid software
-components and services for their resource and debugging any problems that
-arise.  Well-defined requirements and good communication are required in this
-model; otherwise, inconsistencies arise between the resources that either
-inconvenience the user or prevent them from using a particular resource
-altogether.  Periodic failures that occur in Grid services due to network or
-system failures, software misconfiguration, or software bugs also present a
-challenge.  Grid monitoring can be used to detect such problems, leading to a
-more stable and dependable Grid infrastructure.
-
-% What types of Grid monitoring are around and what the limitations are
-One approach to monitoring Grids, used by tools such as
-MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
-display data from existing cluster or system administrator monitoring tools
-such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
-Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
-resources where low-level host statistics and queue information can be
-examined.  This type of monitoring information is useful for showing the
-utilization of Grid resources, but it does not provide the type of
-high-level monitoring needed to detect user problems, such as incompatible
-software components, within the Grid infrastructure.  Industry monitoring
-tools are also available such as IBM Tivoli Monitoring~\cite{tivoli} and
-Microsoft Operations Manager~\cite{mom}, which monitor and manage large
-networks of services.  However, these tools depend on proprietary software and
-are targeted to a single administrative domain, which is unsuitable for Grid
-systems that span multiple administrative domains.
-
-% What user-level monitoring provides and why we think it is good
-User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
-from a generic, impartial user's perspective.  The goal of user-level monitoring is 
-to detect and fix Grid infrastructure problems before users notice them by
-notifying site system administrators and providing them with the error details -- 
-user complaints should not be the first indication of Grid failures.  
-In our view, successful user-level Grid monitoring needs to include
-these features:
-
-\begin{itemize}
-
-\item Runs from a standard user
-account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
-which may have special privileges and use custom shell initialization files.
-
-\item Executes with a standard user GSI credential mapped to a standard user
-account when tests or performance measurements require authentication to Grid
-services.
-
-\item Emulates a regular user by using tests and performance measurements
-created and configured based on user
-documentation, rather than on system administrator knowledge (of hostnames,
-ports, pathnames, etc.).  In cases where documentation and tests are developed
-simultaneously during pre-production, test development should
-be closely coordinated with the documentation as it is written.
-
-\item Centrally manages the configuration of user-level tests or performance
-measurements in order to ensure consistent testing across resources.
-
-\item Easily updates and maintains user-level tests and performance
-measurements.  This is important because tests and measurements are often
-updated when Grid infrastructure changes.
-Also, multiple iterations of test development are often required to
-determine whether a detected test failure stems from a faulty test,
-incomplete user documentation, or a failed Grid resource.
-
-\item Provides a representative indication of Grid status by testing
-documented user commands and individual Grid software components.
-
-\item Automates the periodic execution of user-level tests or performance
-measurements to understand Grid behavior over time.
-
-\item Executes locally on Grid resources to verify user accessible Grid access
-points.  Executes from each resource to every other resource (all-to-all) to
-detect site-to-site configuration errors such as authentication problems.
-
-\end{itemize}
-
-% Inca 1~\cite{inca1} first addressed user-level Grid monitoring but had
-% limitations.  We learned lessons from our TeraGrid deployment and
-% developed Inca 2.
-
-\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
-1~\cite{inca1} to implement a user-level Grid monitoring system that provided
-these features.  At that time, the only available user-level Grid
-monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
-Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
-results in HTML.  Although these tools were easy to install and produced
-useful information, they showed the view of the Grid from a single
-resource, lacked automation, and were not easily extensible.  Inca 1 provided
-the means to verify that the common user environment was deployed consistently
-across all TeraGrid resources and to monitor its status.
-
-The initial
-version of Inca was implemented as a client-server architecture.  It provided
-data collection, data storage (accessible from a Web services interface and with 
-limited archiving capabilities), and data display though Web status
-pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
-2003. Running Inca 1 for a year and a half on TeraGrid taught 
-valuable lessons that have been incorporated into the design of Inca 2, our
-current release.  Inca 2
-contains a number of substantial improvements over Inca 1 with respect to
-security, installation and maintenance, and storage capabilities.  Inca 2 has
-been running on TeraGrid since November 2006, and a production
-version of the software was released in February 2007.  Currently, seven other Grids in the
-U.S., Europe, and Australia use Inca 2.
-
-% This motivated our development of a new version of Inca.
-In the next section, we describe the design goals and features of Inca 2. 
-We then describe the Inca 2 architecture and how it can be used to provide
-user-level Grid monitoring.  In Section~\ref{usecases}, we describe two 
-uses of Inca 2 for Grid software environment verification and benchmarking.  
-Finally, we describe some future work and summarize the paper.
-
-%------------------------------------------------------------------------- 
-\section{Inca 2 Features}
-
-\begin{figure*}[tbp]
-  \centering
-  \includegraphics[width=.6\textwidth]{arch.eps}
-  \caption{\label{arch_fig} Inca architecture.}
-\end{figure*}
-
-% Implements user-level Grid monitoring and who it benefits
-Inca 2 is a system that provides user-level monitoring of Grid functionality
-and performance.  It was designed to be
-general, flexible, scalable, and secure, in addition to being easy to deploy
-and maintain.  Inca benefits Grid operators who oversee the day-to-day
-operation of a Grid, system administrators who provide and manage resources,
-and users who run applications on a Grid.  Besides implementing the features
-described in Section~\ref{intro}, Inca 2 has additional features
-listed below.  A '*' after a feature description indicates it is a new
-feature of Inca 2; other items note improvements to Inca 1 features.  The 
-Inca system:
-
-\begin{enumerate}
-
-\item Collects a wide variety of user-level monitoring results (e.g., simple
-test data to more complex performance benchmark output).
-
-\item Captures the context of a test or benchmark as it executes (e.g.,
-executable name, inputs, source host, etc.) so that system administrators have
-enough information to understand the result and can troubleshoot system
-problems without having to know the internals of Inca.
-
-\item Eases the process of writing tests or benchmarks and deploying them into
-Inca installations.
-
-\item Provides means for sharing tests and benchmarks between Inca users. *
-
-\item Easily adapts to new resources and monitoring requirements in order to
-facilitate maintenance of a running Inca deployment.
-
-\item Stores and archives monitoring results (especially any error messages) 
-in order to understand the behavior of a Grid over time. The results
-are available through a flexible querying interface.
-
-\item Securely manages short-term proxies for testing of Grid services using
-MyProxy~\cite{myproxy}. *
-
-\item Measures the system impact of tests and benchmarks executing on
-the monitored resources in order to tune their execution frequency and
-reduce the impact on resources as needed. *
-
-\end{enumerate}
-
-\noindent The following section describes how the Inca architecture implements
-these features.
-
-%------------------------------------------------------------------------- 
-\section{Inca 2 Architecture}
-
-% overview description of components
-Figure~\ref{arch_fig} shows the architecture of Inca 2, which
-incorporates three core
-components (highlighted box) -- the agent, depot, and reporter manager.
-The \textit{agent} and \textit{reporter managers} coordinate the execution of
-tests and performance measurements on the Grid resources and the
-\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
-or more \textit{reporter repositories} that contain user-level tests and
-benchmarks, called \textit{reporters}, and a configuration file describing how
-to execute them on the Grid resources.  This configuration is normally created
-using an administration GUI tool
-called \textit{incat} (Inca Administration Tool).  The output or results
-collected from the resources are queried by the \textit{data consumer} and
-displayed to users.  The following steps describe how an Inca administrator
-would deploy user-level tests and/or performance measurements to their
-resources.
-
-\begin{enumerate}
-
-\item The Inca
-administrator either writes reporters to monitor the user-level functionality
-and performance of their Grid or uses existing
-reporters in a published repository.
-
-\item The Inca administrator creates a deployment configuration file that
-describes the user-level monitoring for their Grid using incat and submits it
-to the agent.
-
-\item The agent fetches reporters from the reporter repository, creates a
-reporter manager on each resource, and sends the reporters and instructions for
-executing them to each reporter manager.
-
-\item Each reporter manager executes reporters according to its schedule and
-sends data to the depot.
-
-\item Data consumers display collected data by querying the depot.
-\end{enumerate}
-
-\noindent The following subsections describe the Inca components in more
-detail, using the order of the steps above.
-
-\subsection{Reporters}
-
-\lstset{
-  basicstyle=\scriptsize\fontfamily{phv}\selectfont, 
-  frame=single,
-  keywordstyle=\textbf, 
-  identifierstyle=, 
-  commentstyle=\scriptsize, 
-  stringstyle=, 
-  numbers=left, 
-  numberstyle=\scriptsize,
-  stepnumber=2,
-  firstnumber=1,
-  showstringspaces=false} 
-\begin{figure}[tbp]
-\lstset{language=Perl} 
-\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
-\lstset{language=XML,keywordstyle={}} 
-\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
-\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
-availability of a Globus GRAM server and (b) sample of its output.}
-\end{figure}
-
-An Inca reporter is an executable program that tests or measures some aspect
-of a system or installed software.   Reporter executables are designed to be
-easy to produce and can be run outside of the Inca system (e.g., by a system
-administrator).  Existing reporters range from a simple Globus~\cite{globus}
-GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
-to complex Grid application benchmarks~\cite{grasp}.  Reporters must
-support certain command line options and produce an XML document, or
-\emph{report},
-according to the Inca reporter schema.  The goal of the reporter schema is to
-accommodate multiple types of data and to capture enough information about the
-reporter execution to diagnose any detected failures.  The reporter schema
-consists of the following elements:
-
-\begin{itemize}
-\item a set of header tags describing the context of the reporter
-execution:  GMT timestamp, hostname, reporter name, reporter version, working
-directory, reporter path, and arguments;
-\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
-\item a body containing the results expressed as an XML sequence; and
-\item an exit status tag
-indicating whether the reporter was able to complete its test or measurement,
-and an optional error message.  
-\end{itemize} 
-\noindent Because the body of a report can be any XML sequence, it enables
-reporters to express a wide variety of information.  Today, we have four
-standard body schemas to express software version information, software
-functionality or service tests results, usage information, and performance
-results.
-
-An extensible set of Perl APIs is provided to handle much of the effort of
-writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
-pings a pre-WS Globus GRAM server and (b) its corresponding output when
-executed on a local machine.  The reporter uses two of the Perl APIs:
-Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
-Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
-functions for handling the required input arguments
-(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
-10-31) and printing the Inca-compliant header and exit status XML tags
-(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
-1-9, 43-46).  It also includes some informational and debug logging functions
-similar to log4j.  The log output has been very useful to system
-administrators, who can view a summary of the test or benchmark that the
-reporter performed without reading the reporter source code.  Line
-\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
-executes a system command (using a 30 second timeout) after logging it to the
-'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-37).  The subclass
-Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
-standard reporter body schema that reports software functionality or service
-tests results; it handles the printing of the small body XML
-(lines~\ref{pingReporter}(b) 39-41).  Finally, the
-Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
-dependency to the reporter, telling Inca to download a
-short-term proxy before running this reporter (as discussed in
-Section~\ref{security}).  Most current reporters use the Perl APIs and consist
-of fewer than 30 lines of code.
-
-\subsection{Reporter Repositories}
-
-% What are repositories and their key features
-Reporter repositories are collections of reporters, required
-packages and libraries (including the Perl APIs described in the previous
-section), and a catalog file.  Repository contents are accessible using a URL
-and designed to be shared across multiple Inca deployments.  The catalog file,
-patterned after APT's Packages.gz~\cite{apt}, allows the user to indicate
-reporter dependencies on CPAN modules, tar.gz packages, and other external
-sources.  Inca automatically deploys dependencies into a
-subdirectory of its installation (see Section~\ref{agent}); this enables
-reporters to be deployed to resources with minimal delay.  Each package
-specified in the catalog is versioned, allowing Inca to
-automatically distribute reporter code updates such as bug fixes.  Because of
-this, Inca administrators who maintain repositories need to ensure
-that updates to reporters work properly before committing them to a repository.
-
-% We have a lot of reporters ready to be picked 
-The Inca team publishes a reporter repository that contains 143 reporters
-developed for TeraGrid.  Most reporters are either version
-reporters that collect version information from a software package,
-unit test reporters that run a more involved
-functionality test, or performance benchmark reporters.  The unit and version
-reporters cover software such as Grid middleware and tools, compilers, math libraries,
-data tools, and visualization tools.  Current performance reporters
-measure data transfer and execute Grid benchmarks as described in
-Section~\ref{grasp}.
-
-\subsection{Inca administration tool (incat)}
-
-\begin{figure*}[tbp]
-  \centering
-  \mbox{\epsfig{file=incat.eps, width=.9\textwidth}}
-  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
-  and their attributes available from the reporter repository.}
-\end{figure*}
-
-% Incat is interface Inca admin uses to configure reporters to resources
-% introduce series here; why suites are important It is designed to make the
-% effort of configuring and maintaining 100s series on resources easilty
-The Inca administrative tool (incat) is a Java Swing GUI that
-Inca administrators use to configure user-level Grid monitoring on their
-resources.  Incat allows an Inca administrator to choose which resources to
-monitor and which reporters to deploy to those resources.  The configuration
-is stored in a XML file and sent to the agent, which handles its implementation
-(described in the next section).  The Inca administrator can reload the
-configuration to make updates.  Incat provides a number of
-conveniences that enable a large number of results to be managed and collected
-with a minimum effort.
-
-To begin reporter configuration, the Inca administrator enters the location of
-one more reporter repositories, and incat loads and displays the reporters
-available from them (Figure~\ref{incat_fig}).
-For each reporter, the Inca administrator can specify the resources to run on,
-input arguments, the runtime environment, the frequency of execution, resource
-limits, and email notifications.  The sequence of reports that a reporter
-produces on a resource when executed with a specific set of input arguments and
-runtime environment is known as a \emph{report series} (or \emph{series} for
-short).
-Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
-produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
-series can be grouped into \emph{suites} and shared across other Inca
-deployments, e.g.,  a Globus suite or a data transfer
-performance suite.  Suites can also be useful in determining interoperability
-among Grids or whether an application's requirements are being
-fulfilled on a Grid.
-
-% Resource information organized to make it easier to maintain
-For each monitored resource, an Inca administrator selects an access method
-(SSH or Globus) to access the resource and start monitoring there (described
-in Sections~\ref{agent} and ~\ref{rm}).  Resources can be aggregated into
-groups for reference in the series configuration, facilitating the
-process of executing the same series on multiple resources.  Also,
-input and runtime environment attributes can be attached to resource groups
-for reference in series configuration.
-These resource \emph{macros} can have multiple values, in which
-case the series will be executed on the resource once for each macro value.
-Resource groups and macros ease the process of defining and maintaining
-multiple similar series.
-
-\subsection{Agent}
-\label{agent}
-
-The Inca agent is a server that implements the configuration specified by the
-Inca administrator.  When the agent receives a configuration from incat,
-it expands any resource group and macro references to determine
-the series to execute on each resource and stores this
-information in the depot.  The agent stages and
-launches an Inca component, called a reporter manager (described in the
-following subsection), on each resource, using either SSH or Globus.  After a
-reporter manager contacts its agent, the agent transmits the reporters to
-execute, any dependencies, and a suite that contains series
-configuration and an execution schedule.  As an Inca administrator makes
-updates to the configuration, the agent will push out new reporters and/or
-suite changes to each of the affected resources.
-
-The agent regularly pings its reporter managers in order to detect when one has
-failed (for example, when a system is taken down for maintenance) and so must
-be restarted.  The agent also maintains a local cache of reporters and their
-dependencies; it periodically checks repositories
-and automatically distributes reporter updates to the reporter managers as
-needed.  The agent is implemented using Java.
-
-\subsection{Reporter Manager}
-\label{rm}
-
-The Inca reporter manager is a lightweight process responsible for managing
-the schedule and execution of Inca reporters on a single resource. The
-reporter manager receives reporter updates and dependencies from the agent
-along with requests for reporter scheduling changes.  Running under a regular
-user account, the reporter manager executes reporters on-demand or using an
-internal cron scheduler and sends reports to the depot for archiving. The
-reporter manager monitors reporter system usage 
-and enforces limits (e.g., wall clock time, CPU time, memory).
-System usage information is sent to the depot with each report. 
-The reporter manager is implemented using Perl to allow execution on
-a wide variety of UNIX systems.
-
-\subsection{Depot}
-
-The Inca depot server is responsible for storing configuration information and
-the data produced by reporters. The depot uses a relational database via
-Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
-The depot provides full archiving of reporter output, and the database schema is
-tuned to minimize redundant data.  Inca administrators can specify pattern
-tests to run on reports as they are received, and the depot will send email
-when the results of these tests change.  This provides the administrator
-with quick notification of problems as they appear and of the results of
-repairs.
-
-Data can be retrieved using SQL queries. Predefined queries exist to return the
-latest report instances of a suite, a single report instance, or a report
-history.  A Web services interface is also available to provide
-unauthenticated query access to data.  The depot is implemented using Java.
-
-\subsection{Data Consumer}
-
-The Inca data consumer is a Web application that queries the Inca depot for
-data and displays it in a user-friendly format.  The data consumer is packaged
-with Jetty~\cite{jetty} so that Web pages can be served out of the box.  A set
-of extensible JSP tags and pages query the Inca depot for data (returned as
-XML)
-and a set of XSL stylesheets format the data as HTML.  An Inca administrator
-can customize the data display, either by modifying the XSL stylesheets or by
-writing their own JSP tags and pages.
-
-\subsection{Security}
-\label{security}
-
-To provide for security, all Inca components communicate with each other using
-SSL, and sensitive information is encrypted before being written to disk.  To
-handle reporters that
-require a proxy credential to execute, the reporter manager fetches a
-short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
-administrator), then destroys the proxy once the reporter has completed.
-MyProxy authentication information is fetched from the agent each time a proxy
-credential is needed and then cleared from memory.  Generating short-term 
-proxies as needed is more secure than maintaining long-term
-credentials and is easier to manage.
-
-\subsection{Coordinating Inca Deployments}
-
-% Should illustrate that we've thought about how Inca can scale
-\begin{figure*}[tbp]
-  \centering
-  \includegraphics[width=.6\textwidth]{vo.eps}
-  \caption{\label{tg_coord_fig} Coordinated Inca deployments.}
-\end{figure*}
-
-A planned extension to Inca 2 supports the distribution of control and storage
-workload among multiple Inca components.  Figure~\ref{tg_coord_fig} shows a
-scenario where two Inca deployments coordinate with each other.  This could
-occur in application communities like GEON~\cite{geon}, which maintains its
-own Grid but also has access to TeraGrid resources.   Running two Inca
-deployments independently could result in duplicate testing.  Instead, we plan
-to eliminate redundancy by allowing multiple deployments to coordinate suite
-execution.
-Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
-has its own resources but also has access to resources in Grid A.
-When an Inca administrator submits a suite to Grid B, the Inca agent running
-on Grid B will determine which reporters run on Grid A resources and forward
-them as a suite request to Grid A's agent.  If Grid B has permission to submit
-suites, Grid A's agent will execute the suite and configure its depot to
-forwards results back to Grid B's depot.  This extension is also expected
-to provide the mechanisms for scalability and fault tolerance in the Inca
-system.
-
-%-------------------------------------------------------------------------
-
-\section{Use Cases}
-\label{usecases}
-
-\subsection{TeraGrid}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
-  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
-\end{figure}
-
-\begin{figure*}[tbp]
-  \centering
-  \includegraphics[width=.75\textwidth]{status-page.eps}
-  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
-\end{figure*}
-
-% Description and Requirements - Describe CTSS
-Requirements for user-level Grid monitoring on TeraGrid initially included the
-validation and verification of Coordinated TeraGrid Software and Services (CTSS) 
-on each TeraGrid resource.  As described in the introduction, CTSS was designed to
-allow users to run Grid jobs more easily across its distributed, heterogeneous
-resources.  CTSS version 3 (CTSSv3) is available on all TeraGrid compute
-resources and contains approximately 30 software packages that provide
-Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
-tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
-
-To provide user-level monitoring of CTSS, Inca 1 was deployed on TeraGrid in
-2003; TeraGrid's transition to Inca 2 completed in
-November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
-to collect job usage information from Globus 2 GRAM logs and to detect expired
-host and CA certificates and CA CRLs.
-
-% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
-A number of version and unit test reporters were developed to test the software packages in CTSS.
-Currently, there are 56 such reporters executing an average of 109 series on
-each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
-GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
-application tool-related tests, and 2 security-related tests.
-
-The TeraGrid
-Inca configuration makes extensive use of macros and resource groups and
-currently uses 80 series and 82 resource macros to manage the total of 1,928
-series executing on TeraGrid resources.
-Figure~\ref{tg_deploy_fig}(a) illustrates TeraGrid's Inca 2 deployment
-configuration.  The
-agent, depot and consumer components are hosted at SDSC on 
-sapa.sdsc.edu.  A reporter repository for TeraGrid is hosted
-at SDSC on inca.sdsc.edu.
-
-% Results - Consumer view of CTSS, security, etc.
-TeraGrid currently has six status pages to display the Inca monitoring
-information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
-results, a page showing grid job
-usage, results for security tests, results for secure MDS tests, and a list of
-all running reporters.
-
-Figure~\ref{status_page_fig}(b) shows a portion of the TeraGrid detailed grid of
-CTSSv3 test results
-page.  CTSSv3 software packages are listed along the column and TeraGrid
-resources (anonymized) in the header rows.  Test results for each package and
-resource are shown in the table body rows.
-
-\subsection{GrASP}
-\label{grasp}
-
-% Describe GrASP probes
-The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
-serve as simple grid application kernel exemplars as well as a 
-set of diagnostic tools. They test and measure the performance of 
-basic Grid functions including file transfers, remote execution, 
-and information services queries.  There are two basic probes: circle and 
-gather.  The circle probe transfers a 100 MB file around a ring of
-Grid nodes and measures the transfer time at each step.  The gather probe
-transfers a 100 MB file from some number of source nodes to a compute node,
-runs a computation through the job queue on the compute resource, and then
-transfers a 100 MB file to a single destination node.  The transfer of the
-first set of files is executed in parallel.  Transfer, compute, and queue times are recorded.
-
-The GrASP probes yield data about Grid infrastructure performance and reliability.
-In order to be most useful, probe data must be gathered 
-repeatedly over time and archived.
-In addition to storing the performance measurements,
-any error messages encountered must be stored as well.    
-In order to
-gather historical data, the GrASP probes were modified
-to follow the Inca reporter specifications and deployed using Inca.
-Porting the original code to follow the reporter specifications proved to be
-trivial.  A number of scripts were then written to graph and analyze the GrASP
-data and related error messages stored in the Inca depot.
-
-\begin{figure*}[tbp]
-  \centering
-  \mbox{\epsfig{file=errorHistogramTG.eps, width=.6\textwidth}}
-  \caption{\label{errorHist_fig} Number and types of errors collected by
-  GrASP benchmark execution over a six-month period on TeraGrid.}
-\end{figure*}
-
-Using Inca, GrASP was deployed on TeraGrid and GEON for a period of over 6
-months~\cite{grasp2}.  During this deployment, the execution time of Preco, 
-a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
-A recurring Globus 2 bug was also identified as shown in Figure ~\ref{errorHist_fig}.  The figure shows the frequency and types (shortened) of 
-system errors that were detected while executing 
-GrASP on TeraGrid in 2005. The highest occurring
-error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
-the Globus 2 GRAM server.
-
-\subsection{Other Uses}
-
-Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
-Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005, respectively.  
-Similar to TeraGrid, DEISA uses Inca to verify their Common
-Production Environment (DCPE) across 11 heterogeneous resources.  They
-currently have 40 version reporters to verify each of the packages included in
-DCPE.  In addition, they have unit reporters for the DEISA Applications Test
-Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
-library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
-party application.  DEISA is currently using Inca 1 and will transition to
-Inca 2 in the next few months.
-
-NGS currently has Inca 2 deployed on four resources to verify their Grid services (on eight sites) and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
-API developed by the GITS developer.  The GITS reporters include 17 tests, 
-such as small job submissions and data transfers, that verify Globus and GSI-SSH functionality.
-NGS also has 12 tests for their compilers and
-utilize 2 security reporters from the Inca repository.
-
-%------------------------------------------------------------------------- 
-\section{Future Work}
-
-In order to improve problem detection and diagnosis for system administrators,
-we plan to add graph rendering and statistical
-analysis capabilities to the Inca data consumer.  This will improve troubleshooting capabilities by
-allowing errors to be understood in a historical context.  It will also enable
-summary displays analogous to those generated by Web page statistics packages
-like Webalizer~\cite{webalizer} that provide a number of useful
-statistics.  We expect to follow recommendations from TeraGrid and other Inca
-users on the types of statistics and graphs that will be most useful.
-Our plan is to offer a default set of statistics and graphs that can be used
-directly and to provide the capability to add others.
-
-Also to aid system administrator troubleshooting,
-we plan to enhance Inca with a knowledge base that can be used to
-discuss problems and suggest solutions.
-The knowledge base will be populated by solutions provided by
-system administrators and self-moderated to
-improve quality.
-This knowledge base could provide a vital resource
-for system administrators and offer a forum for sharing
-valuable experience and skills.
-
-Finally, we plan to improve the fault tolerance of Inca by enhancing the
-reporter manager so that it caches reports locally if it is unable to
-contact the depot or sends reports to a backup depot if one is available.
-The agent will similarly be enhanced to cache configuration changes locally or
-send configuration to a backup depot if one is available in case of a depot
-failure.
-
-%------------------------------------------------------------------------- 
-\section{Summary}
-
-%1.  Motivate and differentiate the Grid monitoring Inca does 2. Describe Inca
-%2 design and its benefits 3. Illustrate that Inca 2 design is mature and
-%being used in production by several Grids 4. Be different from Inca 1 paper
-The goal of user-level Grid monitoring is to test and measure Grid
-infrastructure from an impartial user perspective and detect problems before
-users notice them.  Inca 2 implements such a user-level Grid monitoring system
-and provides a number of new and improved features over our first version,
-Inca 1.  The architecture and features of Inca 2 enable an Inca administrator
-to easily write and deploy tests and performance measurements to Grid
-resources and maintain them in a changing Grid environment.  The storage,
-archiving, and querying capabilities also enable in-depth analysis of Grid
-errors and performance in a historical context, which benefit Grid
-operators and system administrators.  Inca 2 also provides a number of
-security features such as short-term proxy management.
-A production version of Inca 2 was released in February 2007 and
-has been used in production environments to verify the common user environment
-of TeraGrid and to execute and collect data for a set of Grid benchmarks on
-both TeraGrid and GEON.  Future enhancements of Inca 2 will improve its fault
-tolerance and enable more in-depth analysis of the overall Grid health and
-behavior.  They will also make it easier to detect and resolve errors
-and understand them in a historical context.  The features that Inca
-provides and its proposed enhancements improve the stability of the
-Grid infrastructure it monitors, ultimately improving the productivity of
-scientists who conduct research on a Grid.
-
-%------------------------------------------------------------------------- 
-\section{Acknowledgements}
-
-The authors would like to thank Denis Girou and David Spence for providing
-details for the DEISA and NGS Inca deployments, respectively.  This work was
-supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.
-
-%------------------------------------------------------------------------- 
 \bibliographystyle{abbrv}
-\bibliography{paper}
+\bibliography{wsn-dc}
 

### 2012-07-13 papers/inca-analysis/Inca-anaylsis.tex
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@14853 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass{sig-alternate}
\usepackage{subfigure,url}

\begin{document}

\title{}

\numberofauthors{1}

\author{
\alignauthor
Shava Smallen, Sameer Tilak, etc. \\
\affaddr{University of California, San Diego} \\ 
\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
\email{\{ssmallen,sameer\}@sdsc.edu}\\
}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Future Grid Overview}

The FutureGrid Project provides a geographically distributed experimental platform for computer scientists to understand the behavior and utility of cloud computing approaches. The platform will allow these computer scientists to tackle complex research challenges in the areas ranging from authentication, authorization, scheduling, virtualization, middleware design, interface design and cybersecurity to the optimization of grid-enabled and cloud-enabled computational schemes for researchers in astronomy, chemistry, biology, engineering, atmospheric science and epidemiology. The FutureGrid is a key component of NSF's high-performance cyberinfrastructure and supports innovative computer science research requiring access to lower levels of the grid software stack, the networking software stack, and to virtualization and workflow orchestration tools.

\section{Inca Architecture}

\section{Use cases}

\section{Test suite classes}

\section{Experimental results}

\subsection{Monitoring tools comparison:} Ganglia vs Inca

\subsection{reliability}

\subsection{resource-level}: How do different resources (storage, compute, network) compare in terms of reliability. Where is the bottleneck?
\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
\subsection{site-level}: How do different sites compare in terms of reliability.
\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
\subsection{cloud-stats}
\subsection{hpc-stats:} benchmarks, version numbers.
\subsection{Failures distribution:} Are failures independent or related?
\subsection{upgrade stats:} Patches done every month. 
\subsection{predictability} Is this system system predictable in terms of resource availability or failures.
\subsection{Test success rate}

\section{Future Work}

\section{Conclusion}

\bibliographystyle{abbrv}
\bibliography{wsn-dc}

 \end{document}

### 2013-01-02 pubs/papers/inca-analysis/Inca-anaylsis.tex
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@14852 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
Updated outline with page count for the Inca-Analysis paper.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15046 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
+Large-scale Inca is a user-level monitoring tool that has been used successfully in cyberinfrastructure projects such as the TeraGrid and other similar projects.
+Its flexible architecture enables multiple types of functionality and performance data to easily be collected about the systems it is monitoring.
+A unique centralized monitoring configuration approach makes Inca easy to setup and maintain on multiple systems and lends to consistent monitoring results.
+We are experimenting with using Inca in Cloud environments where users are interested in monitoring the functionality and performance of their personal Clouds as they are re-instantiated on different machines and locations.
+We believe Inca’s flexibility, easy-to-use administrative interfaces, and other features make it a natural fit for Cloud environments.
+
 \end{abstract}
+
+\section{Introduction} (0.5 page)
+
+\section{Future Grid Overview} (1 page)
+Add description of load -- vm count, hrs. etc.
+
+The FutureGrid Project provides a geographically distributed experimental platform for computer scientists to understand the behavior and utility of cloud computing approaches.
+The platform will allow these computer scientists to tackle complex research challenges in the areas ranging from authentication, authorization, scheduling, virtualization, middleware design, interface design and cybersecurity to the optimization of grid-enabled and cloud-enabled computational schemes for researchers in astronomy, chemistry, biology, engineering, atmospheric science and epidemiology.
+The FutureGrid is a key component of NSF's high-performance cyberinfrastructure and supports innovative computer science research requiring access to lower levels of the grid software stack, the networking software stack, and to virtualization and workflow orchestration tools.
+
+\section{Inca Architecture} (0.5 page)
+
+Cyberinfrastructure (CI) aggregates multiple complex and interdependent systems that span several administrative domains.
+This complexity poses challenges for both administrators who build and maintain CI resources and scientists who use them.
+These challenges and the cutting-edge nature of the infrastructure make it susceptible to failures, which frustrate and even dissuade users.
+In order to provide scientists with persistent and reliable CI, the user-level functionality and performance of the system must be monitored.
+Developed in 2003, Inca [1] is a tool that provides user-level monitoring for CI systems.
+It has proven to be a valuable tool for the TeraGrid [2] and eleven other production CI projects [3], and is currently monitoring over a hundred machines.
+Inca differs from other monitoring tools with its user-level monitoring approach, flexibility to collect multiple types of monitoring data, and full archiving support.
+Inca also uses a unique centralized monitoring configuration approach, which is essential for providing consistent monitoring results and a unified and coherent infrastructure for users.
+
+Inca automates the installation, execution, and maintenance of a large variety and number of reporters (monitoring scripts) consistently across Grid resources.
+Monitoring results are collected, archived, and displayed through web status pages.
+The core of the Inca architecture is formed by four server components: the agent, depot, data consumer, and reporter repository (see Figure 1).
+The agent controls the deployment and maintenance of the Inca installation, while the depot provides data storage.
+A reporter repository contains a set of tests and benchmarks, and the data consumer displays the collected results as web status pages.
+An additional Inca component called the reporter manager runs on each monitored resource to collect status and performance data.
+The final component of Inca is a GUI tool (incat) used by Inca administrators to configure and maintain their Inca deployments.
+
+Recently, we have been exploring how to leverage Inca in virtual Cloud environments as part of the work we are doing in FutureGrid [4].
+FutureGrid is an experimental testbed that will be used to develop and test novel approaches to parallel, grid, and cloud computing.
+It supports user “experiments” that can be run either on the bare hardware or on virtual machines using Cloud technologies Nimbus or Eucalyptus.
+In particular, we are interested in using Inca to validate a user’s virtual environment started up by these tools both in terms of functionality and performance.
+For example, a user may want to know how the performance of their virtual cluster compares to a month earlier when they last instantiated it.
+We are also interested in using Inca to validate individual virtual machine images as well.
+
+\section{Use cases} (0.5 pages)
+
+\section{Test suite classes} (0.5 pages)
+
+\section{Analysis results} (4 pages)
+Description of the methodology -- how data was filtered and interpreted.
+
+\subsection{SSH data}
+\subsubsection{Failure Classifiation:} What types of failures do we see?
+\subsubsection{Failures distribution:} Are failures independent or related?
+\subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.
+\subsection{site-level}: How do different sites compare in terms of reliability.
+
+ssh key -- test improvements.
+
+\subsection{cloud-stats}
+\subsection{hpc-stats:} benchmarks, version numbers.
+
+\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
+\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
+\subsection{upgrade stats:} Patches done every month.
+
+\section{Related Work} (0.5 page)
+
+\section{Future Work} (0.25 page)
+
+\section{Conclusion} (0.25 page)
 

### 2013-01-03 papers/inca-analysis/Inca-anaylsis.tex
Added the correct Latex template.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15048 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
-\documentclass{sig-alternate}
+\documentclass{IEEEtran}
 \usepackage{subfigure,url}
@@
 
-\title{}
+\title{Experiences with long-term monitoring of a large-scale distributed heterogenous cyberinfrastructure}
 
-\numberofauthors{1}
-
-\author{
-\alignauthor
-Shava Smallen, Sameer Tilak, etc. \\
-\affaddr{University of California, San Diego} \\ 
-\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
-\email{\{ssmallen,sameer\}@sdsc.edu}\\
+\author{\IEEEauthorblockN{Shava Smallen and Sameer Tilak}
+\IEEEauthorblockA{ University of California, San Diego \\
+La Jolla, CA, USA, Email: {\{ssmallen,stilak\}}@ucsd.edu}
 }
@@
 
+Large-scale Inca is a user-level monitoring tool that has been used successfully in cyberinfrastructure projects such as the TeraGrid and other similar projects.
+Its flexible architecture enables multiple types of functionality and performance data to easily be collected about the systems it is monitoring.
+A unique centralized monitoring configuration approach makes Inca easy to setup and maintain on multiple systems and lends to consistent monitoring results.
+We are experimenting with using Inca in Cloud environments where users are interested in monitoring the functionality and performance of their personal Clouds as they are re-instantiated on different machines and locations.
+We believe Inca’s flexibility, easy-to-use administrative interfaces, and other features make it a natural fit for Cloud environments.
+
 \end{abstract}
 
-\section{Introduction}
+\section{Introduction} (0.5 page)
 
-\section{Future Grid Overview}
+\section{Future Grid Overview} (1 page)
+Add description of load -- vm count, hrs. etc.
 
@@
 
-\section{Inca Architecture}
+\section{Inca Architecture} (0.5 page)
 
-\section{Use cases}
+Cyberinfrastructure (CI) aggregates multiple complex and interdependent systems that span several administrative domains.
+This complexity poses challenges for both administrators who build and maintain CI resources and scientists who use them.
+These challenges and the cutting-edge nature of the infrastructure make it susceptible to failures, which frustrate and even dissuade users.
+In order to provide scientists with persistent and reliable CI, the user-level functionality and performance of the system must be monitored.
+Developed in 2003, Inca [1] is a tool that provides user-level monitoring for CI systems.
+It has proven to be a valuable tool for the TeraGrid [2] and eleven other production CI projects [3], and is currently monitoring over a hundred machines.
+Inca differs from other monitoring tools with its user-level monitoring approach, flexibility to collect multiple types of monitoring data, and full archiving support.
+Inca also uses a unique centralized monitoring configuration approach, which is essential for providing consistent monitoring results and a unified and coherent infrastructure for users.
 
-\section{Test suite classes}
+Inca automates the installation, execution, and maintenance of a large variety and number of reporters (monitoring scripts) consistently across Grid resources.
+Monitoring results are collected, archived, and displayed through web status pages.
+The core of the Inca architecture is formed by four server components: the agent, depot, data consumer, and reporter repository (see Figure 1).
+The agent controls the deployment and maintenance of the Inca installation, while the depot provides data storage.
+A reporter repository contains a set of tests and benchmarks, and the data consumer displays the collected results as web status pages.
+An additional Inca component called the reporter manager runs on each monitored resource to collect status and performance data.
+The final component of Inca is a GUI tool (incat) used by Inca administrators to configure and maintain their Inca deployments.
 
-\section{Experimental results}
+Recently, we have been exploring how to leverage Inca in virtual Cloud environments as part of the work we are doing in FutureGrid [4].
+FutureGrid is an experimental testbed that will be used to develop and test novel approaches to parallel, grid, and cloud computing.
+It supports user “experiments” that can be run either on the bare hardware or on virtual machines using Cloud technologies Nimbus or Eucalyptus.
+In particular, we are interested in using Inca to validate a user’s virtual environment started up by these tools both in terms of functionality and performance.
+For example, a user may want to know how the performance of their virtual cluster compares to a month earlier when they last instantiated it.
+We are also interested in using Inca to validate individual virtual machine images as well.
 
-\subsection{Monitoring tools comparison:} Ganglia vs Inca
+\section{Use cases} (0.5 pages)
 
-\subsection{reliability}
+\section{Test suite classes} (0.5 pages)
 
-\subsection{resource-level}: How do different resources (storage, compute, network) compare in terms of reliability. Where is the bottleneck?
-\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
+\section{Analysis results} (4 pages)
+Description of the methodology -- how data was filtered and interpreted.
+
+\subsection{SSH data}
+\subsubsection{Failure Classifiation:} What types of failures do we see?
+\subsubsection{Failures distribution:} Are failures independent or related?
+\subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.
 \subsection{site-level}: How do different sites compare in terms of reliability.
-\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
+
+ssh key -- test improvements.
+
 \subsection{cloud-stats}
 \subsection{hpc-stats:} benchmarks, version numbers.
-\subsection{Failures distribution:} Are failures independent or related?
+
+\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
+\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
 \subsection{upgrade stats:} Patches done every month.
-\subsection{predictability} Is this system system predictable in terms of resource availability or failures.
-\subsection{Test success rate}
 
-\section{Future Work}
+\section{Related Work} (0.5 page)
 
-\section{Conclusion}
+\section{Future Work} (0.25 page)
+
+\section{Conclusion} (0.25 page)
 

### 2013-01-05 xsede/bin/downtimes.pl
updated script
git-svn-id: file:///localdisk/subversion/inca/trunk/devel/projects/teragrid@15051 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@ -28,13 +28,9 @@ for my $url ( @urls ) {
     my @outages = split(/\n/, $outfile);
     for my $i (1 .. $#outages){
       my @line = split(/,/, $outages[$i]);
-      # 5/16/12 -- resource ids got reversed to <resource-name>-<site>
+      # 10/9/12:  expecting iis id on second field
       my $iis_resource = $line[1];
-      my @iis_resource_ids = split( /-/, $iis_resource );
-      next if scalar(@iis_resource_ids) < 2; # not a resource-site pair
-      my $site = $iis_resource_ids[$#iis_resource_ids];
-      next if $site eq "news";
-      my $resource = $iis_resource_ids[0];
+      next if $iis_resource =~ /general-user-news/;
       my $start= $line[$#line-1];
       $start =~ s/"//g;
       my $end= $line[$#line];
@@ -45,15 +41,21 @@ for my $url ( @urls ) {
       if ( Date_Cmp($now, $startDate) >= 0 &&
            (! defined $endDate || $endDate eq "" || Date_Cmp($now, $endDate)< 1) ) {
         my ($news_id) = $line[2] =~ /(\d+)"/;
-        my $rnode = $xp->find("/res:resourceConfig/resources/resource[name='$resource-$site']/macros/macro[name='__regexp__']/value/text()");
-        print PROP "$site-$resource=$news_id\n";
+        # 10/9/12 -- lonestar has 2 registrations in IIS lonestar and lonestar4
+        my $search_resource = $iis_resource =~ /lonestar/ ? "lonestar4.tacc.teragrid.org" : $iis_resource;
+        $search_resource = $search_resource =~ /ranch/ ? "ranch.tacc.xsede.org" : $search_resource;
+        $search_resource = $search_resource =~ /condor/ ? "condor.purdue.teragrid.org" : $search_resource;
+        my $rnode = $xp->find("/res:resourceConfig/resources/resource[name='$search_resource']/macros/macro[name='__regexp__']/value/text()");
+        print IIS "$iis_resource=$news_id\n";
         foreach my $node ($rnode->get_nodelist) {
           my $resource = XML::XPath::XMLParser::as_string($node);
           my @resources = split(/ /, $resource);
           foreach my $r (@resources) {
-            print IIS "$r=$news_id\n";
+            print PROP "$r=$news_id\n";
           }
         }
+      } else {
+         ##print "$iis_resource $start $end\n";
       }
     }
   }

### 2013-01-05 xsede/bin/downtimes.pl
specify inca install in one place
git-svn-id: file:///localdisk/subversion/inca/trunk/devel/projects/teragrid@15052 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@ -1,22 +1,28 @@
 #!/usr/bin/perl
 
+
 use strict;
 use warnings;
-use lib "/localdisk/inca/teragrid/lib/perl";
+
+my $INCA_INSTALL;
+BEGIN { # force variable to be set during compile
+  $INCA_INSTALL="$ENV{HOME}/xsede";
+}
+use lib "$INCA_INSTALL/lib/perl";
 use LWP::Simple;
 use XML::XPath;
 use XML::XPath::XMLParser;
 use Data::Dumper;
 use Date::Manip;
 
-my $config = `cat /localdisk/inca/teragrid/var/resources.xml`;
+my $config = `cat $INCA_INSTALL/var/resources.xml`;
 my $xp = XML::XPath->new( xml => $config );
 
 # get current downtimes
 # future is looked at too since there were some timezone parsing problems
 my @urls = ( "http://info.teragrid.org/web-apps/csv/tg-outages-v1/future/", "http://info.teragrid.org/web-apps/csv/tg-outages-v1/current/");
-my $pre = "/localdisk/inca/teragrid/webapps";
-my $prop = "$pre/../etc/downtime.properties";
+my $pre = "$INCA_INSTALL/webapps";
+my $prop = "$INCA_INSTALL/etc/downtime.properties";
 my $iis =  "$pre/inca/html/downtimes-iis.txt";
 open PROP,">$prop";
 open IIS,">$iis";

### 2013-01-06 pubs/papers/inca-analysis/Inca-anaylsis.tex
Minor updates to title.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15049 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
Added fg- machine paritition table info.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15055 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 
-\title{}
+\title{Experiences with long-term monitoring of a large-scale distributed and heterogenous cyberinfrastructure}
 
-\numberofauthors{1}
-
-\author{
-\alignauthor
-Shava Smallen, Sameer Tilak, etc. \\
-\affaddr{University of California, San Diego} \\ 
-\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
-\email{\{ssmallen,sameer\}@sdsc.edu}\\
+\author{\IEEEauthorblockN{Shava Smallen and Sameer Tilak}
+\IEEEauthorblockA{ University of California, San Diego \\
+La Jolla, CA, USA, Email: {\{ssmallen,stilak\}}@ucsd.edu}
 }
@@
 
-\section{Future Grid Overview} (1 page)
+\section{FutureGrid Overview} (1 page)
 Add description of load -- vm count, hrs. etc.
@@
 The FutureGrid is a key component of NSF's high-performance cyberinfrastructure and supports innovative computer science research requiring access to lower levels of the grid software stack, the networking software stack, and to virtualization and workflow orchestration tools.
+
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | }
+ \hline
+Resource & HPC  & Eucalyptus & Nimbus  & Openstack   \\
+  \hline
+Site 1 resource 1 (1136 cores) & 44.7\% (508 cores) & 21.1\% (240 cores) & &  19.7\% (224 cores) \\  \hline
+Site1 resource 2(664 cores) & 100\% (664 cores) & & & \\  \hline
+Site 2 (705.28 cores) & 86.2\% (608 cores) & & 13.8\% (97.28 cores) &  \\  \hline
+Site 3 (640 cores) & 48.8\% (312 cores) & & 51.2\% (328 cores) &  \\  \hline
+Site 4 (632 cores) & 43\% (272 cores) & 15.2\% (96 cores) & 22.8\% (144 cores) & 3.8\% (24 cores)   \\  \hline
+Site 5 (192 cores) & & & 95.8\% (184 cores) &   \\  \hline
+
+\end{tabular}
+\caption{FutureGrid: Machine Partition Information (A small percentage of nodes may be unavailable or used for management) }
+ \label{tab:fg-machine-allocation}
+
+\end{table*}
 

### 2013-10-02 pubs/papers/inca-analysis/Inca-anaylsis.tex
Updated text.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15331 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@
 \documentclass{IEEEtran}
-\usepackage{subfigure,url}
+\usepackage{graphicx,subfigure,url, amsmath}
 
@@
 
-\section{Introduction} (0.5 page)
+\section{Introduction} (0.5 page) (Sameer and Shava)
 
-\section{FutureGrid Overview} (1 page)
+\section{FutureGrid Overview} (0.5 page) (Shava)
+
 Add description of load -- vm count, hrs. etc.
@@
 
-\section{Inca Architecture} (0.5 page)
+\section{Inca Architecture} (0.5 page) (Shava)
 
@@
 
-\section{Use cases} (0.5 pages)
+\section{Monitoring data analysis} (3 - 4 pages)
 
-\section{Test suite classes} (0.5 pages)
-
-\section{Analysis results} (4 pages)
+\subsection{Test suite description} (2 pages, 0.5 page/class) (Shava)
 Description of the methodology -- how data was filtered and interpreted.
 
+\subsection{Results} (Sameer)
+
 \subsection{SSH data}
-\subsubsection{Failure Classifiation:} What types of failures do we see?
+\subsubsection{Failure Classification:} What types of failures do we see?
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.60]{figs/fg-failure-counts}
+\caption{Failure Classification}
+\label{fig:fg-failure-counts}
+\end{center}
+\end{figure*}
+
+\subsection{site-level}: How do different sites compare in terms of reliability.
+
+%$\begin{equation} \label{eq:MTBF}
+$ MTBF$ =  $\Sigma$ (start of downtime - start of uptime) $/$ (number of failures)
+% \end{equation}
+
+\begin{figure*}
+\centering
+\mbox{
+\subfigure[MTBF for all FutureGrid sites ]{
+   \includegraphics[scale =0.70] {figs/MTBF}
+   \label{fig:subfig1}
+ }\quad
+
+ \subfigure[Failure counts for all FugureGrid sites]{
+   \includegraphics[scale =0.70] {figs/site-level-failure-count}
+   \label{fig:subfig2}
+ }
+}
+\centering
+\label{myfigure}
+\caption{Android software stack and its comparison with Linux}
+\end{figure*}
+
 \subsubsection{Failures distribution:} Are failures independent or related?
 \subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.
-\subsection{site-level}: How do different sites compare in terms of reliability.
+
+\subsection{cloud-stats}
+
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | }
+ \hline
+Nimbus & tacc-alamo  & uc-hotel & ucsd-sierra  & ufl-foxtrot   \\
+  \hline
+clientStatus & 98\% & 96\% &  81\% &  80\% \\  \hline
+create-publicvm & 93\%& 89\% &  91\% & 58\% \\  \hline
+storage & 100\% & 97\% & 98\% &  99\% \\  \hline
+
+\end{tabular}
+\caption{Nimbus: Reliability across FutureGrid machines}
+ \label{tab:nimbus-fg-reliability}
+
+\end{table*}
+
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | }
+ \hline
+Eucalyptus & iu-india  & ucsd-sierra    \\
+  \hline
+clientStatus & 96\% & 93\%  \\  \hline
+create-publicvm & 77\%& 56\%  \\  \hline
+storage & 100\% & 97\%   \\  \hline
+
+\end{tabular}
+\caption{Eucalyptus: Reliability across FutureGrid machines}
+ \label{tab:eucalyptus-fg-reliability} 
+\end{table*}
 
@@
 
-\subsection{cloud-stats}
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | }
+ \hline
+Openstack & iu-india      \\
+  \hline
+clientStatus & 97\%   \\  \hline
+create-publicvm & 71\%  \\  \hline
+storage & 80\%  \\  \hline
+
+\end{tabular}
+\caption{Openstack: Reliability across FutureGrid machines}
+ \label{tab:openstack-fg-reliability}
+
+\end{table*}
+
 \subsection{hpc-stats:} benchmarks, version numbers.
+
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | c | c | c | }
+ \hline
+HPC jobs & iu-bravo & iu-delta & iu-india  & iu-xray  & tacc-alamo & uc-hotel & ucsd-sierra \\
+  \hline
+batch-testjob & & & 88\% & 97\% &   77\% &  100 & 99\% \% \\  \hline
+batch-testjob\_to\_bravo & 99\% & & & & & & \\  \hline
+batch-testjob\_to\_delta &  & 95\% & & & & & \\  \hline
+CUDA-testjob\_to\_delta &  & 95\% & & & & & \\  \hline
+myhadoop &  & & 54\% & & 59\% & 89\% & 47\%  \\  \hline
+
+\end{tabular}
+\caption{HPC jobs: Reliability across FutureGrid machines}
+ \label{tab:hpc-fg-reliability}
+
+\end{table*}
+
+\begin{table*}
+
+\begin{tabular}{| l | c | c | c | c | }
+ \hline
+HPCC jobs & iu-india  & iu-xray & ucsd-sierra    \\
+  \hline
+hpcc8 & 99\% & 97\% & 72\% \\  \hline
+hpcc16 & 99\% & 96\% & \\  \hline
+hpcc32 &  & 95\% &   \\  \hline
+hpcc64 & 97\% & 96\% &  \\  \hline
+hpcc128 & 93\% & 93\% &   \\  \hline
+hpcc256 & 79\% & 71\% &   \\  \hline
+hpcc512 & & 93\% &   \\  \hline
+hpcc672 & & 99\%  &  \\  \hline
+
+\end{tabular}
+\caption{HPCC jobs: Reliability across FutureGrid machines}
+ \label{tab:hpcc-fg-reliability} 
+\end{table*}
 
@@
 
-\section{Related Work} (0.5 page)
+\section{Lessons Learned / Best Practices} (1 page) (Shava and Sameer)
 
-\section{Future Work} (0.25 page)
+\section{Related Work} (0.5 page) (Shava and Sameer)
 
-\section{Conclusion} (0.25 page)
+\section{Future Work} (0.25 page) (Shava and Sameer)
+
+\section{Conclusion} (0.25 page) (Shava and Sameer)
 

### 2022-07-07 pubs/papers/inca-analysis/csvdata/getHistory.pl
removing commit that lacked history

@@ -1,118 +1,0 @@
-#!/usr/bin/perl
-
-use strict;
-use warnings;
-use Time::Local;
-
-sub fetchData {
-  my ($filename, $suite, $resource, $nickname, $startdate, $enddate) = @_;
-
-  my $url = "http://inca.futuregrid.org:8080/inca/CSV/rest/$suite/$resource/$nickname/$startdate/$enddate";
-  print "Fetching data from $url\n";
-  `wget --header "Accept-Language: en-US,en"  -O "$filename.tmp" '$url' 2>&1`;
-  my $firstline = `head -1 $filename.tmp`;
-  die "Problem fetching history from $url" if $firstline !~ /resource, targetResource/;
-  return "$filename.tmp";
-}
-
-sub getDate {
-  my $time = shift;
-  my ($sec,$min,$hour,$mday,$mon,$year,$wday,$yday,$isdst) = localtime($time);
-  return sprintf( "%02d%02d%02d", $mon+1, $mday, $year-100);
-}
-
-sub getTimestamp {
-  my $collected = shift;
-
-  my ($year, $month, $day, $hour, $min, $sec) = $collected =~ /20(\d\d)-(\d\d)-(\d\d)T(\d+):(\d+):(\d+)/;
-  return timelocal($sec,$min,$hour,$day,$month-1,$year);
-}
-
-my ($filename, $frequency, $prepend) = @ARGV;
-my ($datadir, $basename) = $filename =~ /(\S+?)\/([^\/]+)$/;
-my ($suite, $nickname, $resource) = $basename =~ /([^\+]+)\+([^\+]+)\+([^\+]+?)\.csv/;
-
-$datadir = "." if ! defined $datadir;
-my $end = time() + 86400;; 
-my $enddate = getDate($end);
-if ( ! -f $filename || defined $prepend ) {
-  if ( -f $filename ) {
-    my @firstlines = `head -2 $filename`;
-    my $collected = (split(/","/, $firstlines[1]))[6];
-    die "No timestamp found in $firstlines[1]" if ! defined $collected;
-    $end = getTimestamp($collected);
-    my ($year, $month, $day) = $collected =~ /20(\d\d)-(\d\d)-(\d\d)/;
-    $enddate = "$month$day$year";
-  } else {
-    print "Creating new data file $filename\n";
-  }
-  my $numtries = 0;
-  while( $numtries <=10 ) {
-     my $start = $end - ($frequency * 3600);
-     my $startdate = getDate($start);
[…]
